### 2016-12-02 paper1_jrss.Rnw
initializing the paper and uploading the latex style files

\documentclass{statsoc}

%======================================================%
%-----------------------------------------------------------------------------------------------%
%****************************************************************************%
%++++++++++++++++++++++++++++++++++++++++++++++++++++++%
%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~%
%  My Packages and Commands %

%\usepackage{fullpage}
\usepackage{setspace}
\usepackage[left=1in,top=1in,right=1in]{geometry}
\pdfpagewidth 8.5in
\pdfpageheight 11in 
\setlength{\textheight}{9in}

% BIBLIOGRAPHY
\usepackage[authoryear]{natbib}
\bibpunct{(}{)}{;}{a}{}{,}
%\linespread{1.5}

\long\def\symbolfootnote[#1]#2{\begingroup%
\def\thefootnote{\fnsymbol{footnote}}\footnote[#1]{#2}\endgroup}

\usepackage{amssymb, amsmath, blindtext, enumitem}

%============================================
%============================================
%My New Commands
%============================================
\newcommand{\balpha}{\mbox{\boldmath $\alpha$} }
\newcommand{\bbeta}{\mbox{\boldmath $\beta$} }
\newcommand{\bdelta}{\mbox{\boldmath $\delta$} }
\newcommand{\bepsilon}{\mbox{\boldmath $\epsilon$} }
\newcommand{\bgamma}{\mbox{\boldmath $\gamma$} }
\newcommand{\blambda}{\mbox{\boldmath $\lambda$} }
\newcommand{\bmu}{\mbox{\boldmath $\mu$} }
\newcommand{\bnu}{\mbox{\boldmath $\nu$} }
\newcommand{\bomega}{\mbox{\boldmath $\omega$} }
\newcommand{\bphi}{\mbox{\boldmath $\phi$} }
\newcommand{\bpsi}{\mbox{\boldmath $\psi$} }
\newcommand{\brho}{\mbox{\boldmath $\rho$} }
\newcommand{\bsigma}{\mbox{\boldmath $\sigma$} }
\newcommand{\btau}{\mbox{\boldmath $\tau$} }
\newcommand{\btheta}{\mbox{\boldmath $\theta$} }
\newcommand{\bupsilon}{\mbox{\boldmath $\upsilon$} }
\newcommand{\bxi}{\mbox{\boldmath $\xi$} }
\newcommand{\bzeta}{\mbox{\boldmath $\zeta$} }
\newcommand{\bDelta}{\mbox{\boldmath $\Delta$} }
\newcommand{\bGamma}{\mbox{\boldmath $\Gamma$} }
\newcommand{\bLambda}{\mbox{\boldmath $\Lambda$} }
\newcommand{\bPhi}{\mbox{\boldmath $\Phi$} }
\newcommand{\bSigma}{\mbox{\boldmath $\Sigma$} }
\newcommand{\bTheta}{\mbox{\boldmath $\Theta$} }

\newcommand{\bfa}{\mbox{\bf a} }
\newcommand{\bfb}{\mbox{\bf b} }
\newcommand{\bfc}{\mbox{\bf c} }
\newcommand{\bfd}{\mbox{\bf d} }
\newcommand{\bfe}{\mbox{\bf e} }
\newcommand{\bff}{\mbox{\bf f} }
\newcommand{\bfg}{\mbox{\bf g} }
\newcommand{\bfh}{\mbox{\bf h} }
\newcommand{\bfi}{\mbox{\bf i} }
\newcommand{\bfj}{\mbox{\bf j} }
\newcommand{\bfk}{\mbox{\bf k} }
\newcommand{\bfl}{\mbox{\bf l} }
\newcommand{\bfm}{\mbox{\bf m} }
\newcommand{\bfn}{\mbox{\bf n} }
\newcommand{\bfo}{\mbox{\bf o} }
\newcommand{\bfp}{\mbox{\bf p} }
\newcommand{\bfq}{\mbox{\bf q} }
\newcommand{\bfr}{\mbox{\bf r} }
\newcommand{\bfs}{\mbox{\bf s} }
\newcommand{\bft}{\mbox{\bf t} }
\newcommand{\bfu}{\mbox{\bf u} }
\newcommand{\bfv}{\mbox{\bf v} }
\newcommand{\bfw}{\mbox{\bf w} }
\newcommand{\bfx}{\mbox{\bf x} }
\newcommand{\bfy}{\mbox{\bf y} }
\newcommand{\bfz}{\mbox{\bf z} }
\newcommand{\bfA}{\mbox{\bf A} }
\newcommand{\bfB}{\mbox{\bf B} }
\newcommand{\bfC}{\mbox{\bf C} }
\newcommand{\bfD}{\mbox{\bf D} }
\newcommand{\bfE}{\mbox{\bf E} }
\newcommand{\bfF}{\mbox{\bf F} }
\newcommand{\bfG}{\mbox{\bf G} }
\newcommand{\bfH}{\mbox{\bf H} }
\newcommand{\bfI}{\mbox{\bf I} }
\newcommand{\bfJ}{\mbox{\bf J} }
\newcommand{\bfK}{\mbox{\bf K} }
\newcommand{\bfL}{\mbox{\bf L} }
\newcommand{\bfM}{\mbox{\bf M} }
\newcommand{\bfN}{\mbox{\bf N} }
\newcommand{\bfO}{\mbox{\bf O} }
\newcommand{\bfP}{\mbox{\bf P} }
\newcommand{\bfQ}{\mbox{\bf Q} }
\newcommand{\bfR}{\mbox{\bf R} }
\newcommand{\bfS}{\mbox{\bf S} }
\newcommand{\bfT}{\mbox{\bf T} }
\newcommand{\bfU}{\mbox{\bf U} }
\newcommand{\bfV}{\mbox{\bf V} }
\newcommand{\bfW}{\mbox{\bf W} }
\newcommand{\bfX}{\mbox{\bf X} }
\newcommand{\bfY}{\mbox{\bf Y} }
\newcommand{\bfZ}{\mbox{\bf Z} }

\newcommand{\calA}{{\cal A}}
\newcommand{\calB}{{\cal B}}
\newcommand{\calC}{{\cal C}}
\newcommand{\calD}{{\cal D}}
\newcommand{\calE}{{\cal E}}
\newcommand{\calF}{{\cal F}}
\newcommand{\calG}{{\cal G}}
\newcommand{\calH}{{\cal H}}
\newcommand{\calI}{{\cal I}}
\newcommand{\calJ}{{\cal J}}
\newcommand{\calK}{{\cal K}}
\newcommand{\calL}{{\cal L}}
\newcommand{\calM}{{\cal M}}
\newcommand{\calN}{{\cal N}}
\newcommand{\calO}{{\cal O}}
\newcommand{\calP}{{\cal P}}
\newcommand{\calQ}{{\cal Q}}
\newcommand{\calR}{{\cal R}}
\newcommand{\calS}{{\cal S}}
\newcommand{\calT}{{\cal T}}
\newcommand{\calU}{{\cal U}}
\newcommand{\calV}{{\cal V}}
\newcommand{\calW}{{\cal W}}
\newcommand{\calX}{{\cal X}}
\newcommand{\calY}{{\cal Y}}
\newcommand{\calZ}{{\cal Z}}

\renewcommand{\Hat}{\widehat}
\renewcommand{\Bar}{\overline}
\renewcommand{\Tilde}{\widetilde}

\newcommand{\iid}{\stackrel{iid}{\sim}}
\newcommand{\indep}{\overset{ind}{\sim}}
\newcommand{\argmax}{{\mathop{\rm arg\, max}}}
\newcommand{\argmin}{{\mathop{\rm arg\, min}}}
\newcommand{\Frechet}{ \mbox{Fr$\acute{\mbox{e}}$chet} }
\newcommand{\Matern}{ \mbox{Mat$\acute{\mbox{e}}$rn} }

\providecommand{\argmin}[1]{\underset{{#1}}{\rm \ argmin}} 
\providecommand{\argmax}[1]{\underset{{#1}}{\rm \ argmax}}

\newcommand{\seteq}{\stackrel{set}{\ =\ }}

\newcommand{\bfig}{\begin{figure}}
\newcommand{\efig}{\end{figure}}
\newcommand{\beqx}{\begin{equation*}}
\newcommand{\eeqx}{\end{equation*}}
\newcommand{\beq}{\begin{equation}}
\newcommand{\eeq}{\end{equation}}
\newcommand{\beqa}{\begin{eqnarray}}
\newcommand{\eeqa}{\end{eqnarray}}
\newcommand{\beqax}{\begin{eqnarray*}}
\newcommand{\eeqax}{\end{eqnarray*}}
\newcommand{\beqn}{\begin{dmath}}
\newcommand{\eeqn}{\end{dmath}}
\newcommand{\beqnx}{\begin{dmath*}}
\newcommand{\eeqnx}{\end{dmath*}}

\let\originalleft\left
\let\originalright\right
\renewcommand{\left}{\mathopen{}\mathclose\bgroup\originalleft}
\renewcommand{\right}{\aftergroup\egroup\originalright}

\providecommand{\itbf}[1]{\textit{\textbf{#1}}} 
\providecommand{\abs}[1]{\left\lvert#1\right\rvert} 
\providecommand{\norm}[1]{\left\lVert#1\right\rVert}

\newcommand{\cond}{\,\left\vert\vphantom{}\right.}
\newcommand{\Cond}{\,\Big\vert\vphantom{}\Big.}
\newcommand{\COND}{\,\Bigg\vert\vphantom{}\Bigg.}

\providecommand{\paren}[1]{\left(#1\right)} 
\providecommand{\Paren}[1]{\Big(#1\Big)}
\providecommand{\PAREN}[1]{\bigg(#1\bigg)} 
\providecommand{\bracket}[1]{\left[ #1 \right]} 
\providecommand{\Bracket}[1]{\Big[ #1 \Big]} 
\providecommand{\BRACKET}[1]{\bigg[ #1 \bigg]} 
\providecommand{\curlybrace}[1]{\left\{ #1 \right\}} 
\providecommand{\Curlybrace}[1]{\Big\{ #1 \Big\}} 
\providecommand{\CURLYBRACE}[1]{\bigg\{ #1 \bigg\}}

\newcommand{\Bern}{\mbox{{\sf Bern}}}
\newcommand{\Bernoulli}{\mbox{{\sf Bernoulli}}}
\newcommand{\Beta}{\mbox{{\sf Beta}}}
\newcommand{\Bin}{\mbox{{\sf Bin}}}
\newcommand{\Binomial}{\mbox{{\sf Binomial}}}
\newcommand{\DE}{\mbox{{\sf DE}}}
\newcommand{\Exponential}{\mbox{{\sf Exponential}}}
\newcommand{\F}{\mbox{{\sf F}}}
\newcommand{\Gam}{\mbox{{\sf Gamma}}}
\newcommand{\GP}{\mbox{{\sf GP}}}
\newcommand{\GPD}{\mbox{{\sf GPD}}}
\newcommand{\Geom}{\mbox{{\sf Geom}}}
\newcommand{\Geometric}{\mbox{{\sf Geometric}}}
\newcommand{\HyperGeom}{\mbox{{\sf HyperGeom}}}
\newcommand{\HyperGeometric}{\mbox{{\sf HyperGeometric}}}
\newcommand{\InverseGam}{\mbox{{\sf InverseGamma}}}
\newcommand{\InvWish}{\mbox{{\sf InvWish}}}
\newcommand{\MVN}{\mbox{{\sf MVN}}}
\newcommand{\NB}{\mbox{{\sf NB}}}
\newcommand{\NegBin}{\mbox{{\sf NegBin}}}
\newcommand{\NegativeBinomial}{\mbox{{\sf NegativeBinomial}}}
\newcommand{\Normal}{\mbox{{\sf Normal}}}
\newcommand{\Pois}{\mbox{{\sf Pois}}}
\newcommand{\Poisson}{\mbox{{\sf Poisson}}}
\newcommand{\Unif}{\mbox{{\sf Unif}}}
\newcommand{\Uniform}{\mbox{{\sf Uniform}}}
\newcommand{\Weibull}{\mbox{{\sf Weibull}}}

\renewcommand{\P}{{\sf P}}
\newcommand{\Prob}{{\sf Prob}}
\newcommand{\median}{{\mathop{\rm median}}}
\newcommand{\E}{\mathsf{E}}
\newcommand{\V}{\mathsf{V}}
\newcommand{\VAR}{\mathsf{VAR}}
\newcommand{\COV}{\mathsf{COV}}

\newcommand{\Ind}{\mathds{1}}
\newcommand{\zerovect}{\mbox{\bf 0}}
\newcommand{\onesvect}{\mbox{\bf 1}}
\providecommand{\real}[1]{\mathbb{#1}}
\newcommand{\Real}{\mathbb{R}}
\newcommand{\ppd}{\mathcal{P}}
\DeclareMathOperator{\logit}{logit}
\DeclareMathOperator{\expit}{expit}
\DeclareMathOperator{\dint}{\displaystyle\int}
\DeclareMathOperator{\dsum}{\displaystyle\sum}

%============================================
%My New Commands
%============================================
%============================================

\newcommand{\bitemize}{\begin{itemize}\setlength{\itemsep}{1pt}\setlength{\parskip}{1pt}}
\newcommand{\eitemize}{\end{itemize}}
\newcommand{\benum}{\begin{enumerate}\setlength{\itemsep}{1pt}\setlength{\parskip}{1pt}}
\newcommand{\eenum}{\end{enumerate}}

\usepackage{fancyhdr}
\pagestyle{fancy}

%\lhead{\footnotesize \parbox{11cm}{Custom left-head-note} }
\cfoot{}
\lfoot{\footnotesize \parbox{11cm}{}}
\rfoot{\footnotesize Page \thepage\ }
%\rfoot{\footnotesize Page \thepage\ of \pageref{LastPage}}
%\renewcommand\headheight{24pt}
\renewcommand\footrulewidth{0.4pt}

\usepackage[colorlinks=false,
          %  pdfborder={0 0 0},
            ]{hyperref}

%  My Packages and Commands %
%======================================================%
%-----------------------------------------------------------------------------------------------%
%****************************************************************************%
%++++++++++++++++++++++++++++++++++++++++++++++++++++++%
%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~%
%______________________________________________________%

%============================================
%============================================
% PREAMBLE
%============================================
%============================================

\title[Graphical modeling of seabird distributions]{Graphical modeling of seabird distributions}
\author[Author 1 {\it et al.}]{Author 1}
\address{Affiliation,
City,
         Country.}
\email{Author@emailaddress.com}
\author{Author 2}
\address{Affiliation,
         City,
         Country.}

%============================================
%============================================
\begin{document}%\linenumbers
%============================================
%============================================

%============================================
\begin{abstract}
  Graphical modeling of seabird distributions.
\end{abstract}

\keywords{Graphical modeling, Marked point process, Seabird distribution}
%============================================

%============================================
\section{Introduction}
%============================================

%============================================
\section{Methods}
%============================================

\end{document}

### 2017-01-19 paper1_jrss.tex
initializing the paper and uploading the latex style files
updated

--- 2016-12-02 paper1_jrss.Rnw
@@
-\documentclass{statsoc}
+\documentclass{statsoc}\usepackage[]{graphicx}\usepackage[]{color}
+%% maxwidth is the original width if it is less than linewidth
+%% otherwise use linewidth (to make sure the graphics do not exceed the margin)
+\makeatletter
+\def\maxwidth{ %
+  \ifdim\Gin@nat@width>\linewidth
+    \linewidth
+  \else
+    \Gin@nat@width
+  \fi
+}
+\makeatother
+
+\definecolor{fgcolor}{rgb}{0.345, 0.345, 0.345}
+\newcommand{\hlnum}[1]{\textcolor[rgb]{0.686,0.059,0.569}{#1}}%
+\newcommand{\hlstr}[1]{\textcolor[rgb]{0.192,0.494,0.8}{#1}}%
+\newcommand{\hlcom}[1]{\textcolor[rgb]{0.678,0.584,0.686}{\textit{#1}}}%
+\newcommand{\hlopt}[1]{\textcolor[rgb]{0,0,0}{#1}}%
+\newcommand{\hlstd}[1]{\textcolor[rgb]{0.345,0.345,0.345}{#1}}%
+\newcommand{\hlkwa}[1]{\textcolor[rgb]{0.161,0.373,0.58}{\textbf{#1}}}%
+\newcommand{\hlkwb}[1]{\textcolor[rgb]{0.69,0.353,0.396}{#1}}%
+\newcommand{\hlkwc}[1]{\textcolor[rgb]{0.333,0.667,0.333}{#1}}%
+\newcommand{\hlkwd}[1]{\textcolor[rgb]{0.737,0.353,0.396}{\textbf{#1}}}%
+\let\hlipl\hlkwb
+
+\usepackage{framed}
+\makeatletter
+\newenvironment{kframe}{%
+ \def\at@end@of@kframe{}%
+ \ifinner\ifhmode%
+  \def\at@end@of@kframe{\end{minipage}}%
+  \begin{minipage}{\columnwidth}%
+ \fi\fi%
+ \def\FrameCommand##1{\hskip\@totalleftmargin \hskip-\fboxsep
+ \colorbox{shadecolor}{##1}\hskip-\fboxsep
+     % There is no \\@totalrightmargin, so:
+     \hskip-\linewidth \hskip-\@totalleftmargin \hskip\columnwidth}%
+ \MakeFramed {\advance\hsize-\width
+   \@totalleftmargin\z@ \linewidth\hsize
+   \@setminipage}}%
+ {\par\unskip\endMakeFramed%
+ \at@end@of@kframe}
+\makeatother
+
+\definecolor{shadecolor}{rgb}{.97, .97, .97}
+\definecolor{messagecolor}{rgb}{0, 0, 0}
+\definecolor{warningcolor}{rgb}{1, 0, 1}
+\definecolor{errorcolor}{rgb}{1, 0, 0}
+\newenvironment{knitrout}{}{} % an empty environment to be redefined in TeX
+
+\usepackage{alltt}
 
@@
 
-\title[Graphical modeling of seabird distributions]{Graphical modeling of seabird distributions}
+\title[Modeling dependencies in multivariate seabird distributions]{Modeling dependencies in multivariate seabird distributions: linking graphical models to social network analysis}
 \author[Author 1 {\it et al.}]{Author 1}
@@
 %============================================
+\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
 \begin{document}%\linenumbers
@@
 
+%============================================
+\section{Data}
+%============================================
+
+species: 
+Herring gull $(n=3978)$,
+greater shearwater $(n=3732)$,
+northern gannet $(n=3451)$,
+great black-backed gull $(n=3319)$,
+Wilson's storm-petrel $(n=2746)$,
+common loon $(n=1900)$,
+northern fulmar $(n=1688)$,
+red-throated loon $(n=1400)$,
+Cory's shearwater $(n=1138)$,
+Leach's storm-petrel $(n=1005)$,
+unidentified gull $(n=984)$,
+common tern $(n=982)$,
+black-legged kittiwake $(n=971)$,
+dovekie $(n=962)$,
+razorbill $(n=908)$,
+sooty shearwater $(n=871)$,
+laughing gull $(nl=856)$,
+long-tailed duck $(n=851)$,
+unidentified loon $(n=754)$,
+Bonaparte's gull $(n=708)$,
+unidentified scoter $(n=703)$,
+surf scoter $(n=678)$,
+black scoter $(n=669)$,
+unidentified tern $(n=619)$,
+unidentified alcid $(n=555)$,
+unidentified large gull $(n=553)$,
+unidentified bird $(n=543)$,
+ring-billed gull $(n=530)$,
+common eider $(n=528)$,
+white-winged scoter $(n=522)$,
+atlantic puffin $(n=403)$,
+red phalarope $(n=394)$,
+unidentified storm-petrel $(n=379)$,
+manx shearwater $(n=374)$,
+unidentified shearwater $(n=364)$,
+double-crested cormorant $(n=354)$,
+unidentified large alcid (razorbill or murre) $(n=330)$,
+unidentified small gull $(n=313)$,
+ubbg $(n=299)$,
+unidentified phalarope $(n=292)$,
+pomarine jaeger $(n=287)$,
+red-breasted merganser $(n=220)$,
+red-necked phalarope $(n=207)$,
+royal tern $(n=207)$,
+dark scoter $(n=199)$,
+unidentified small tern $(n=184)$,
+south polar skua $(n=169)$,
+bufflehead $(n=159)$,
+parasitic jaeger $(n=154)$,
+common murre $(n=153)$,
+unidentified diving/sea duck $(n=121)$,
+Forster's tern $(n=119)$,
+great skua $(n=117)$,
+unidentified merganser $(n=117)$,
+roseate tern $(n=115)$,
+arctic tern $(n=103)$,
+barn swallow $(n=99)$,
+unidentified cormorant $(n=99)$,
+lesser black-backed gull $(n=97)$,
+unidentified passerine $(n=97)$,
+brown pelican $(n=92)$,
+unidentified large tern $(n=91)$,
+unidentified skua $(n=89)$,
+unidentified shorebird $(n=87)$,
+Audubon's shearwater $(n=86)$,
+thick-billed murre $(n=83)$,
+common goldeneye $(n=82)$,
+unidentified jaeger $(n=78)$,
+black guillemot $(n=75)$,
+unidentified murre $(n=73)$,
+horned grebe $(n=65)$,
+unidentified grebe $(n=63)$,
+least tern $(n=61)$,
+unidentified scaup $(n=52)$,
+red-necked grebe $(n=49)$,
+American black duck $(n=47)$,
+unidentified goldeneye $(n=34)$,
+band-rumped storm-petrel $(n=23)$ and, finally,
+black-capped petrel $(n=3)$.
+
+While some marine bird species such as various types of gulls have been sighted at numerous locations, other species occurred only very rarely.
+At the same time, as we defined a minimum of at least $50$ marine birds per species as inclusion criteria, this limited number of locations equivalently implies that certain marine bird species appeared in groupings rather than as isolated birds or occurred only in a geographically strictly-limited habitat.
+An example of such only rarely observed species are black-capped petrels whose $50$ counted sighting have only been recorded at $n=3$ different locations.
+This reflects our expectations, as black-capped petrels have been classified as endangered species by the IUCN Red List of Threatened Species.
+Discovering the relevant subset of species whose spatial occurrence is linked to the spatial pattern of any endangered species  by means of a SDGM might provide new insights into multivariate interdependencies.
+This new insights might provide important knowledge for the conservation of endangered species and might assist to understand such phenomena from a global perspective on different natural environments.
+
+%============================================
+\section{Results}
+%============================================
+
 \end{document}

### 2017-01-30 paper1_jrss.tex
Updated itemize

@@
-\documentclass{statsoc}\usepackage[]{graphicx}\usepackage[]{color}
+\documentclass{statsoc}
+\usepackage[]{graphicx}
+\usepackage[]{color}
+
 %% maxwidth is the original width if it is less than linewidth
@@
 \usepackage{alltt}
+\usepackage{amsfonts,epsfig,eurosym, amsmath, amsthm,  blindtext, enumitem}
+\usepackage[latin1]{inputenc}
+\usepackage[T1]{fontenc}
+\usepackage{pdfsync}
+\usepackage{natbib}
+\usepackage{rotating}
+\usepackage[margin=40pt,font=small,labelfont=bf,format=plain,indention=0cm,textfont=it]{caption}
+\usepackage[normalem]{ulem}
+\usepackage{bbm}
+\usepackage{url}
 
@@
 \def\thefootnote{\fnsymbol{footnote}}\footnote[#1]{#2}\endgroup}
-
-\usepackage{amssymb, amsmath, blindtext, enumitem}
 
@@
 
-\title[Modeling dependencies in multivariate seabird distributions]{Modeling dependencies in multivariate seabird distributions: linking graphical models to social network analysis}
+\title[Modeling dependencies in multivariate seabird distributions]{Modeling dependencies in multivariate seabird distributions: linking spatial dependence graph models to centrality measures}
 \author[Author 1 {\it et al.}]{Author 1}
@@
 
-\keywords{Graphical modeling, Marked point process, Seabird distribution}
+\keywords{Graphical modeling, Species importance, Marked point process, Network centrality measures, Seabird distribution}
 %============================================
@@
 %============================================
+
+\begin{itemize}
+\item We estimate the conditional spatial dependence structure between different seabird species
+\item edges express the partial (pairwise) interrelation between two species conditional on al remaining species
+\item we omit to implement a formal test statistic as we assume that dependence might vary between species
+\item we set a threshold indicating weak/ intermediate partial effects
+\item we combine spatial dependence graph model with importance tools of social network analysis
+\item info can provide important insides for species conservation
+\item eg which are the most important species in the overall graph
+\end{itemize}
 
@@
 species: 
-Herring gull $(n=3978)$,
-greater shearwater $(n=3732)$,
-northern gannet $(n=3451)$,
-great black-backed gull $(n=3319)$,
-Wilson's storm-petrel $(n=2746)$,
-common loon $(n=1900)$,
-northern fulmar $(n=1688)$,
-red-throated loon $(n=1400)$,
-Cory's shearwater $(n=1138)$,
-Leach's storm-petrel $(n=1005)$,
-unidentified gull $(n=984)$,
-common tern $(n=982)$,
-black-legged kittiwake $(n=971)$,
-dovekie $(n=962)$,
-razorbill $(n=908)$,
-sooty shearwater $(n=871)$,
-laughing gull $(nl=856)$,
-long-tailed duck $(n=851)$,
-unidentified loon $(n=754)$,
-Bonaparte's gull $(n=708)$,
-unidentified scoter $(n=703)$,
-surf scoter $(n=678)$,
-black scoter $(n=669)$,
-unidentified tern $(n=619)$,
-unidentified alcid $(n=555)$,
-unidentified large gull $(n=553)$,
-unidentified bird $(n=543)$,
-ring-billed gull $(n=530)$,
-common eider $(n=528)$,
-white-winged scoter $(n=522)$,
-atlantic puffin $(n=403)$,
-red phalarope $(n=394)$,
-unidentified storm-petrel $(n=379)$,
-manx shearwater $(n=374)$,
-unidentified shearwater $(n=364)$,
-double-crested cormorant $(n=354)$,
-unidentified large alcid (razorbill or murre) $(n=330)$,
-unidentified small gull $(n=313)$,
-ubbg $(n=299)$,
-unidentified phalarope $(n=292)$,
-pomarine jaeger $(n=287)$,
-red-breasted merganser $(n=220)$,
-red-necked phalarope $(n=207)$,
-royal tern $(n=207)$,
-dark scoter $(n=199)$,
-unidentified small tern $(n=184)$,
-south polar skua $(n=169)$,
-bufflehead $(n=159)$,
-parasitic jaeger $(n=154)$,
-common murre $(n=153)$,
-unidentified diving/sea duck $(n=121)$,
-Forster's tern $(n=119)$,
-great skua $(n=117)$,
-unidentified merganser $(n=117)$,
-roseate tern $(n=115)$,
-arctic tern $(n=103)$,
-barn swallow $(n=99)$,
-unidentified cormorant $(n=99)$,
-lesser black-backed gull $(n=97)$,
-unidentified passerine $(n=97)$,
-brown pelican $(n=92)$,
-unidentified large tern $(n=91)$,
-unidentified skua $(n=89)$,
-unidentified shorebird $(n=87)$,
-Audubon's shearwater $(n=86)$,
-thick-billed murre $(n=83)$,
-common goldeneye $(n=82)$,
-unidentified jaeger $(n=78)$,
-black guillemot $(n=75)$,
-unidentified murre $(n=73)$,
-horned grebe $(n=65)$,
-unidentified grebe $(n=63)$,
-least tern $(n=61)$,
-unidentified scaup $(n=52)$,
-red-necked grebe $(n=49)$,
-American black duck $(n=47)$,
-unidentified goldeneye $(n=34)$,
-band-rumped storm-petrel $(n=23)$ and, finally,
+Herring gull $(n=3978)$, greater shearwater $(n=3732)$,
+northern gannet $(n=3451)$,great black-backed gull $(n=3319)$,Wilson's storm-petrel $(n=2746)$,common loon $(n=1900)$,northern fulmar, $(n=1688)$,red-throated loon $(n=1400)$,Cory's shearwater $(n=1138)$, Leach's storm-petrel $(n=1005)$,unidentified gull $(n=984)$,common tern $(n=982)$,black-legged kittiwake $(n=971)$,dovekie $(n=962)$,razorbill $(n=908)$, sooty shearwater $(n=871)$, laughing gull $(nl=856)$, long-tailed duck $(n=851)$,unidentified loon $(n=754)$, Bonaparte's gull $(n=708)$,unidentified scoter $(n=703)$, surf scoter $(n=678)$,
+black scoter $(n=669)$, unidentified tern $(n=619)$,
+unidentified alcid $(n=555)$, unidentified large gull $(n=553)$, unidentified bird $(n=543)$, ring-billed gull $(n=530)$, common eider $(n=528)$, white-winged scoter $(n=522)$, atlantic puffin $(n=403)$, red phalarope $(n=394)$, unidentified storm-petrel $(n=379)$, manx shearwater $(n=374)$, unidentified shearwater $(n=364)$, double-crested cormorant $(n=354)$, unidentified large alcid (razorbill or murre) $(n=330)$, unidentified small gull $(n=313)$,ubbg $(n=299)$,unidentified phalarope $(n=292)$,pomarine jaeger $(n=287)$,red-breasted merganser $(n=220)$,red-necked phalarope $(n=207)$,royal tern $(n=207)$,dark scoter $(n=199)$,unidentified small tern $(n=184)$,south polar skua $(n=169)$,bufflehead $(n=159)$,parasitic jaeger $(n=154)$,common murre $(n=153)$,unidentified diving/sea duck $(n=121)$,Forster's tern $(n=119)$,great skua $(n=117)$,unidentified merganser $(n=117)$,roseate tern $(n=115)$,arctic tern $(n=103)$,barn swallow $(n=99)$,unidentified cormorant $(n=99)$,lesser black-backed gull $(n=97)$,unidentified passerine $(n=97)$,brown pelican $(n=92)$,unidentified large tern $(n=91)$,unidentified skua $(n=89)$,unidentified shorebird $(n=87)$,Audubon's shearwater $(n=86)$,thick-billed murre $(n=83)$,common goldeneye $(n=82)$,unidentified jaeger $(n=78)$,black guillemot $(n=75)$,unidentified murre $(n=73)$,horned grebe $(n=65)$,unidentified grebe $(n=63)$,least tern $(n=61)$,unidentified scaup $(n=52)$,
+red-necked grebe $(n=49)$,American black duck $(n=47)$,unidentified goldeneye $(n=34)$,band-rumped storm-petrel $(n=23)$ and, finally,
 black-capped petrel $(n=3)$.
@@
 \section{Results}
-%============================================
+============================================
+
+$\star$ in general: important for species conservation: e.g. black-capped petrels only linked to unidentified goldeneyes, both listed as threatened species by IUCN.
+
+$\star$ most important species by means of the degree centrality are unidentified alcids, Arctic terns, barn swallows, red phalaropes, dovekies, buffleheads, brown pelicans, unidentified mergansers and great black-backed gulls.
+
+$\star$ these species are most often linked to alternative species (no. adjacent species)
+
+$\star$ buffleheads, royal terns, unidentified alcids, Arctic terns, common murres, barn swallows, greater shearwaters, manx shearwaters, Bonaparte's gulls and Northern gannets are the most important species by means of the betweenness centrality.
+
+$\star$ these species are most often intermediate species, that is most links from a to b path through these species
 

### 2017-02-08 paper1_jrss.tex
updaten refs and fixed def error

@@
 \usepackage[]{color}
+\let\proof\relax 
+\let\endproof\relax
 
@@
   Graphical modeling of seabird distributions.
+Simultaneous estimation of conditional spatial interrelation for a subset of $79$ seabird species by means of a spatial dependence graph model (SDGM).
+Linkage to Social network analysis toolbox to detect the most influential species (in term of importance within the estimated SDGM)
 \end{abstract}
@@
 \item We estimate the conditional spatial dependence structure between different seabird species
+\item that is, structural dependence between two patterns conditional on all remaining patterns
+\item so not interrelation between points $i$ and $j$, but interrelations between components $i$ and $j$ where $i$ and $j$ are sets of points within a bounded planar region.
 \item edges express the partial (pairwise) interrelation between two species conditional on al remaining species
@@
 %============================================
+
+Primary idea by \cite{Eckardt2016}, extension to multivariate spp with quantitative marks by \cite{Eckardt2016b}
+
+Analysis was carried out using the \texttt{sdgm} R package of \cite{Eckardt2016a}.
 
@@
 \section{Results}
-============================================
+%============================================
 
@@
 
+\bibliographystyle{rss}
+\bibliography{lit}
 \end{document}

### 2017-02-22 paper1_jrss.Rnw
some paragraph

@@
 
-%\usepackage{fullpage}
-\usepackage{setspace}
-\usepackage[left=1in,top=1in,right=1in]{geometry}
-\pdfpagewidth 8.5in
-\pdfpageheight 11in 
-\setlength{\textheight}{9in}
+%\usepackage{geometry}
+\usepackage{fullpage}
+%\usepackage{setspace}
+%\usepackage[left=1in,top=1in,right=1in]{geometry}
+%\pdfpagewidth 8.5in
+%\pdfpageheight 11in
 
@@
 \bibpunct{(}{)}{;}{a}{}{,}
-%\linespread{1.5}
+\linespread{1.5}
 
@@
 
-\usepackage{fancyhdr}
-\pagestyle{fancy}
+%\usepackage{fancyhdr}
+%\pagestyle{fancy}
 
 %\lhead{\footnotesize \parbox{11cm}{Custom left-head-note} }
-\cfoot{}
-\lfoot{\footnotesize \parbox{11cm}{}}
-\rfoot{\footnotesize Page \thepage\ }
+%\cfoot{}
+%\lfoot{\footnotesize \parbox{11cm}{}}
+%\rfoot{\footnotesize Page \thepage\ }
 %\rfoot{\footnotesize Page \thepage\ of \pageref{LastPage}}
 %\renewcommand\headheight{24pt}
-\renewcommand\footrulewidth{0.4pt}
+%\renewcommand\footrulewidth{0.4pt}
 
@@
 \title[Graphical modeling of seabird distributions]{Graphical modeling of seabird distributions}
-\author[Author 1 {\it et al.}]{Author 1}
+\author[Author 1 {\it et al.}]{Matthias Eckhardt}
 \address{Affiliation,
@@
 \email{Author@emailaddress.com}
-\author{Author 2}
-\address{Affiliation,
-         City,
-         Country.}
+\author{Earvin Balderama}
+\address{Loyola University Chicago,
+         Chicago, IL,
+         USA.}
 
@@
   Graphical modeling of seabird distributions.
+Simultaneous estimation of conditional spatial interrelation for a subset of $79$ seabird species by means of a spatial dependence graph model (SDGM).
+Linkage to Social network analysis toolbox to detect the most influential species (in term of importance within the estimated SDGM)
 \end{abstract}
 
-\keywords{Graphical modeling, Marked point process, Seabird distribution}
+\keywords{Graphical modeling, Species importance, Marked point process, Network centrality measures, Seabird distribution}
 %============================================
@@
 
+Information on the distribution of sea birds, especially in the form of maps, is of particular interest to ecologists, environmentalists and policy-makers.
+Maps conveying the spatial and temporal distribution over the US Mid- and Northeast-Atlantic ocean regions were created by Balderama et al.~(2016) for individual species of sea bird and sea duck.
+
+It is generally known that species distributions are not independent.
+The occurrence of a sea bird species in a particular location is affected (either positively or negatively) by the occurrence of other species in the same location.
+
+This is very important in terms of Thus, external factors that may cause changes to the distribution of a single species will undoubtedly have effects on the distribution of other species.
+Determining these associations between different species has been difficult (CITATIONS), especially when trying to associate many species all at once.
+
+However, a multivariate analysis of sea bird distribution would be very useful in
+
+\begin{itemize}
+\item We estimate the conditional spatial dependence structure between different seabird species
+\item that is, structural dependence between two patterns conditional on all remaining patterns
+\item so not interrelation between points $i$ and $j$, but interrelations between components $i$ and $j$ where $i$ and $j$ are sets of points within a bounded planar region.
+\item edges express the partial (pairwise) interrelation between two species conditional on al remaining species
+\item we omit to implement a formal test statistic as we assume that dependence might vary between species
+\item we set a threshold indicating weak/ intermediate partial effects
+\item we combine spatial dependence graph model with importance tools of social network analysis
+\item info can provide important insides for species conservation
+\item eg which are the most important species in the overall graph
+\end{itemize}
+
 %============================================
@@
 
+Primary idea by \cite{Eckardt2016}, extension to multivariate spp with quantitative marks by \cite{Eckardt2016b}
+
+Analysis was carried out using the \texttt{sdgm} R package of \cite{Eckardt2016a}.
+
+%============================================
+\section{Data}
+%============================================
+
+species: 
+Herring gull $(n=3978)$, greater shearwater $(n=3732)$,
+northern gannet $(n=3451)$,great black-backed gull $(n=3319)$,Wilson's storm-petrel $(n=2746)$,common loon $(n=1900)$,northern fulmar, $(n=1688)$,red-throated loon $(n=1400)$,Cory's shearwater $(n=1138)$, Leach's storm-petrel $(n=1005)$,unidentified gull $(n=984)$,common tern $(n=982)$,black-legged kittiwake $(n=971)$,dovekie $(n=962)$,razorbill $(n=908)$, sooty shearwater $(n=871)$, laughing gull $(nl=856)$, long-tailed duck $(n=851)$,unidentified loon $(n=754)$, Bonaparte's gull $(n=708)$,unidentified scoter $(n=703)$, surf scoter $(n=678)$,
+black scoter $(n=669)$, unidentified tern $(n=619)$,
+unidentified alcid $(n=555)$, unidentified large gull $(n=553)$, unidentified bird $(n=543)$, ring-billed gull $(n=530)$, common eider $(n=528)$, white-winged scoter $(n=522)$, atlantic puffin $(n=403)$, red phalarope $(n=394)$, unidentified storm-petrel $(n=379)$, manx shearwater $(n=374)$, unidentified shearwater $(n=364)$, double-crested cormorant $(n=354)$, unidentified large alcid (razorbill or murre) $(n=330)$, unidentified small gull $(n=313)$,ubbg $(n=299)$,unidentified phalarope $(n=292)$,pomarine jaeger $(n=287)$,red-breasted merganser $(n=220)$,red-necked phalarope $(n=207)$,royal tern $(n=207)$,dark scoter $(n=199)$,unidentified small tern $(n=184)$,south polar skua $(n=169)$,bufflehead $(n=159)$,parasitic jaeger $(n=154)$,common murre $(n=153)$,unidentified diving/sea duck $(n=121)$,Forster's tern $(n=119)$,great skua $(n=117)$,unidentified merganser $(n=117)$,roseate tern $(n=115)$,arctic tern $(n=103)$,barn swallow $(n=99)$,unidentified cormorant $(n=99)$,lesser black-backed gull $(n=97)$,unidentified passerine $(n=97)$,brown pelican $(n=92)$,unidentified large tern $(n=91)$,unidentified skua $(n=89)$,unidentified shorebird $(n=87)$,Audubon's shearwater $(n=86)$,thick-billed murre $(n=83)$,common goldeneye $(n=82)$,unidentified jaeger $(n=78)$,black guillemot $(n=75)$,unidentified murre $(n=73)$,horned grebe $(n=65)$,unidentified grebe $(n=63)$,least tern $(n=61)$,unidentified scaup $(n=52)$,
+red-necked grebe $(n=49)$,American black duck $(n=47)$,unidentified goldeneye $(n=34)$,band-rumped storm-petrel $(n=23)$ and, finally,
+black-capped petrel $(n=3)$.
+
+While some marine bird species such as various types of gulls have been sighted at numerous locations, other species occurred only very rarely.
+At the same time, as we defined a minimum of at least $50$ marine birds per species as inclusion criteria, this limited number of locations equivalently implies that certain marine bird species appeared in groupings rather than as isolated birds or occurred only in a geographically strictly-limited habitat.
+An example of such only rarely observed species are black-capped petrels whose $50$ counted sighting have only been recorded at $n=3$ different locations.
+This reflects our expectations, as black-capped petrels have been classified as endangered species by the IUCN Red List of Threatened Species.
+Discovering the relevant subset of species whose spatial occurrence is linked to the spatial pattern of any endangered species  by means of a SDGM might provide new insights into multivariate interdependencies.
+This new insights might provide important knowledge for the conservation of endangered species and might assist to understand such phenomena from a global perspective on different natural environments.
+
+%============================================
+\section{Results}
+%============================================
+
+$\star$ in general: important for species conservation: e.g. black-capped petrels only linked to unidentified goldeneyes, both listed as threatened species by IUCN.
+
+$\star$ most important species by means of the degree centrality are unidentified alcids, Arctic terns, barn swallows, red phalaropes, dovekies, buffleheads, brown pelicans, unidentified mergansers and great black-backed gulls.
+
+$\star$ these species are most often linked to alternative species (no. adjacent species)
+
+$\star$ buffleheads, royal terns, unidentified alcids, Arctic terns, common murres, barn swallows, greater shearwaters, manx shearwaters, Bonaparte's gulls and Northern gannets are the most important species by means of the betweenness centrality.
+
+$\star$ these species are most often intermediate species, that is most links from a to b path through these species
+
+\bibliographystyle{rss}
+\bibliography{lit}
 \end{document}

### 2017-02-22 paper1_jrss.tex
some paragraph

@@
-\documentclass{statsoc}
-\usepackage[]{graphicx}
-\usepackage[]{color}
-\let\proof\relax 
-\let\endproof\relax
-
+\documentclass{statsoc}\usepackage[]{graphicx}\usepackage[]{color}
 %% maxwidth is the original width if it is less than linewidth
@@
 \usepackage{alltt}
-\usepackage{amsfonts,epsfig,eurosym, amsmath, amsthm,  blindtext, enumitem}
-\usepackage[latin1]{inputenc}
-\usepackage[T1]{fontenc}
-\usepackage{pdfsync}
-\usepackage{natbib}
-\usepackage{rotating}
-\usepackage[margin=40pt,font=small,labelfont=bf,format=plain,indention=0cm,textfont=it]{caption}
-\usepackage[normalem]{ulem}
-\usepackage{bbm}
-\usepackage{url}
 
@@
 \def\thefootnote{\fnsymbol{footnote}}\footnote[#1]{#2}\endgroup}
+
+\usepackage{amssymb, amsmath, blindtext, enumitem}
 
@@
 
-\title[Modeling dependencies in multivariate seabird distributions]{Modeling dependencies in multivariate seabird distributions: linking spatial dependence graph models to centrality measures}
-\author[Author 1 {\it et al.}]{Author 1}
+\title[Graphical modeling of seabird distributions]{Graphical modeling of seabird distributions}
+\author[Author 1 {\it et al.}]{Matthias Eckhardt}
 \address{Affiliation,
@@
 %============================================
+\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
 \IfFileExists{upquote.sty}{\usepackage{upquote}}{}
@@
 %============================================
+
+Information on the distribution of sea birds, especially in the form of maps, is of particular interest to ecologists, environmentalists and policy-makers.
+Maps conveying the spatial and temporal distribution over the US Mid- and Northeast-Atlantic ocean regions were created by Balderama et al.~(2016) for individual species of sea bird and sea duck.
+
+It is generally known that species distributions are not independent.
+The occurrence of a sea bird species in a particular location is affected (either positively or negatively) by the occurrence of other species in the same location.
+
+This is very important in terms of Thus, external factors that may cause changes to the distribution of a single species will undoubtedly have effects on the distribution of other species.
+Determining these associations between different species has been difficult (CITATIONS), especially when trying to associate many species all at once.
+
+However, a multivariate analysis of sea bird distribution would be very useful in
 

### 2017-06-14 paper1_jrss.tex
draft intro and some citations

@@
-\documentclass{statsoc}\usepackage[]{graphicx}\usepackage[]{color}
-%% maxwidth is the original width if it is less than linewidth
-%% otherwise use linewidth (to make sure the graphics do not exceed the margin)
-\makeatletter
-\def\maxwidth{ %
-  \ifdim\Gin@nat@width>\linewidth
-    \linewidth
-  \else
-    \Gin@nat@width
-  \fi
-}
-\makeatother
-
-\definecolor{fgcolor}{rgb}{0.345, 0.345, 0.345}
-\newcommand{\hlnum}[1]{\textcolor[rgb]{0.686,0.059,0.569}{#1}}%
-\newcommand{\hlstr}[1]{\textcolor[rgb]{0.192,0.494,0.8}{#1}}%
-\newcommand{\hlcom}[1]{\textcolor[rgb]{0.678,0.584,0.686}{\textit{#1}}}%
-\newcommand{\hlopt}[1]{\textcolor[rgb]{0,0,0}{#1}}%
-\newcommand{\hlstd}[1]{\textcolor[rgb]{0.345,0.345,0.345}{#1}}%
-\newcommand{\hlkwa}[1]{\textcolor[rgb]{0.161,0.373,0.58}{\textbf{#1}}}%
-\newcommand{\hlkwb}[1]{\textcolor[rgb]{0.69,0.353,0.396}{#1}}%
-\newcommand{\hlkwc}[1]{\textcolor[rgb]{0.333,0.667,0.333}{#1}}%
-\newcommand{\hlkwd}[1]{\textcolor[rgb]{0.737,0.353,0.396}{\textbf{#1}}}%
-\let\hlipl\hlkwb
-
-\usepackage{framed}
-\makeatletter
-\newenvironment{kframe}{%
- \def\at@end@of@kframe{}%
- \ifinner\ifhmode%
-  \def\at@end@of@kframe{\end{minipage}}%
-  \begin{minipage}{\columnwidth}%
- \fi\fi%
- \def\FrameCommand##1{\hskip\@totalleftmargin \hskip-\fboxsep
- \colorbox{shadecolor}{##1}\hskip-\fboxsep
-     % There is no \\@totalrightmargin, so:
-     \hskip-\linewidth \hskip-\@totalleftmargin \hskip\columnwidth}%
- \MakeFramed {\advance\hsize-\width
-   \@totalleftmargin\z@ \linewidth\hsize
-   \@setminipage}}%
- {\par\unskip\endMakeFramed%
- \at@end@of@kframe}
-\makeatother
-
-\definecolor{shadecolor}{rgb}{.97, .97, .97}
-\definecolor{messagecolor}{rgb}{0, 0, 0}
-\definecolor{warningcolor}{rgb}{1, 0, 1}
-\definecolor{errorcolor}{rgb}{1, 0, 0}
-\newenvironment{knitrout}{}{} % an empty environment to be redefined in TeX
-
-\usepackage{alltt}
+\documentclass{statsoc}
 
@@
 \usepackage{amssymb, amsmath, blindtext, enumitem}
+
+\usepackage{longtable}
 
@@
 \IfFileExists{upquote.sty}{\usepackage{upquote}}{}
-\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
 \begin{document}%\linenumbers
@@
 
-Information on the distribution of sea birds, especially in the form of maps, is of particular interest to ecologists, environmentalists and policy-makers.
-Maps conveying the spatial and temporal distribution over the US Mid- and Northeast-Atlantic ocean regions were created by Balderama et al.~(2016) for individual species of sea bird and sea duck.
-
-It is generally known that species distributions are not independent.
 The occurrence of a sea bird species in a particular location is affected (either positively or negatively) by the occurrence of other species in the same location. 
-
-This is very important in terms of Thus, external factors that may cause changes to the distribution of a single species will undoubtedly have effects on the distribution of other species.
+Thus, external factors that may cause changes to the distribution of a single species will undoubtedly have an effect on the distribution of other species.
 Determining these associations between different species has been difficult (CITATIONS), especially when trying to associate many species all at once.
 
-However, a multivariate analysis of sea bird distribution would be very useful in
+Quantifying the spatial dependence structure between bird species and environmental covariates is important.
+While studies have related the spatial distribution of one species with that of a prey or predator species, or of environmental variables acting as proxies for climate \citep{Goyert2014, Goyert2016}, there has been relatively few studies that investigate and utilize measures of inter-species dependence.
 
+Community models may combine several species, known to have facilitative interactions with each other, into one model \citep{Goyert2016, Sollmann2016}.
+However, these models treat the observed data the same way as if the observations are of only one species.
+
+Studying the degree of interaction between species may help inform ocean planning.
+Mapping the distribution of rare and endangered avian species is important when planning the placement of offshore wind farms.
+Such rare species are obviously difficult to monitor, so finding a more commonly occuring species that is highly dependent with the rare species has ecological importance.
+
+Attempts at modeling between-species interactions are often limited to the bivariate case \citep{Andersen1992, Nightingale2015}.
+For three or more species, models are usually hindered by computing time due to the estimation of very many interaction parameters \citep{Jalilian2015}.
+
+Ecological data usually contains spatial observations from multiple species of interest.
+
+There is a need for fast and practically applicable methods for analysing multivariate point patterns, and is currently a growing but challenging topic for researchers \citep{Moller2016}.
+
+Information on the distribution of sea birds, especially in the form of maps, is of particular interest to ecologists, environmentalists and policy-makers.
+Maps conveying the spatial and temporal distribution over the US Mid- and Northeast-Atlantic ocean regions were created by \cite{Balderama2016} for several individual species of marine birds.
+
+Models are usually run on inidivudal species. 
+%There is a danger in this, in that it doesn't take into account the dependence structure between species. 
+There is a danger in this in that tt is generally known that species distributions are not independent.
+Maps of the spatial distribution of marine birds undoubetedly have some overlap
+
+However, a multivariate analysis of sea bird distribution would be very useful in determining how bird species affect one another's presence.
+
+This will also help us to categorize observations of unidentified or unknown species to those of identified species.
+
+%It creates a false sense that a species distribution is independent
+
+%Models are usually run on either indivudual species or all-species-combined data.
+
+There are several advantages with this approach:
+
+1. These observations are usually removed before analyzing data at the species level.
+
+Here we include these locations of unknown species and from the results may be able to determine what species they are more likely to be from the resulting network map.
+
+%============================================
+\section{Data}
+%============================================
+
+Data are point locations of marine bird sightings over the Northeast- and Mid-Atlantic coast regions of the United States, as described in \cite{Balderama2016}.
+The point locations are the longitude and latitude coordinates of the midpoints of line transect segments from boat and aerial surveys between July, 1998 and April, 2014.
+Species are labelled by its common name and a four-letter species code.
+Names that include the word ``unidentified'' accommodate birds identified to a family but not to a species.
+
+Table~\ref{tab:species} shows a summary of the observed data by species code and common name. There are 79 different codes. However, some codes signify an unidentified or partially identified species.
+
+%\afterpage{
+{\scriptsize
+\begin{longtable}{| l | c | c | c | c | c | c | }
+\caption{Summary of observed data by species code.}
+\label{tab:species}\\
+\hline
+  &   &  &   &   &   &  \\ 
+\textbf{Species code}  & \textbf{Common name}  & \textbf{sightings}  &\textbf{average mark}  &\textbf{}  &\textbf{}  &\textbf{}   \\ 
+\hline
+ABDU &  American Black Duck & 47 & 1.25 &  &  &  \\ 
+ARTE &  Arctic Tern & 103 & 0.94 &  &   &  \\ 
+ATPU &  Atlantic Puffin & 403 & 1.17 &   &  &  \\ 
+AUSH &  Audubon's Shearwater & 86 & 1.20 &   &  &  \\ 
+BRSP &  Band-rumped Storm-petrel & 23   & 0.29 &  &  &  \\ 
+BARS &  Barn Swallow & 99 & 0.34 &  &  &    \\ 
+BCPE &  Black-capped Petrel & 3 & 1.56  &    &  &  \\ 
+BLKI &  Black-legged Kittiwake & 971 & 1.45 &  &  &  \\ 
+BLGU &  Black Guillemot & 75 & 0.42  &  &  &  \\ 
+BLSC &  Black Scoter & 669 & 4.31 &  &   &  \\ 
+BOGU &  Bonaparte's Gull & 708 & 0.99 &  &   &  \\ 
+BRPE &  Brown Pelican & 92 & 0.29 &  &  &   \\ 
+BUFF &  Bufflehead & 159 & 1.86 &  &  &  \\ 
+COEI &  Common Eider & 528 & 59.74 &  &    &  \\ 
+COGO &  Common Goldeneye & 82 & 1.25 &    &  &  \\ 
+COLO &  Common Loon & 1900 & 0.51 &   &  &  \\ 
+COMU &  Common Murre & 153 & 0.88  &   &  &  \\ 
+COTE &  Common Tern & 982 & 1.80 &  &   &  \\ 
+COSH &  Cory's Shearwater & 1138 & 2.69 &  &  &  \\ 
+DASC &  Dark Scoter (Black or Surf) & 199 & 2.09 &  &  &   \\ 
+DCCO &  Double-crested Cormorant & 354 & 2.37 &  &  &  \\ 
+DOVE &  Dovekie & 962 & 5.73 &  &  &    \\ 
+FOTE &  Forster's Tern & 119 & 0.52 &  &    &  \\ 
+GBBG &  Great Black-backed Gull & 3319 & 2.46  &  &   &  \\ 
+UBBG &  Great or Lesser Black-backed Gull & 299 & 0.18 &  &   &  \\ 
+GRSH &  Great Shearwater & 3732 & 8.99 &  &  &   \\ 
+GRSK &  Great Skua & 117 & 0.61 &  &  & \\ 
+HERG &  Herring Gull & 3978 & 2.71 &  &  &  \\ 
+HOGR &  Horned Grebe & 65 & 0.07 &  &  &  \\ 
+LAGU &  Laughing Gull & 856  & 0.80 &  &   &  \\ 
+LESP &  Leach's Storm-petrel & 1005 & 3.63 &  &  &  \\ 
+LETE &  Least Tern & 61 & 0.27 &  &  &  \\ 
+LBBG &  Lesser Black-backed Gull & 97 & 0.30 &  &  &  \\ 
+LTDU &  Long-tailed Duck & 851 & 8.64 &  &  &    \\ 
+MASH &  Manx Shearwater & 374 & 0.92 &  &  &    \\ 
+NOFU &  Northern Fulmar & 1688 & 5.25 &  &  &   \\ 
+NOGA &  Northern Gannet & 3451 & 2.51 &  &  &   \\ 
+PAJA &  Parasitic Jaeger & 154 & 0.37 &  &  &   \\ 
+POJA &  Pomarine Jaeger & 287 & 0.70 &  &  &   \\ 
+RAZO &  Razorbill & 908 & 1.26 &  &  &   \\ 
+REPH &  Red Phalarope & 394 & 8.64 &  &  &  \\ 
+RBME &  Red-breasted Merganser & 220 & 0.78 &  &  &  \\ 
+RNGR &  Red-necked Grebe & 49 & 0.11 &  &  &    \\ 
+RNPH &  Red-necked Phalarope & 207 & 7.65 &  &  &    \\ 
+RTLO &  Red-throated Loon & 1400 & 0.59 &  &  &   \\ 
+RBGU &  Ring-billed Gull & 530 & 0.71 &  &  &   \\ 
+ROST &  Roseate Tern & 115 & 0.88 &  &  &    \\ 
+ROYT &  Royal Tern & 207 & 0.22 &  &  &    \\ 
+SOSH &  Sooty Shearwater & 871 & 6.69 &  &  &   \\ 
+SPSK &  South Polar Skua & 169 & 0.74  &  &  &  \\ 
+SUSC &  Surf Scoter & 678 & 4.96 &  &  &   \\ 
+TBMU &  Thick-billed Murre & 83 & 1.33 & &  &  \\ 
+UNAL &  Unidentified Alcid & 555 & 0.71 &  &  &  \\ 
+UNBI &  Unidentified Bird & 543 & 1.06 &  &  &  \\ 
+UNCO &  Unidentified Cormorant & 99 & 0.43  &  &  &  \\ 
+UNDD &  Unidentified Diving/Sea Duck & 121 & 0.80 &  &  &  \\ 
+UNGO &  Unidentified Goldeneye & 34 & 2.29 &  &  &  \\ 
+UNGR &  Unidentified Grebe & 63 & 0.06 &  &  &  \\ 
+UNGU &  Unidentified Gull & 984 & 2.98 &  &  &  \\ 
+UNJA &  Unidentified Jaeger & 78 & 0.46 & &  &  \\ 
+UNLA &  Unidentified Large Alcid (Razorbill or Murre) & 330 & 0.84 &  &  &  \\ 
+UNLG &  Unidentified Large Gull & 553 & 3.51  &  &  &  \\ 
+UNLT &  Unidentified Large Tern & 91 & 0.35 & &  &  \\ 
+UNLO &  Unidentified Loon & 754 & 0.64 &  &  &  \\ 
+UNME &  Unidentified Merganser & 117 & 0.97 &  &  &  \\ 
+UNMU &  Unidentified Murre & 73 & 1.98 & &  &  \\ 
+UNPA &  Unidentified Passerine & 97 & 0.47 &  &  &  \\ 
+UNPH &  Unidentified Phalarope & 292 & 28.47 &  &  &  \\ 
+SCAU &  Unidentified Scaup & 52 & 11.02  & &  &  \\ 
+UNSC &  Unidentified Scoter & 703 & 26.64 &  &  &  \\ 
+UNSH &  Unidentified Shearwater & 364 & 3.80 & &  &  \\ 
+SHOR &  Unidentified Shorebird & 87 & 1.96 &  &  &  \\ 
+UNSK &  Unidentified Skua & 89 & 0.67 &  &  &  \\ 
+UNSG &  Unidentified Small Gull & 313 & 0.38  &  &  &  \\ 
+UNST &  Unidentified Small Tern & 184 & 0.18 &  &  &  \\ 
+UNSP &  Unidentified Storm-petrel & 379 & 40.11 & &  &  \\ 
+UNTE &  Unidentified Tern & 619 & 2.62 &  &  &  \\ 
+WWSC &  White-winged Scoter & 522 & 2.78 &  &  &   \\ 
+WISP &  Wilson's Storm-petrel & 2746 & 6.88 &  &  &  \\ 
+\hline 
+\end{longtable}}
+%}
+
+While some marine bird species such as various types of gulls have been sighted at numerous locations, other species occurred only very rarely.
+At the same time, as we defined a minimum of at least $50$ marine birds per species as inclusion criteria, this limited number of locations equivalently implies that certain marine bird species appeared in groupings rather than as isolated birds or occurred only in a geographically strictly-limited habitat.
+An example of such only rarely observed species are black-capped petrels whose $50$ counted sighting have only been recorded at $n=3$ different locations.
+This reflects our expectations, as black-capped petrels have been classified as endangered species by the IUCN Red List of Threatened Species.
+Discovering the relevant subset of species whose spatial occurrence is linked to the spatial pattern of any endangered species  by means of a SDGM might provide new insights into multivariate interdependencies.
+This new insights might provide important knowledge for the conservation of endangered species and might assist to understand such phenomena from a global perspective on different natural environments.
+
+%============================================
+\section{Methods}
+%============================================
 \begin{itemize}
@@
 
-%============================================
-\section{Methods}
-%============================================
-
 Primary idea by \cite{Eckardt2016}, extension to multivariate spp with quantitative marks by \cite{Eckardt2016b}
@@
 Analysis was carried out using the \texttt{sdgm} R package of \cite{Eckardt2016a}.
-
-%============================================
-\section{Data}
-%============================================
-
-species: 
-Herring gull $(n=3978)$, greater shearwater $(n=3732)$,
-northern gannet $(n=3451)$,great black-backed gull $(n=3319)$,Wilson's storm-petrel $(n=2746)$,common loon $(n=1900)$,northern fulmar, $(n=1688)$,red-throated loon $(n=1400)$,Cory's shearwater $(n=1138)$, Leach's storm-petrel $(n=1005)$,unidentified gull $(n=984)$,common tern $(n=982)$,black-legged kittiwake $(n=971)$,dovekie $(n=962)$,razorbill $(n=908)$, sooty shearwater $(n=871)$, laughing gull $(nl=856)$, long-tailed duck $(n=851)$,unidentified loon $(n=754)$, Bonaparte's gull $(n=708)$,unidentified scoter $(n=703)$, surf scoter $(n=678)$,
-black scoter $(n=669)$, unidentified tern $(n=619)$,
-unidentified alcid $(n=555)$, unidentified large gull $(n=553)$, unidentified bird $(n=543)$, ring-billed gull $(n=530)$, common eider $(n=528)$, white-winged scoter $(n=522)$, atlantic puffin $(n=403)$, red phalarope $(n=394)$, unidentified storm-petrel $(n=379)$, manx shearwater $(n=374)$, unidentified shearwater $(n=364)$, double-crested cormorant $(n=354)$, unidentified large alcid (razorbill or murre) $(n=330)$, unidentified small gull $(n=313)$,ubbg $(n=299)$,unidentified phalarope $(n=292)$,pomarine jaeger $(n=287)$,red-breasted merganser $(n=220)$,red-necked phalarope $(n=207)$,royal tern $(n=207)$,dark scoter $(n=199)$,unidentified small tern $(n=184)$,south polar skua $(n=169)$,bufflehead $(n=159)$,parasitic jaeger $(n=154)$,common murre $(n=153)$,unidentified diving/sea duck $(n=121)$,Forster's tern $(n=119)$,great skua $(n=117)$,unidentified merganser $(n=117)$,roseate tern $(n=115)$,arctic tern $(n=103)$,barn swallow $(n=99)$,unidentified cormorant $(n=99)$,lesser black-backed gull $(n=97)$,unidentified passerine $(n=97)$,brown pelican $(n=92)$,unidentified large tern $(n=91)$,unidentified skua $(n=89)$,unidentified shorebird $(n=87)$,Audubon's shearwater $(n=86)$,thick-billed murre $(n=83)$,common goldeneye $(n=82)$,unidentified jaeger $(n=78)$,black guillemot $(n=75)$,unidentified murre $(n=73)$,horned grebe $(n=65)$,unidentified grebe $(n=63)$,least tern $(n=61)$,unidentified scaup $(n=52)$,
-red-necked grebe $(n=49)$,American black duck $(n=47)$,unidentified goldeneye $(n=34)$,band-rumped storm-petrel $(n=23)$ and, finally,
-black-capped petrel $(n=3)$.
-
-While some marine bird species such as various types of gulls have been sighted at numerous locations, other species occurred only very rarely.
-At the same time, as we defined a minimum of at least $50$ marine birds per species as inclusion criteria, this limited number of locations equivalently implies that certain marine bird species appeared in groupings rather than as isolated birds or occurred only in a geographically strictly-limited habitat.
-An example of such only rarely observed species are black-capped petrels whose $50$ counted sighting have only been recorded at $n=3$ different locations.
-This reflects our expectations, as black-capped petrels have been classified as endangered species by the IUCN Red List of Threatened Species.
-Discovering the relevant subset of species whose spatial occurrence is linked to the spatial pattern of any endangered species  by means of a SDGM might provide new insights into multivariate interdependencies.
-This new insights might provide important knowledge for the conservation of endangered species and might assist to understand such phenomena from a global perspective on different natural environments.
 
@@
 
+%============================================
+\section{Discussion}
+%============================================
+
+Methods for studying multivariate species distributions are still not well developed. Future research may focus on niche partitioning and finding common areas of species overlap.
+
+%%
+Identifying ecologically important areas for community assemblages is important in marine spatial planning (Ehler and Douvere 2009), and our study suggests that a diverse set of species may attract (or repel) each other to (or from) feeding areas.
+We recommend a synthesis of community and ecosystem approaches in applied conservation management, since facilitation and competition fundamentally shape dynamic environmental processes.
+
 \bibliographystyle{rss}

### 2017-07-03 paper1_jrss.tex
updated results

@@
 \usepackage{amssymb, amsmath, blindtext, enumitem}
-
+\usepackage{graphicx}
 \usepackage{longtable}
+\usepackage{dsfont}
+
+\usepackage{listings}
 
@@
 
-\title[Graphical modeling of seabird distributions]{Graphical modeling of seabird distributions}
-\author[Author 1 {\it et al.}]{Matthias Eckhardt}
-\address{Affiliation,
-City,
-         Country.}
+\title[Graphical modeling of seabird distributions]{Exploring dependencies of multivariate seabird distributions: Linking graphical models to social network analysis}
+\author[Author 1 {\it et al.}]{Matthias Eckardt}
+\address{Humboldt-Universit{\"a}t zu Berlin,
+Berlin,
+ Germany.}
 \email{Author@emailaddress.com}
@@
 Table~\ref{tab:species} shows a summary of the observed data by species code and common name. There are 79 different codes. However, some codes signify an unidentified or partially identified species.
+
+\textit{ For our analysis we considered  on 128812 locations on marine bird sightings related to 306 different marine birds.
+Form this data, we preselected a sample of 204 species which have have at least been observed at three locations.
+By this, our analysis covered 128674 different locations.}
+
+The observed planar point patterns for the $20$ most frequently recorded bird species is shown in Figure \ref{fig:birds20}.
+
+\begin{figure}
+\centering
+\makebox{\includegraphics[scale=0.45]{BirdsTop20.eps}}
+      \caption{\label{fig:birds20} Spatial point patterns of the $20$ most frequently observed marine bird species.}
+\end{figure}
+
+\textbf{Maybe reduce table to most frequent species, eg. top 20 birds}
 
@@
 %============================================
+
+data as multivariate marked spatial point process as defined in \cite{Eckardt2016b}.
+
+literature on point process
+\cite{Chiu2013}, \cite{Illian2008} and \cite{StoyanStoyan1994}.
+For a comprehensive treatment of various models and statistics for marks and points we refer the interested reader to \cite{Illian2008}, \cite{Baddeley2010} and \cite{WiegandMoloney2013}
+
 \begin{itemize}
@@
 
+For an intense description of different aspects of network analysis we refer the interested reader to \cite{Carrington2005}, \cite{Kolaczyk:2009} and \cite{Goldenberg:EtAl:2010}.
+
+Although graphical modelling and network analysis are two distinct fields and are in general treated separately, the conjunction of both fields could offer additional benefits for the analysis of multivariate spatial data.
+Especially for the analysis of high-dimensional spatial data one might be interested in the structural importance of a distinct node in a given SDGM.
+That is, how substantial is the impact of a certain node on the observed network structure.
+Queries of this type are covered by centrality measures which aim to value the importance of a distinct  node in the network.
+Although a rich methodological toolbox for the structural analysis of (social) network data exist, we only  we considered four different centrality measures: the degree, the closeness, the betweenness and the eigenvector centrality (cf.
+\cite{Borgatti2006, Freeman1979, Newman2004}).
+Although these measure are similar in spirit, they are different in detail and each of these three centrality measures formalizes a different concept of importance from a (social) network  perspective.
+
+\textbf{meaning}
+ Betweenness centrality measures the number of shortest paths
+going through a specific vertex
+
+Closeness is the mean geodesic distance between a given node and
+ all other nodes with paths from the given node to the other
+ node. This is close to being the mean shortest path, but 
+geodesic distances give higher values for more central nodes.
+
+ Eigenvector centrality gives greater weight to a node the more 
+ it is connected to other highly connected nodes. A node
+ connected to five high-scoring nodes will have higher 
+ eigenvector centrality than a node connected to five low-scoring
+ nodes. Thus, it is often interpreted as measuring a node's
+ network
+
+For our analysis we estimated all marked auto- and cross-spectral densities for all $204$ species nonparametrically using a discrete Fourier transform of the demeaned mark values.
+Form this, we computed separate spectra density matrices of dimension $204 \times 204$ for all frequencies.
+To obtain the mSDGM, we finally inverted and rescaled each matrix such that an edge in the mSDGM is equivalent to non-vanishing absolute rescaled marked inverse spectral value in at least one frequency.
+To capture variation in strength of spatial interdependencies in our data, we choose two arbitrary thresholds $\alpha$ for the edges below of which we assume two patterns as conditional uncorrelated.
+That is, as our data contains a wide range of differently-sized of marine bird species we assume a variation in strength of spatial interrelations between different types of trees.
+A similar idea has been proposed by \cite{GatherImhoffFried2002} with respect to intensive care monitoring.
+
+computed two different mSDGMs by using two thresholds $\alpha=0.3$ and $\alpha=0.6$.
+
 %============================================
@@
 
+For our first mSDGM, we considered a threshold $\alpha=0.3$ which we interpret as a conditional interrelation of weak effect size.
+For this, we treated all values of the empirical absolute rescaled marked inverse spectra below $\alpha=0.3$ as zero.
+The resulting mSDGM  is depicted in Figure \ref{fig:g30}.
+
+\begin{figure}
+\centering
+\makebox{\includegraphics[scale=0.5]{rawg30.eps}}
+      \caption{\label{fig:g30} Marked spatial dependence graph model for the $204$ different marine bird species, and bird counts as quantitative mark for a threshold level of $\alpha=0.3$.}
+\end{figure}
+
+This SDGM consisted of two $4$-node subgraphs, a $6$- node subgraph and a $153$-node subgraph and of 3400 edges.
+Besides, we also found $37$ isolated species (AMCO, AMPI, AMRE, BAOR, BLPW, BRAN, BTBW, BUPE, COYE, FEPE, GCKI, GRCA, LESC, LISH, MABO, MAWA, MERL, NOFL, NOHA NOTE, NOWA, PEFA, RBTR, RCKI, RTHU, RUBL, SAVS, SNBU, SPAR, Surf Scoter, UNHU, UNPT, UNTB, USAN, WTSP, YBCH, YWAR).
+These findings imply that non of the $37$ species are interrelated to any other species taken into account at threshold $\alpha=.3$.
+This could mean that the isolated nodes tend to represent species whose marked point patterns are different from all remaining marked point patterns taken into account.
+This is an interesting result as the isolated nodes are related to both frequent and endangered species and also differently-sized types of marine birds.
+One reason for this could be due to our sample scheme.
+We restricted the dataset to a subset of $204$ different marine bird species, so while there probably are interrelations of this $37$ aerial species to alternative types of birds, the alternative birds did not appear in our subsample.
+However, the global interrelations within coastal habitat are very complex and are still not completely understood.
+
+Although several findings could be discussed in detail, we only considered structural interdependies for the marked patterns of Roseate Tern, Least Tern and the endangered species Black-capped Petrel, GBHE, YCNH and SAVS.
+
+We begin our discussion with the structural interrelations for Roseate Tern and Least Tern.
+While we found $62$ conditionally interrelated marked patterns for Roseate Tern, we only observed $10$ interdependent species for Least Tern.
+For Roseate Tern, these species are Dovekie, AMGO, AMKE, AMOY, AMRO, BBPL, BHCO, BHGU, Red-necked Phalarope, Red Phalarope, BRBO, CHSW, DUNL, EUST, Forster's Tern, SBDO, GRYE, HADU, HOME, LEYE, NOPI, MALL,  Manx Shearwater, PAWA, PEEP, PESA, PISI, RBNU, REDH, RUDU, RUTU, SAGU, SATE, Unidentified Scaup, Pomarine Jaeger, Red-breasted Merganser, Ring-billed Gull, Great or Lesser Black-backed Gull, UCAT, UNBI, UNFR, UNPE, Unidentified Large Alcid , Unidentified Large Gull, Unidentified Merganser, Unidentified Small Tern, BANS, WHIM, GREG, MODO, Unidentified Storm-petrel, WIPH, WODU, YCNH, YRWA, BRSP, BLKI, Black-capped Petrel,   BonapArctic Tern's Gull, BRNO, Common Goldeneye and Dark Scoter.
+For Least Tern we have edges to   Common Murre, Barn Swallow, Arctic Tern, Unidentified Cormorant, Unidentified Shorebird, Unidentified Diving/Sea Duck, South Polar Skua, Unidentified Grebe, Black Guillemotand, Parasitic Jaeger.
+
+For GBHE we observed $74$ direct interrelations to alternative marine birds, namely AMGO, AMKE, AMOY, AMRO, BBPL, BHCO, BHGU, GRCO, BRBO, CATE, CHSW, COME, DEJU, DUNL, EUST,  GADW, GRHE, SBDO, GRYE, HADU, HOME, LESA, LEYE,
+LIGU, NOPI, HEPE, ICGU, LTJA, MALL, OSPR,  PAWA, PEEP, PESA, PISI, PUMA, PUSA, RBNU, REDH,  RUDU, RUTU, RWBL, SAGU, SAND, SATE, SEPL,
+ SESA, SOSP, SPSA, TRES, UCAT, ULSB, UNEI, UNFR, UNPE, BANS, UNWA, MYWA, WFSP, WHIM, GLGU,  GOME, GREG, MODO, BRTE, WILL, WIPH, WODU, YCNH, YRWA, UCRT, BLTE, BRNO, CANG, and, lastly, AWPE.
+\textbf{These birds are .....}.
+
+Similarly, focussing on the interrelation which are present for YCNH, we found $79$ links.
+These interdependent species are  AWPE, Common Loon, Dovekie, Great Black-backed Gull, AMGO, AMKE, AMOY, AMRO, BBPL, BHCO, BHGU, Great Shearwater, Roseate Tern, BRBO, CHSW, COME, DEJU, DUNL, EUST, GADW, GRHE, GBHE, SBDO, GRYE,  HADU, HOME, LESA, LEYE, NOPI, ICGU, Laughing Gull, MALL, OSPR, PAWA, PEEP, PESA, PISI, PUSA, RBNU
+ REDH, RUDU, RUTU, RWBL, SAGU, SATE, Unidentified Scaup, SEPL, SESA, SOSP, Pomarine Jaeger, Ring-billed Gull, SPSA, TRES, UCAT  ULSB, UNBI, UNEI, UNFR, UNPE, Unidentified Large Gull, Unidentified Merganser, Unidentified Small Tern, BANS, WFSP, WHIM, GLGU, GOME, GREG, MODO, WILL, WIPH, WODU, YRWA, UCRT, BLKI, Black-capped Petrel,   BonapArctic Tern's Gull, BRNO and CANG.\textbf{These birds are .....}.
+
+For Black-capped Petrel, we found 64 alternative marked point patterns which are directly interrelated to the spatial marked pattern of Black-capped Petrel. These species are 
+  Dovekie, AMGO, AMKE, AMOY, AMRO, BBPL, BHCO, BHGU, Red-necked Phalarope, Red Phalarope, Roseate Tern, BRBO, CHSW, DUNL, EUST, Forster's Tern, SBDO, GRYE, HADU, HOME, LEYE, NOPI, Horned Grebe, Laughing Gull, MALL,  Manx Shearwater, PAWA, PESA, PISI, RBNU,  REDH, RUDU, RUTU, SAGU, SATE, Unidentified Scaup, Pomarine Jaeger, Red-breasted Merganser,  Ring-billed Gull, Sooty Shearwater, Great or Lesser Black-backed Gull, UCAT, UNBI, UNFR, UNPE,
+ Unidentified Large Alcid , Unidentified Large Gull, Unidentified Merganser, Unidentified Small Tern, BANS, WHIM, GREG, MODO,  Unidentified Storm-petrel, WIPH, WODU, YCNH, YRWA, BRSP, BLKI,
+   BonapArctic Tern's Gull, BRNO, Common Goldeneye, and Dark Scoter. \textbf{These birds are .....}.
+
+\textbf{Interestingly, SAVS is isolated in both SDGMs}
+
+These findings imply the presence of complex conditional interdependencies between the marked spatial pattern of GBHF and also YCNH to a wide range of alternative species whereas we found no spatial interdependencies for SAVS to any alternative species taken into account.
+
+As a second model, we also computed a SDGM for a threshold $\alpha=.6$. (we interprete this as interdependencies of intermediate effect size). The resulting mSDGM is depicted in Figure \ref{fig:g60}.
+
+\begin{figure}
+\centering
+\makebox{\includegraphics[scale=0.5]{rawg60.eps}}
+      \caption{\label{fig:g60} Marked spatial dependence graph model for the $204$ different marine bird species, and bird counts as quantitative mark for a threshold level of $\alpha=0.3$.}
+\end{figure}
+
+In this SGDM, we observed two pairs of joined nodes, a $3$-node subgraph, a $4$-node subgraph, a $6$-node subgraph, a $7$-node subgraph, a $8$-node subgraph, a $10$-node subgraph, a $49$-node subgraph and a , a $4$-node subgraph, a $6$-node subgraph, a $71$-node subgraph and $1880$ edges.
+In addition, we also found $42$ isolated nodes, namely AMCO, AMPI, AMRE, BAOR, BLPW, BRAN, BTBW, BUPE, COYE, FEPE, GCKI, GRCA, Herring Gull, LESC, LISH, MABO, MAFR, MAWA, MERL, NOFL, NOHA, NOTE, NOWA, PEFA, RBTR, RCKI, RTHU, RUBL, SAVS, SNBU, SPAR, Surf Scoter, SWAL, UNDU, UNHU, Unidentified Passerine, UNPT, UNTB, USAN, WTSP, YBCH, YWAR.
+Again, for the isolated nodes, we concluded that non of marked spatial patterns of these species is conditionally interdependent to any alternative marked pattern taken into account at a threshold $\alpha=.6$.
+
+As before, we first discuss the spatial interdependencies for Roseate Tern and Least Tern.
+In contrast to our previous findings, only $13$ edges remain for Roseate Tern at a threshold $\alpha=.6$, namely Red-necked Phalarope, Forster's Tern, Unidentified Scaup, Pomarine Jaeger, Ring-billed Gull, Unidentified Merganser, Unidentified Small Tern, BRSP, BLKI, Black-capped Petrel,   BonapArctic Tern's Gull, Common Goldeneye, and Dark Scoter.
+
+Least Tern is linked to 7 from 204 species, named:
+   Common Murre Arctic Tern Unidentified Cormorant Unidentified Diving/Sea Duck South Polar Skua Black GuillemotParasitic Jaeger
+
+\textbf{ .....}
+
+With respect to the marked spatial pattern of GBHE, the neighborhood consisted of $41$ alternative species, namely AWPEBANS, BHCO, BHGU,  BLTE,  CATE, CANG, CHSW, COME, DEJU, DUNL, GLGU, GOME, GRCO, LESA, LIGU, ICGU, LTJA, MALL, MODO, MYWA, OSPR, PAWA, PEEP, PUMA, REDH, RUTU, RWBL, SAND, SEPL, SESA, SOSP, TRES, UNEI, UNFR, UNPE,  UNWA, YRWA, WFSP, WHIM, and WODU.
+
+\textbf{...}
+
+For YCNH we detected $52$ interrelated species at a threshold $\alpha=.6$. 
+  AMGO, AMKE, AMOY, AMRO, BBPL, BHCO, BHGU, BRBO, CHSW, COME, DUNL, EUST, SBDO, GRYE, HADU, HOME, LESA, LEYE, NOPI, ICGU, MALL, OSPR, PAWA, PEEP, PESA, PISI, RBNU, REDH, RUDU, RUTU, RWBL, SAGU, SATE, SEPL, SESA, SOSP,
+ UCAT, UNEI, UNFR, UNPE, BANS, WFSP, WHIM, GOME, GREG,
+ MODO, WIPH, WODU, YRWA, BRNO, CANG and AWPE.
+
+\textbf{...}
+
+Similarly, only $13$ conditional interdependencies remained with respect to the marked pattern of  Black-capped Petrelfor a threshold $\alpha=.6$ including the marked point patterns of Red-necked Phalarope, Roseate Tern, Forster's Tern, Unidentified Scaup, Pomarine Jaeger, Ring-billed Gull, Unidentified Merganser, Unidentified Small Tern, BRSP, BLKI,   BonapArctic Tern's Gull, Common Goldeneye and also Dark Scoter.
+
+To detect the most influential species within our data, we compute 4 different centrality measures (listed Table \ref{tab:centrality:measures}).
+The results for the threshold $\alpha=.3$ are listed below, isolated species excluded.
+
+\begin{table}
+\caption{\label{tab:centrality:measures}Centrality measures for SDGM for threshold $\alpha=.3$. Isolated nodes excluded.}
+\centering
+\fbox{%
+\begin{tabular}{*{5}{c}}
+\em code &\em degree &\em betweenness &\em closeness &\em eigen\\
+\hline
+MALL  &  $80$  &  $80.370354$  &  $9.37E-05$  &  $1.000000e+00$\\
+BANS  &  $80$  &  $80.370354$  &  $9.37E-05$  &  $1.000000e+00$\\
+WHIM  &  $80$  &  $80.370354$  &  $9.37E-05$  &  $1.000000e+00$\\
+WODU  &  $80$  &  $80.370354$  &  $9.37E-05$  &  $1.000000e+00$\\
+AMKE  &  $79$  &  $64.521344$  &  $9.37E-05$  &  $9.930130e-01$\\
+AMRO  &  $79$  &  $64.521344$  &  $9.37E-05$  &  $9.930130e-01$\\
+BBPL  &  $79$  &  $64.521344$  &  $9.37E-05$  &  $9.930130e-01$\\
+BHCO  &  $79$  &  $74.852463$  &  $9.37E-05$  &  $9.917427e-01$\\
+BRBO  &  $79$  &  $64.521344$  &  $9.37E-05$  &  $9.930130e-01$\\
+CHSW  &  $79$  &  $64.521344$  &  $9.37E-05$  &  $9.930130e-01$\\
+EUST  &  $79$  &  $64.521344$  &  $9.37E-05$  &  $9.930130e-01$\\
+SBDO  &  $79$  &  $64.521344$  &  $9.37E-05$  &  $9.930130e-01$\\
+GRYE  &  $79$  &  $64.521344$  &  $9.37E-05$  &  $9.930130e-01$\\
+HADU  &  $79$  &  $64.521344$  &  $9.37E-05$  &  $9.930130e-01$\\
+HOME  &  $79$  &  $64.521344$  &  $9.37E-05$  &  $9.930130e-01$\\
+LEYE  &  $79$  &  $64.521344$  &  $9.37E-05$  &  $9.930130e-01$\\
+NOPI  &  $79$  &  $64.521344$  &  $9.37E-05$  &  $9.930130e-01$\\
+PAWA  &  $79$  &  $64.521344$  &  $9.37E-05$  &  $9.930130e-01$\\
+PESA  &  $79$  &  $64.521344$  &  $9.37E-05$  &  $9.930130e-01$\\
+PISI  &  $79$  &  $64.521344$  &  $9.37E-05$  &  $9.930130e-01$\\
+RBNU  &  $79$  &  $64.521344$  &  $9.37E-05$  &  $9.930130e-01$\\
+RUDU  &  $79$  &  $64.521344$  &  $9.37E-05$  &  $9.930130e-01$\\
+RUTU  &  $79$  &  $64.521344$  &  $9.37E-05$  &  $9.930130e-01$\\
+SAGU  &  $79$  &  $64.521344$  &  $9.37E-05$  &  $9.930130e-01$\\
+SATE  &  $79$  &  $64.521344$  &  $9.37E-05$  &  $9.930130e-01$\\
+UNFR  &  $79$  &  $64.521344$  &  $9.37E-05$  &  $9.930130e-01$\\
+UNPE  &  $79$  &  $74.852463$  &  $9.37E-05$  &  $9.917427e-01$\\
+GREG  &  $79$  &  $64.521344$  &  $9.37E-05$  &  $9.930130e-01$\\
+WIPH  &  $79$  &  $64.521344$  &  $9.37E-05$  &  $9.930130e-01$\\
+YCNH  &  $79$  &  $64.521344$  &  $9.37E-05$  &  $9.930130e-01$\\
+BRNO  &  $79$  &  $64.521344$  &  $9.37E-05$  &  $9.930130e-01$\\
+BHGU  &  $78$  &  $70.510241$  &  $9.37E-05$  &  $9.829660e-01$\\
+DUNL  &  $78$  &  $70.510241$  &  $9.37E-05$  &  $9.829660e-01$\\
+REDH  &  $78$  &  $70.510241$  &  $9.37E-05$  &  $9.829660e-01$\\
+MODO  &  $78$  &  $70.510241$  &  $9.37E-05$  &  $9.829660e-01$\\
+YRWA  &  $78$  &  $70.510241$  &  $9.37E-05$  &  $9.829660e-01$\\
+TRES  &  $76$  &  $396.293914$  &  $9.32E-05$  &  $8.710167e-01$\\
+SOSP  &  $75$  &  $45.678051$  &  $9.36E-05$  &  $9.546329e-01$\\
+UNEI  &  $75$  &  $45.678051$  &  $9.36E-05$  &  $9.546329e-01$\\
+DEJU  &  $74$  &  $191.068166$  &  $9.32E-05$  &  $8.695110e-01$\\
+GBHE  &  $74$  &  $226.132882$  &  $9.32E-05$  &  $8.697880e-01$\\
+GLGU  &  $74$  &  $191.068166$  &  $9.32E-05$  &  $8.695110e-01$\\
+LESA  &  $73$  &  $125.782452$  &  $9.31E-05$  &  $8.690015e-01$\\
+OSPR  &  $73$  &  $125.782452$  &  $9.31E-05$  &  $8.690015e-01$\\
+AMGO  &  $72$  &  $49.578329$  &  $9.36E-05$  &  $9.162885e-01$\\
+AMOY  &  $72$  &  $49.578329$  &  $9.36E-05$  &  $9.162885e-01$\\
+COME  &  $72$  &  $104.948978$  &  $9.31E-05$  &  $8.675207e-01$\\
+UCAT  &  $72$  &  $49.578329$  &  $9.36E-05$  &  $9.162885e-01$\\
+WFSP  &  $72$  &  $104.948978$  &  $9.31E-05$  &  $8.675207e-01$\\
+RWBL  &  $70$  &  $22.730622$  &  $9.34E-05$  &  $9.053099e-01$\\
+SEPL  &  $70$  &  $22.730622$  &  $9.34E-05$  &  $9.053099e-01$\\
+AWPE  &  $70$  &  $22.730622$  &  $9.34E-05$  &  $9.053099e-01$\\
+PEEP  &  $69$  &  $38.941332$  &  $9.35E-05$  &  $8.863426e-01$\\
+SESA  &  $69$  &  $56.090039$  &  $9.31E-05$  &  $8.620495e-01$\\
+GOME  &  $69$  &  $56.090039$  &  $9.31E-05$  &  $8.620495e-01$\\
+UNST  &  $66$  &  $864.535742$  &  $9.35E-05$  &  $7.261004e-01$\\
+UNBI  &  $65$  &  $162.419996$  &  $9.35E-05$  &  $7.316740e-01$\\
+LAGU  &  $64$  &  $388.758703$  &  $9.35E-05$  &  $6.854566e-01$\\
+POJA  &  $64$  &  $157.699639$  &  $9.34E-05$  &  $7.174345e-01$\\
+BCPE  &  $64$  &  $979.935364$  &  $9.36E-05$  &  $6.892403e-01$\\
+CANG  &  $64$  &  $23.269845$  &  $9.35E-05$  &  $8.382226e-01$\\
+GBBG  &  $63$  &  $511.095976$  &  $9.35E-05$  &  $6.644262e-01$\\
+SCAU  &  $63$  &  $429.075802$  &  $9.35E-05$  &  $7.079279e-01$\\
+RBGU  &  $63$  &  $174.4483$  &  $9.35E-05$  &  $7.533343e-01$\\
+UNME  &  $63$  &  $153.685067$  &  $9.34E-05$  &  $7.091772e-01$\\
+BOGU  &  $63$  &  $174.4483$  &  $9.35E-05$  &  $7.533343e-01$\\
+ROST  &  $62$  &  $148.609153$  &  $9.34E-05$  &  $6.905912e-01$\\
+BLKI  &  $62$  &  $165.552583$  &  $9.34E-05$  &  $7.510736e-01$\\
+COLO  &  $60$  &  $454.304315$  &  $9.34E-05$  &  $6.354029e-01$\\
+GADW  &  $59$  &  $1.436417$  &  $9.30E-05$  &  $7.795919e-01$\\
+GRHE  &  $59$  &  $1.436417$  &  $9.30E-05$  &  $7.795919e-01$\\
+PUSA  &  $59$  &  $1.436417$  &  $9.30E-05$  &  $7.795919e-01$\\
+SPSA  &  $59$  &  $1.436417$  &  $9.30E-05$  &  $7.795919e-01$\\
+ULSB  &  $59$  &  $1.436417$  &  $9.30E-05$  &  $7.795919e-01$\\
+WILL  &  $59$  &  $1.436417$  &  $9.30E-05$  &  $7.795919e-01$\\
+UCRT  &  $59$  &  $1.436417$  &  $9.30E-05$  &  $7.795919e-01$\\
+ICGU  &  $58$  &  $1.649017$  &  $9.30E-05$  &  $7.766811e-01$\\
+UNLG  &  $58$  &  $157.442443$  &  $9.34E-05$  &  $6.242535e-01$\\
+DOVE  &  $56$  &  $194.321598$  &  $9.34E-05$  &  $5.873140e-01$\\
+GRSH  &  $48$  &  $288.105101$  &  $9.33E-05$  &  $4.697169e-01$\\
+LIGU  &  $48$  &  $123.565465$  &  $9.29E-05$  &  $4.833385e-01$\\
+MYWA  &  $48$  &  $123.565465$  &  $9.29E-05$  &  $4.833385e-01$\\
+BRSP  &  $28$  &  $407.588982$  &  $9.30E-05$  &  $1.731580e-01$\\
+RNPH  &  $27$  &  $53.421704$  &  $9.29E-05$  &  $1.731189e-01$\\
+UNSP  &  $27$  &  $49.85151$  &  $9.29E-05$  &  $1.549736e-01$\\
+COGO  &  $26$  &  $39.864962$  &  $9.29E-05$  &  $1.722011e-01$\\
+CATE  &  $24$  &  $25.047311$  &  $9.21E-05$  &  $1.539562e-01$\\
+FOTE  &  $24$  &  $24.555419$  &  $9.29E-05$  &  $1.607928e-01$\\
+BLTE  &  $24$  &  $25.047311$  &  $9.21E-05$  &  $1.539562e-01$\\
+LTJA  &  $23$  &  $22.428263$  &  $9.21E-05$  &  $1.534467e-01$\\
+UNWA  &  $23$  &  $22.428263$  &  $9.21E-05$  &  $1.534467e-01$\\
+DASC  &  $23$  &  $246.349381$  &  $9.29E-05$  &  $1.550616e-01$\\
+GRCO  &  $22$  &  $19.270691$  &  $9.21E-05$  &  $1.297163e-01$\\
+PUMA  &  $22$  &  $19.270691$  &  $9.21E-05$  &  $1.297163e-01$\\
+SAND  &  $22$  &  $19.270691$  &  $9.21E-05$  &  $1.297163e-01$\\
+SOSH  &  $22$  &  $35.136566$  &  $9.28E-05$  &  $9.390908e-02$\\
+UNDD  &  $21$  &  $431.447758$  &  $9.29E-05$  &  $6.035436e-02$\\
+UNLT  &  $21$  &  $20.900229$  &  $9.28E-05$  &  $8.421874e-02$\\
+BRTE  &  $20$  &  $14.69234$  &  $9.21E-05$  &  $1.053226e-01$\\
+UNCO  &  $19$  &  $410.715654$  &  $9.28E-05$  &  $6.528103e-02$\\
+BLSC  &  $18$  &  $428.995063$  &  $9.28E-05$  &  $7.086913e-02$\\
+DCCO  &  $18$  &  $245.042857$  &  $9.27E-05$  &  $6.999939e-02$\\
+LTDU  &  $17$  &  $41.640397$  &  $9.27E-05$  &  $7.254790e-02$\\
+NOGA  &  $17$  &  $160.237757$  &  $9.27E-05$  &  $5.381070e-02$\\
+HEPE  &  $16$  &  $155.745163$  &  $9.20E-05$  &  $5.593917e-02$\\
+MASH  &  $16$  &  $90.089212$  &  $9.27E-05$  &  $6.768689e-02$\\
+REPH  &  $15$  &  $59.456976$  &  $9.27E-05$  &  $6.550681e-02$\\
+RBME  &  $15$  &  $59.456976$  &  $9.27E-05$  &  $6.550681e-02$\\
+UBBG  &  $15$  &  $59.456976$  &  $9.27E-05$  &  $6.550681e-02$\\
+UNLA  &  $15$  &  $59.456976$  &  $9.27E-05$  &  $6.550681e-02$\\
+ABDU  &  $14$  &  $2.912409$  &  $9.20E-05$  &  $4.369921e-02$\\
+WTTR  &  $14$  &  $2.912409$  &  $9.20E-05$  &  $4.369921e-02$\\
+COMU  &  $13$  &  $133.71799$  &  $9.20E-05$  &  $3.216736e-03$\\
+RAZO  &  $13$  &  $368.994253$  &  $9.25E-05$  &  $3.164179e-02$\\
+BARS  &  $12$  &  $207.723894$  &  $9.17E-05$  &  $3.455434e-04$\\
+SPSK  &  $12$  &  $53.468537$  &  $9.20E-05$  &  $4.227004e-03$\\
+UNGR  &  $12$  &  $207.723894$  &  $9.17E-05$  &  $3.455434e-04$\\
+UNSG  &  $12$  &  $224.536021$  &  $9.24E-05$  &  $1.560035e-02$\\
+BRPE  &  $12$  &  $224.536021$  &  $9.24E-05$  &  $1.560035e-02$\\
+RNGR  &  $11$  &  $0$  &  $9.09E-05$  &  $1.786223e-02$\\
+SHOR  &  $11$  &  $174.360858$  &  $9.16E-05$  &  $3.003178e-04$\\
+ATPU  &  $11$  &  $39.152444$  &  $9.16E-05$  &  $5.391765e-03$\\
+ARTE  &  $10$  &  $39.727535$  &  $9.19E-05$  &  $1.996873e-03$\\
+GRSK  &  $10$  &  $268.176822$  &  $9.20E-05$  &  $2.782868e-03$\\
+LESP  &  $10$  &  $310.367803$  &  $9.25E-05$  &  $3.691295e-02$\\
+LETE  &  $10$  &  $39.727535$  &  $9.19E-05$  &  $1.996873e-03$\\
+HOGR  &  $9$  &  $720.079655$  &  $9.27E-05$  &  $1.088519e-02$\\
+SOTE  &  $9$  &  $132.848369$  &  $9.20E-05$  &  $2.527661e-03$\\
+AUSH  &  $9$  &  $3.172553$  &  $9.23E-05$  &  $1.557767e-02$\\
+LBBG  &  $8$  &  $21.656632$  &  $9.09E-05$  &  $9.112791e-05$\\
+MAFR  &  $8$  &  $0$  &  $9.20E-05$  &  $3.624032e-02$\\
+TBMU  &  $8$  &  $149$  &  $9.05E-05$  &  $1.647815e-05$\\
+UNSK  &  $8$  &  $149$  &  $9.05E-05$  &  $1.647815e-05$\\
+BLGU  &  $8$  &  $151$  &  $9.18E-05$  &  $1.983332e-03$\\
+COSH  &  $7$  &  $89.976832$  &  $9.17E-05$  &  $1.506881e-03$\\
+UNJA  &  $7$  &  $10.767651$  &  $9.09E-05$  &  $5.559037e-05$\\
+UNTE  &  $7$  &  $89.976832$  &  $9.17E-05$  &  $1.506881e-03$\\
+PAJA  &  $7$  &  $0$  &  $9.18E-05$  &  $1.982934e-03$\\
+ROYT  &  $6$  &  $23.486786$  &  $9.12E-05$  &  $5.376720e-04$\\
+WWSC  &  $6$  &  $23.564037$  &  $9.15E-05$  &  $5.104993e-04$\\
+UNPH  &  $6$  &  $23.486786$  &  $9.12E-05$  &  $5.376720e-04$\\
+UNSH  &  $6$  &  $23.486786$  &  $9.12E-05$  &  $5.376720e-04$\\
+CEDW  &  $5$  &  $0$  &  $2.48E-05$  &  $0.000000e+00$\\
+GBTE  &  $5$  &  $0$  &  $2.48E-05$  &  $0.000000e+00$\\
+SNGO  &  $5$  &  $0$  &  $2.48E-05$  &  $0.000000e+00$\\
+UNEG  &  $5$  &  $0$  &  $2.48E-05$  &  $0.000000e+00$\\
+UNSA  &  $5$  &  $0$  &  $2.48E-05$  &  $0.000000e+00$\\
+UNFI  &  $5$  &  $0$  &  $2.48E-05$  &  $0.000000e+00$\\
+COTE  &  $5$  &  $74.509944$  &  $9.15E-05$  &  $5.842575e-04$\\
+WISP  &  $5$  &  $12.356908$  &  $9.13E-05$  &  $5.022849e-04$\\
+RTLO  &  $4$  &  $0$  &  $9.05E-05$  &  $5.741835e-05$\\
+UNAL  &  $4$  &  $25.213789$  &  $9.05E-05$  &  $3.724320e-05$\\
+UNSC  &  $3$  &  $0$  &  $2.45E-05$  &  $0.000000e+00$\\
+GRSC  &  $3$  &  $0$  &  $2.45E-05$  &  $0.000000e+00$\\
+GWTE  &  $3$  &  $0$  &  $2.45E-05$  &  $0.000000e+00$\\
+UNGO  &  $3$  &  $0$  &  $8.93E-05$  &  $4.767535e-07$\\
+UNDU  &  $3$  &  $0$  &  $2.45E-05$  &  $0.000000e+00$\\
+UNGU  &  $3$  &  $0$  &  $2.45E-05$  &  $0.000000e+00$\\
+UNLO  &  $3$  &  $0$  &  $2.45E-05$  &  $0.000000e+00$\\
+UNMU  &  $3$  &  $0$  &  $8.93E-05$  &  $4.767535e-07$\\
+USSB  &  $3$  &  $0$  &  $2.45E-05$  &  $0.000000e+00$\\
+COEI  &  $3$  &  $0$  &  $2.45E-05$  &  $0.000000e+00$\\
+NOFU  &  $2$  &  $0$  &  $9.13E-05$  &  $5.347083e-04$\\
+BUFF  &  $2$  &  $99.767649$  &  $9.15E-05$  &  $9.987188e-04$\\
+UNPA  &  $1$  &  $0$  &  $9.05E-05$  &  $2.828221e-05$\\
+SWAL  &  $1$  &  $0$  &  $9.08E-05$  &  $7.976898e-04$\\
+HERG  &  $1$  &  $0$  &  $9.15E-05$  &  $7.673378e-04$\\
+\end{tabular}}
+\end{table}
+
+betweenness centrality is shown in Figure \ref{fig:g30between}
+
+\begin{figure}
+\centering
+\makebox{\includegraphics[scale=0.5]{betweeng30.eps}}
+      \caption{\label{fig:g30between} Betweenness centrality for the marked spatial dependence graph model for the $204$ different marine bird species, and bird counts as quantitative mark for a threshold level of $\alpha=0.3$.
+ }
+\end{figure}
+
+For this plot, we found that BCPE is the most important marine bird species by means of the betweenness centrality measure.
+Besides BCPE, we observed a high importance of UNST, HOGR as well as GBBG amongst other species.
+
+Similar calculations have been performed for the threshold $\alpha=0.6$.
+
+ The results are given below, isolated species excluded.
+
+\begin{lstlisting}
+39     COME     58   49.987456 3.674174e-05 1.000000e+00
+59     LESA     58   49.987456 3.674174e-05 1.000000e+00
+82     OSPR     58   49.987456 3.674174e-05 1.000000e+00
+104    SESA     58   49.987456 3.674174e-05 1.000000e+00
+155    WFSP     58   49.987456 3.674174e-05 1.000000e+00
+160    GOME     58   49.987456 3.674174e-05 1.000000e+00
+74     ICGU     56   19.908538 3.673904e-05 9.943346e-01
+97     RWBL     56   19.908538 3.673904e-05 9.943346e-01
+103    SEPL     56   19.908538 3.673904e-05 9.943346e-01
+107    SOSP     56   19.908538 3.673904e-05 9.943346e-01
+123    UNEI     56   19.908538 3.673904e-05 9.943346e-01
+203    AWPE     56   19.908538 3.673904e-05 9.943346e-01
+23     BHCO     55    8.418041 3.673364e-05 9.894355e-01
+24     BHGU     55    8.418041 3.673364e-05 9.894355e-01
+42     DUNL     55    8.418041 3.673364e-05 9.894355e-01
+93     REDH     55    8.418041 3.673364e-05 9.894355e-01
+130    UNPE     55    8.418041 3.673364e-05 9.894355e-01
+163    MODO     55    8.418041 3.673364e-05 9.894355e-01
+175    YRWA     55    8.418041 3.673364e-05 9.894355e-01
+195    CANG     55    8.418041 3.673364e-05 9.894355e-01
+38     CHSW     53    4.526542 3.673095e-05 9.742804e-01
+79     MALL     53    4.526542 3.673095e-05 9.742804e-01
+83     PAWA     53    4.526542 3.673095e-05 9.742804e-01
+84     PEEP     53    4.526542 3.673095e-05 9.742804e-01
+96     RUTU     53    4.526542 3.673095e-05 9.742804e-01
+124    UNFR     53    4.526542 3.673095e-05 9.742804e-01
+150    BANS     53    4.526542 3.673095e-05 9.742804e-01
+156    WHIM     53    4.526542 3.673095e-05 9.742804e-01
+171    WODU     53    4.526542 3.673095e-05 9.742804e-01
+14     AMGO     52    0.000000 3.671746e-05 9.636128e-01
+15     AMKE     52    0.000000 3.671746e-05 9.636128e-01
+16     AMOY     52    0.000000 3.671746e-05 9.636128e-01
+19     AMRO     52    0.000000 3.671746e-05 9.636128e-01
+22     BBPL     52    0.000000 3.671746e-05 9.636128e-01
+35     BRBO     52    0.000000 3.671746e-05 9.636128e-01
+43     EUST     52    0.000000 3.671746e-05 9.636128e-01
+53     SBDO     52    0.000000 3.671746e-05 9.636128e-01
+54     GRYE     52    0.000000 3.671746e-05 9.636128e-01
+56     HADU     52    0.000000 3.671746e-05 9.636128e-01
+57     HOME     52    0.000000 3.671746e-05 9.636128e-01
+61     LEYE     52    0.000000 3.671746e-05 9.636128e-01
+69     NOPI     52    0.000000 3.671746e-05 9.636128e-01
+86     PESA     52    0.000000 3.671746e-05 9.636128e-01
+87     PISI     52    0.000000 3.671746e-05 9.636128e-01
+90     RBNU     52    0.000000 3.671746e-05 9.636128e-01
+95     RUDU     52    0.000000 3.671746e-05 9.636128e-01
+98     SAGU     52    0.000000 3.671746e-05 9.636128e-01
+100    SATE     52    0.000000 3.671746e-05 9.636128e-01
+118    UCAT     52    0.000000 3.671746e-05 9.636128e-01
+161    GREG     52    0.000000 3.671746e-05 9.636128e-01
+170    WIPH     52    0.000000 3.671746e-05 9.636128e-01
+174    YCNH     52    0.000000 3.671746e-05 9.636128e-01
+193    BRNO     52    0.000000 3.671746e-05 9.636128e-01
+52     GBHE     41  315.767672 3.672150e-05 5.731912e-01
+41     DEJU     26   18.848384 3.669994e-05 4.071560e-01
+116    TRES     26  170.399687 3.670264e-05 2.632387e-01
+159    GLGU     26   18.848384 3.669994e-05 4.071560e-01
+62     LIGU     20   75.510551 3.669455e-05 1.522058e-01
+154    MYWA     20   75.510551 3.669455e-05 1.522058e-01
+36     CATE     15   23.242211 3.665555e-05 4.061106e-02
+146    UNST     15  188.485579 3.148515e-05 1.989399e-16
+26     GRCO     14   23.098542 3.665420e-05 2.550392e-02
+72     HEPE     14   65.661463 3.663138e-05 1.484379e-02
+88     PUMA     14   23.098542 3.665420e-05 2.550392e-02
+99     SAND     14   23.098542 3.665420e-05 2.550392e-02
+142    UNME     14  137.727271 3.148416e-05 1.492049e-16
+191    BLTE     14   23.098542 3.665420e-05 2.550392e-02
+6      DOVE     13  111.950982 3.149309e-05 9.946995e-17
+29     RNPH     13   63.299561 3.149309e-05 1.492049e-16
+32     ROST     13   25.728846 3.147524e-05 4.973498e-17
+45     FOTE     13   63.299561 3.149309e-05 9.946995e-17
+120    UNBI     13   94.166508 3.149309e-05 4.973498e-17
+140    UNLG     13   82.258497 3.149210e-05 0.000000e+00
+151    UNWA     13    9.715423 3.665286e-05 2.545595e-02
+165    BRTE     13    7.718029 3.663004e-05 1.483630e-02
+167    UNSP     13  113.383211 3.149408e-05 0.000000e+00
+188    BRSP     13   63.299561 3.149309e-05 9.946995e-17
+190    BCPE     13   25.728846 3.147524e-05 4.973498e-17
+197    COGO     13   63.299561 3.149309e-05 1.492049e-16
+78     LTJA     12    1.513058 3.665152e-05 2.538510e-02
+112    SOSH     12  112.611727 3.148813e-05 4.973498e-17
+126    UNLT     12  112.611727 3.148813e-05 4.973498e-17
+202    DASC     12   45.798378 3.149110e-05 4.973498e-17
+108    POJA     11    7.328846 3.147326e-05 0.000000e+00
+185    BRPE     11   54.509180 3.144951e-05 9.946995e-17
+7      GBBG     10   38.630214 3.148020e-05 1.243374e-16
+31     REPH     10   39.426508 3.146138e-05 7.460246e-17
+80     MASH     10   39.426508 3.146138e-05 7.460246e-17
+109    RBME     10   39.426508 3.146138e-05 4.973498e-17
+139    UNLA     10   39.426508 3.146138e-05 4.973498e-17
+145    UNSG     10   19.096963 3.143666e-05 9.946995e-17
+148    WTTR     10    6.133804 3.657778e-05 3.806856e-03
+183    ATPU     10   42.362745 3.144852e-05 7.460246e-17
+1      BLSC      9   90.311158 3.147029e-05 4.973498e-17
+2      COLO      9   40.043107 3.147723e-05 7.460246e-17
+8      LTDU      9   90.311158 3.147029e-05 1.243374e-16
+117    UBBG      9   19.483694 3.146039e-05 9.946995e-17
+12     ABDU      8    3.277441 3.657243e-05 2.577287e-03
+27     GRSH      8   17.044593 3.147425e-05 4.973498e-17
+114    SHOR      8   11.666667 2.526146e-05 7.460246e-17
+3      COMU      7    1.000000 2.500563e-05 7.460246e-17
+25     ARTE      7    1.000000 2.500563e-05 4.973498e-17
+77     LETE      7    1.000000 2.500563e-05 0.000000e+00
+133    SPSK      7    1.000000 2.500563e-05 4.973498e-17
+179    AUSH      7    0.000000 3.143369e-05 7.460246e-17
+5      DCCO      6  175.595538 3.147524e-05 7.460246e-17
+21     BARS      6    2.416667 2.526018e-05 2.486749e-17
+46     GADW      6    0.000000 2.487934e-05 6.216872e-17
+50     GRHE      6    0.000000 2.487934e-05 8.703621e-17
+58     LBBG      6    4.000000 2.526018e-05 4.973498e-17
+75     LAGU      6    0.000000 3.146831e-05 2.486749e-17
+89     PUSA      6    0.000000 2.487934e-05 7.460246e-17
+102    SCAU      6    0.000000 3.146534e-05 2.486749e-17
+110    RBGU      6    3.511946 3.147128e-05 7.460246e-17
+115    SPSA      6    0.000000 2.487934e-05 2.486749e-17
+119    ULSB      6    0.000000 2.487934e-05 6.216872e-17
+137    UNGR      6    2.416667 2.526018e-05 3.730123e-17
+169    WILL      6    0.000000 2.487934e-05 6.216872e-17
+178    UCRT      6    0.000000 2.487934e-05 4.973498e-17
+189    BLKI      6    2.498296 3.146930e-05 4.973498e-17
+192    BOGU      6    3.511946 3.147128e-05 4.973498e-17
+33     UNCO      5    0.000000 2.500438e-05 4.973498e-17
+37     CEDW      5    0.000000 2.475431e-05 6.216872e-17
+47     GBTE      5    0.000000 2.475431e-05 6.216872e-17
+71     GRSK      5    0.750000 2.525954e-05 6.216872e-17
+106    SNGO      5    0.000000 2.475431e-05 4.973498e-17
+111    ROYT      5    2.753559 3.142184e-05 4.973498e-17
+113    SOTE      5    0.750000 2.525954e-05 4.973498e-17
+121    UNDD      5    0.000000 2.500438e-05 7.460246e-17
+122    UNEG      5    0.000000 2.475431e-05 3.730123e-17
+144    UNSA      5    0.000000 2.475431e-05 4.973498e-17
+177    UNFI      5    0.000000 2.475431e-05 3.730123e-17
+184    BLGU      5    0.000000 2.500438e-05 6.216872e-17
+187    PAJA      5    0.000000 2.500438e-05 3.730123e-17
+200    UNPH      5   94.621344 3.143962e-05 4.973498e-17
+201    UNSH      5    2.753559 3.142184e-05 3.730123e-17
+10     NOGA      4    0.000000 3.144654e-05 3.730123e-17
+28     RAZO      4  252.000000 3.144654e-05 3.730123e-17
+73     HOGR      4    0.000000 2.525699e-05 3.730123e-17
+129    UNJA      4    0.000000 2.525827e-05 3.730123e-17
+134    TBMU      4    0.000000 2.525827e-05 0.000000e+00
+166    UNSK      4    0.000000 2.525827e-05 2.486749e-17
+34     UNSC      3    0.000000 2.450800e-05 3.730123e-17
+94     RNGR      3    0.000000 3.654169e-05 4.025636e-04
+138    UNGU      3    0.000000 2.450800e-05 4.351810e-17
+141    UNLO      3    0.000000 2.450800e-05 4.351810e-17
+149    WWSC      3  135.000000 3.137058e-05 2.486749e-17
+168    UNTE      3  215.000000 3.140999e-05 4.351810e-17
+196    COEI      3    0.000000 2.450800e-05 3.730123e-17
+4      COSH      2    0.000000 3.136763e-05 3.108436e-17
+9      NOFU      2   47.000000 3.128422e-05 1.243374e-17
+51     GRSC      2    0.000000 2.438668e-05 2.486749e-17
+55     GWTE      2    0.000000 2.438668e-05 1.865062e-17
+135    UNAL      2   92.131464 3.143962e-05 2.486749e-17
+153    USSB      2    0.000000 2.438668e-05 1.243374e-17
+194    BUFF      2  105.144842 3.145445e-05 1.865062e-17
+198    COTE      2   92.000000 3.132832e-05 1.865062e-17
+30     RTLO      1    0.000000 2.426654e-05 9.325308e-18
+76     LESP      1    0.000000 3.123829e-05 9.325308e-18
+125    UNGO      1    0.000000 2.426654e-05 9.325308e-18
+143    UNMU      1    0.000000 2.426654e-05 6.216872e-18
+199    WISP      1    0.000000 2.426654e-05 6.216872e-18
+\end{lstlisting}
+
 %============================================
@@
 
+\subsection*{Neighbors for $\alpha=0.3$}
+
+We found the following structure for the threshold $\alpha=.3$
+\begin{lstlisting}
+species BLSC
+is linked to 18 from 204 species, named:
+  COLO COMU COSH DCCO DOVE GBBG LTDU NOGA 
+GRSH RAZO LAGU SOSH UNBI UNLT SPSK
+ UNLG UNSP UNTE
+
+species COLO
+is linked to 60 from 204 species
+  BLSC DCCO DOVE GBBG LTDU NOGA AMGO AMKE
+ AMOY AMRO BBPL BHCO BHGU GRSH RAZO
+ RNPH UNCO BRBO CHSW DUNL EUST FOTE SBDO
+ GRYE HADU HOME LEYE NOPI LAGU MALL
+ PAWA PEEP PESA PISI RBNU REDH RUDU RUTU
+ SAGU SATE SOSH UCAT UNBI UNDD UNFR
+ UNLT UNPE UNLG BANS WHIM GREG MODO UNSP 
+WIPH WODU YCNH YRWA BRSP BRNO COGO
+
+species COMU
+is linked to 13 from 204 species, named:
+  BLSC BARS ARTE UNCO GRSK HOGR LETE SOTE  
+  UNDD SPSK UNGR BLGU PAJA
+
+species COSH
+is linked to 7 from 204 species, named:
+ BLSC RAZO RTLO WWSC UNTE COTE WISP
+
+species DCCO
+is linked to 18 from 204 species, named:
+  BLSC COLO DOVE GBBG LTDU NOGA GRSH RAZO 
+RNPH FOTE LAGU SOSH UNLT UNLG UNSP
+ BRSP BUFF COGO
+
+species DOVE
+is linked to 56 from 204 species, named:
+  BLSC COLO DCCO GBBG LTDU AMGO AMKE AMOY 
+AMRO BBPL GRSH RNPH ROST UNCO BRBO
+ CHSW EUST FOTE SBDO GRYE HADU HOME LEYE 
+NOPI LAGU MALL PAWA PESA PISI RBNU
+ RUDU RUTU SAGU SATE POJA RBGU SOSH UCAT 
+UNBI UNFR UNLT UNLG BANS WHIM GREG
+ UNSP WIPH WODU YCNH BRSP BLKI BCPE BOGU BRNO COGO DASC
+
+species GBBG
+is linked to 63 from 204 species, named:
+  BLSC COLO DCCO DOVE LTDU NOGA AMGO AMKE AMOY
+ AMRO BBPL BHCO BHGU GRSH RAZO
+ RNPH UNCO BRBO CHSW DUNL EUST FOTE SBDO GRYE
+ HADU HOME LEYE NOPI LAGU MALL
+ PAWA PEEP PESA PISI RBNU REDH RUDU RUTU SAGU
+ SATE SOSP SOSH UCAT UNBI UNDD
+ UNEI UNFR UNLT UNPE UNLG BANS WHIM GREG MODO 
+UNSP WIPH WODU YCNH YRWA BRSP
+ BRNO COGO DASC
+
+species LTDU
+is linked to 17 from 204 species, named:
+  BLSC COLO DCCO DOVE GBBG NOGA GRSH RAZO UNCO 
+LAGU SOSH UNBI UNDD UNLT SPSK
+ UNLG UNSP
+
+species NOFU
+is linked to 2 from 204 species, named:
+ LESP COTE
+
+species NOGA
+is linked to 17 from 204 species, named:
+  BLSC COLO DCCO GBBG LTDU GRSH RAZO RNPH FOTE LAGU 
+SOSH UNDD UNLT UNSP HERG
+ BRSP COGO
+
+species SUSC
+is linked to 0 from 204 species
+
+species ABDU
+is linked to 14 from 204 species, named:
+  GRCO CATE LIGU HEPE LTJA PUMA RNGR SAND TRES
+ WTTR UNWA MYWA BRTE BLTE
+
+species AMCO
+is linked to 0 from 204 species
+
+species AMGO
+is linked to 72 from 204 species, named:
+  COLO DOVE GBBG AMKE AMOY AMRO BBPL BHCO BHGU
+ GRSH ROST BRBO CHSW COME DEJU
+ DUNL EUST GBHE SBDO GRYE HADU HOME LESA LEYE 
+NOPI ICGU LAGU MALL OSPR PAWA
+ PEEP PESA PISI RBNU REDH RUDU RUTU RWBL SAGU 
+SATE SCAU SEPL SESA SOSP POJA
+ RBGU TRES UCAT UNBI UNEI UNFR UNPE UNLG UNME 
+UNST BANS WFSP WHIM GLGU GOME
+ GREG MODO WIPH WODU YCNH YRWA BLKI BCPE BOGU BRNO 
+CANG AWPE
+
+species AMKE
+is linked to 79 from 204 species, named:
+  COLO DOVE GBBG AMGO AMOY AMRO BBPL BHCO
+ BHGU GRSH ROST BRBO CHSW COME DEJU
+ DUNL EUST GADW GRHE GBHE SBDO GRYE HADU 
+HOME LESA LEYE NOPI ICGU LAGU MALL
+ OSPR PAWA PEEP PESA PISI PUSA RBNU REDH 
+RUDU RUTU RWBL SAGU SATE SCAU SEPL
+ SESA SOSP POJA RBGU SPSA TRES UCAT ULSB 
+UNBI UNEI UNFR UNPE UNLG UNME UNST
+ BANS WFSP WHIM GLGU GOME GREG MODO WILL 
+WIPH WODU YCNH YRWA UCRT BLKI BCPE
+ BOGU BRNO CANG AWPE
+
+species AMOY
+is linked to 72 from 204 species, named:
+  COLO DOVE GBBG AMGO AMKE AMRO BBPL BHCO 
+BHGU GRSH ROST BRBO CHSW COME DEJU
+ DUNL EUST GBHE SBDO GRYE HADU HOME LESA 
+LEYE NOPI ICGU LAGU MALL OSPR PAWA
+ PEEP PESA PISI RBNU REDH RUDU RUTU RWBL 
+SAGU SATE SCAU SEPL SESA SOSP POJA
+ RBGU TRES UCAT UNBI UNEI UNFR UNPE UNLG 
+UNME UNST BANS WFSP WHIM GLGU GOME
+ GREG MODO WIPH WODU YCNH YRWA BLKI BCPE 
+BOGU BRNO CANG AWPE
+
+species AMPI
+is linked to 0 from 204 species
+
+species AMRE
+is linked to 0 from 204 species
+
+species AMRO
+is linked to 79 from 204 species, named:
+  COLO DOVE GBBG AMGO AMKE AMOY BBPL BHCO
+ BHGU GRSH ROST BRBO CHSW COME DEJU
+ DUNL EUST GADW GRHE GBHE SBDO GRYE HADU 
+HOME LESA LEYE NOPI ICGU LAGU MALL
+ OSPR PAWA PEEP PESA PISI PUSA RBNU REDH 
+RUDU RUTU RWBL SAGU SATE SCAU SEPL
+ SESA SOSP POJA RBGU SPSA TRES UCAT ULSB 
+UNBI UNEI UNFR UNPE UNLG UNME UNST
+ BANS WFSP WHIM GLGU GOME GREG MODO WILL 
+WIPH WODU YCNH YRWA UCRT BLKI BCPE
+ BOGU BRNO CANG AWPE
+
+species BAOR
+is linked to 0 from 204 species
+
+species BARS
+is linked to 12 from 204 species, named:
+  COMU ARTE LBBG GRSK HOGR LETE SOTE SHOR 
+UNJA TBMU UNGR UNSK
+
+species BBPL
+is linked to 79 from 204 species, named:
+  COLO DOVE GBBG AMGO AMKE AMOY AMRO BHCO 
+BHGU GRSH ROST BRBO CHSW COME DEJU
+ DUNL EUST GADW GRHE GBHE SBDO GRYE HADU 
+HOME LESA LEYE NOPI ICGU LAGU MALL
+ OSPR PAWA PEEP PESA PISI PUSA RBNU REDH 
+RUDU RUTU RWBL SAGU SATE SCAU SEPL
+ SESA SOSP POJA RBGU SPSA TRES UCAT ULSB 
+UNBI UNEI UNFR UNPE UNLG UNME UNST
+ BANS WFSP WHIM GLGU GOME GREG MODO WILL 
+WIPH WODU YCNH YRWA UCRT BLKI BCPE
+ BOGU BRNO CANG AWPE
+
+species BHCO
+is linked to 79 from 204 species, named:
+  COLO GBBG AMGO AMKE AMOY AMRO BBPL BHGU 
+ROST BRBO CHSW COME DEJU DUNL EUST
+ GADW GRHE GBHE SBDO GRYE HADU HOME LESA 
+LEYE LIGU NOPI ICGU LAGU MALL OSPR
+ PAWA PEEP PESA PISI PUSA RBNU REDH RUDU 
+RUTU RWBL SAGU SATE SCAU SEPL SESA
+ SOSP POJA RBGU SPSA TRES UCAT ULSB UNBI 
+UNEI UNFR UNPE UNLG UNME UNST BANS
+ MYWA WFSP WHIM GLGU GOME GREG MODO WILL 
+WIPH WODU YCNH YRWA UCRT BLKI BCPE
+ BOGU BRNO CANG AWPE
+
+species BHGU
+is linked to 78 from 204 species, named:
+  COLO GBBG AMGO AMKE AMOY AMRO BBPL BHCO 
+ROST BRBO CHSW COME DEJU DUNL EUST
+ GADW GRHE GBHE SBDO GRYE HADU HOME LESA 
+LEYE LIGU NOPI ICGU LAGU MALL OSPR
+ PAWA PEEP PESA PISI PUSA RBNU REDH RUDU 
+RUTU RWBL SAGU SATE SCAU SEPL SESA
+ SOSP POJA RBGU SPSA TRES UCAT ULSB UNBI
+ UNEI UNFR UNPE UNME UNST BANS MYWA
+ WFSP WHIM GLGU GOME GREG MODO WILL WIPH
+ WODU YCNH YRWA UCRT BLKI BCPE BOGU
+ BRNO CANG AWPE
+
+species ARTE
+is linked to 10 from 204 species
+  COMU BARS UNCO LETE SHOR UNDD 
+SPSK UNGR BLGU PAJA
+
+species GRCO
+is linked to 22 from 204 species, named:
+  ABDU CATE COME DEJU GBHE LESA LIGU MAFR 
+HEPE LTJA OSPR PUMA RNGR SAND TRES
+ WTTR UNWA MYWA WFSP GLGU BRTE BLTE
+
+species GRSH
+is linked to 48 from 204 species, named:
+  BLSC COLO DCCO DOVE GBBG LTDU NOGA AMGO 
+AMKE AMOY AMRO BBPL RAZO RNPH UNCO
+ BRBO CHSW EUST FOTE SBDO GRYE HADU HOME 
+LEYE NOPI LAGU PAWA PESA PISI RBNU
+ RUDU RUTU SAGU SATE SOSH UCAT UNBI UNDD 
+UNFR UNLT UNLG GREG UNSP WIPH YCNH
+ BRSP BRNO COGO
+
+species RAZO
+is linked to 13 from 204 species, named:
+  BLSC COLO COSH DCCO GBBG LTDU NOGA GRSH 
+SOSH UNLT WWSC UNTE WISP
+
+species RNPH
+is linked to 27 from 204 species, named:
+  COLO DCCO DOVE GBBG NOGA GRSH ROST UNCO FOTE
+ LAGU SCAU POJA RBGU SOSH UNBI
+ UNDD UNLT UNLG UNME UNST UNSP BRSP BLKI BCPE 
+BOGU COGO DASC
+
+species RTLO
+is linked to 4 from 204 species, named:
+ COSH WWSC UNTE WISP
+
+species REPH
+is linked to 15 from 204 species, named:
+  ROST LESP MASH SCAU POJA RBME UBBG UNLA UNME
+ UNSG UNST AUSH ATPU BRPE BCPE
+
+species ROST
+is linked to 62 from 204 species, named:
+  DOVE AMGO AMKE AMOY AMRO BBPL BHCO BHGU RNPH
+ REPH BRBO CHSW DUNL EUST FOTE
+ SBDO GRYE HADU HOME LEYE NOPI MALL MASH PAWA
+ PEEP PESA PISI RBNU REDH RUDU
+ RUTU SAGU SATE SCAU POJA RBME RBGU UBBG UCAT 
+UNBI UNFR UNPE UNLA UNLG UNME
+ UNST BANS WHIM GREG MODO UNSP WIPH WODU YCNH 
+YRWA BRSP BLKI BCPE BOGU BRNO
+ COGO DASC
+
+species UNCO
+is linked to 19 from 204 species, named:
+  COLO COMU DOVE GBBG LTDU ARTE GRSH RNPH
+ LAGU LETE SCAU SOSH UNDD UNLT SPSK
+ UNSP BLGU PAJA BRSP
+
+species UNSC
+is linked to 3 from 204 species, named:
+ UNGU UNLO COEI
+
+species BRBO
+is linked to 79 from 204 species, named:
+  COLO DOVE GBBG AMGO AMKE AMOY AMRO BBPL
+ BHCO BHGU GRSH ROST CHSW COME DEJU
+ DUNL EUST GADW GRHE GBHE SBDO GRYE HADU 
+HOME LESA LEYE NOPI ICGU LAGU MALL
+ OSPR PAWA PEEP PESA PISI PUSA RBNU REDH 
+RUDU RUTU RWBL SAGU SATE SCAU SEPL
+ SESA SOSP POJA RBGU SPSA TRES UCAT ULSB 
+UNBI UNEI UNFR UNPE UNLG UNME UNST
+ BANS WFSP WHIM GLGU GOME GREG MODO WILL 
+WIPH WODU YCNH YRWA UCRT BLKI BCPE
+ BOGU BRNO CANG AWPE
+
+species CATE
+is linked to 24 from 204 species, named:
+  ABDU GRCO COME DEJU GBHE LESA LIGU MAFR 
+HEPE LTJA OSPR PUMA RNGR SAND SESA
+ TRES WTTR UNWA MYWA WFSP GLGU GOME BRTE BLTE
+
+species CEDW
+is linked to 5 from 204 species, named:
+ GBTE SNGO UNEG UNSA UNFI
+
+species CHSW
+is linked to 79 from 204 species, named:
+  COLO DOVE GBBG AMGO AMKE AMOY AMRO BBPL 
+BHCO BHGU GRSH ROST BRBO COME DEJU
+ DUNL EUST GADW GRHE GBHE SBDO GRYE HADU 
+HOME LESA LEYE NOPI ICGU LAGU MALL
+ OSPR PAWA PEEP PESA PISI PUSA RBNU REDH 
+RUDU RUTU RWBL SAGU SATE SCAU SEPL
+ SESA SOSP POJA RBGU SPSA TRES UCAT ULSB 
+UNBI UNEI UNFR UNPE UNLG UNME UNST
+ BANS WFSP WHIM GLGU GOME GREG MODO WILL 
+WIPH WODU YCNH YRWA UCRT BLKI BCPE
+ BOGU BRNO CANG AWPE
+
+species COME
+is linked to 72 from 204 species, named:
+  AMGO AMKE AMOY AMRO BBPL BHCO BHGU GRCO
+ BRBO CATE CHSW DEJU DUNL EUST GADW
+ GRHE GBHE SBDO GRYE HADU HOME LESA LEYE 
+LIGU NOPI ICGU LTJA MALL OSPR PAWA
+ PEEP PESA PISI PUMA PUSA RBNU REDH RUDU 
+RUTU RWBL SAGU SAND SATE SEPL SESA
+ SOSP SPSA TRES UCAT ULSB UNEI UNFR UNPE 
+BANS UNWA MYWA WFSP WHIM GLGU GOME
+ GREG MODO WILL WIPH WODU YCNH YRWA UCRT 
+BLTE BRNO CANG AWPE
+
+species COYE
+is linked to 0 from 204 species
+
+species DEJU
+is linked to 74 from 204 species, named:
+  AMGO AMKE AMOY AMRO BBPL BHCO BHGU GRCO
+ BRBO CATE CHSW COME DUNL EUST GADW
+ GRHE GBHE SBDO GRYE HADU HOME LESA LEYE 
+LIGU MAFR NOPI ICGU LTJA MALL OSPR
+ PAWA PEEP PESA PISI PUMA PUSA RBNU REDH 
+RUDU RUTU RWBL SAGU SAND SATE SEPL
+ SESA SOSP SPSA TRES UCAT ULSB UNEI UNFR 
+UNPE BANS UNWA MYWA WFSP WHIM GLGU
+ GOME GREG MODO BRTE WILL WIPH WODU YCNH 
+YRWA UCRT BLTE BRNO CANG AWPE
+
+species DUNL
+is linked to 78 from 204 species, named:
+  COLO GBBG AMGO AMKE AMOY AMRO BBPL BHCO 
+BHGU ROST BRBO CHSW COME DEJU EUST
+ GADW GRHE GBHE SBDO GRYE HADU HOME LESA 
+LEYE LIGU NOPI ICGU LAGU MALL OSPR
+ PAWA PEEP PESA PISI PUSA RBNU REDH RUDU 
+RUTU RWBL SAGU SATE SCAU SEPL SESA
+ SOSP POJA RBGU SPSA TRES UCAT ULSB UNBI 
+UNEI UNFR UNPE UNME UNST BANS MYWA
+ WFSP WHIM GLGU GOME GREG MODO WILL WIPH 
+WODU YCNH YRWA UCRT BLKI BCPE BOGU
+ BRNO CANG AWPE
+
+species EUST
+is linked to 79 from 204 species, named:
+  COLO DOVE GBBG AMGO AMKE AMOY AMRO BBPL
+ BHCO BHGU GRSH ROST BRBO CHSW COME
+ DEJU DUNL GADW GRHE GBHE SBDO GRYE HADU
+ HOME LESA LEYE NOPI ICGU LAGU MALL
+ OSPR PAWA PEEP PESA PISI PUSA RBNU REDH 
+RUDU RUTU RWBL SAGU SATE SCAU SEPL
+ SESA SOSP POJA RBGU SPSA TRES UCAT ULSB 
+UNBI UNEI UNFR UNPE UNLG UNME UNST
+ BANS WFSP WHIM GLGU GOME GREG MODO WILL 
+WIPH WODU YCNH YRWA UCRT BLKI BCPE
+ BOGU BRNO CANG AWPE
+
+species FEPE
+is linked to 0 from 204 species
+
+species FOTE
+is linked to 24 from 204 species, named:
+  COLO DCCO DOVE GBBG NOGA GRSH RNPH ROST
+ LAGU SCAU POJA RBGU SOSH UNBI UNLT
+ UNLG UNME UNST UNSP BRSP BCPE BOGU COGO 
+DASC
+
+species GADW
+is linked to 59 from 204 species, named:
+  AMKE AMRO BBPL BHCO BHGU BRBO CHSW COME 
+DEJU DUNL EUST GRHE GBHE SBDO GRYE
+ HADU HOME LESA LEYE LIGU NOPI MALL OSPR 
+PAWA PESA PISI PUSA RBNU REDH RUDU
+ RUTU RWBL SAGU SATE SEPL SESA SOSP SPSA 
+TRES ULSB UNEI UNFR UNPE BANS MYWA
+ WFSP WHIM GLGU GOME GREG MODO WILL WIPH 
+WODU YCNH YRWA UCRT BRNO AWPE
+
+species GBTE
+is linked to 5 from 204 species, named:
+ CEDW SNGO UNEG UNSA UNFI
+
+species GCKI
+is linked to 0 from 204 species
+
+species GRCA
+is linked to 0 from 204 species
+
+species GRHE
+is linked to 59 from 204 species, named:
+  AMKE AMRO BBPL BHCO BHGU BRBO CHSW COME 
+DEJU DUNL EUST GADW GBHE SBDO GRYE
+ HADU HOME LESA LEYE LIGU NOPI MALL OSPR 
+PAWA PESA PISI PUSA RBNU REDH RUDU
+ RUTU RWBL SAGU SATE SEPL SESA SOSP SPSA 
+TRES ULSB UNEI UNFR UNPE BANS MYWA
+ WFSP WHIM GLGU GOME GREG MODO WILL WIPH 
+WODU YCNH YRWA UCRT BRNO AWPE
+
+species GRSC
+is linked to 3 from 204 species, named:
+ GWTE UNDU USSB
+
+species GBHE
+is linked to 74 from 204 species, named:
+  AMGO AMKE AMOY AMRO BBPL BHCO BHGU GRCO 
+BRBO CATE CHSW COME DEJU DUNL EUST
+ GADW GRHE SBDO GRYE HADU HOME LESA LEYE 
+LIGU NOPI HEPE ICGU LTJA MALL OSPR
+ PAWA PEEP PESA PISI PUMA PUSA RBNU REDH
+ RUDU RUTU RWBL SAGU SAND SATE SEPL
+ SESA SOSP SPSA TRES UCAT ULSB UNEI UNFR 
+UNPE BANS UNWA MYWA WFSP WHIM GLGU
+ GOME GREG MODO BRTE WILL WIPH WODU YCNH 
+YRWA UCRT BLTE BRNO CANG AWPE
+
+species SBDO
+is linked to 79 from 204 species, named:
+  COLO DOVE GBBG AMGO AMKE AMOY AMRO BBPL BHCO 
+BHGU GRSH ROST BRBO CHSW COME
+ DEJU DUNL EUST GADW GRHE GBHE GRYE HADU HOME 
+LESA LEYE NOPI ICGU LAGU MALL
+ OSPR PAWA PEEP PESA PISI PUSA RBNU REDH RUDU 
+RUTU RWBL SAGU SATE SCAU SEPL
+ SESA SOSP POJA RBGU SPSA TRES UCAT ULSB UNBI 
+UNEI UNFR UNPE UNLG UNME UNST
+ BANS WFSP WHIM GLGU GOME GREG MODO WILL WIPH 
+WODU YCNH YRWA UCRT BLKI BCPE
+ BOGU BRNO CANG AWPE
+
+species GRYE
+is linked to 79 from 204 species, named:
+  COLO DOVE GBBG AMGO AMKE AMOY AMRO BBPL BHCO
+ BHGU GRSH ROST BRBO CHSW COME
+ DEJU DUNL EUST GADW GRHE GBHE SBDO HADU HOME 
+LESA LEYE NOPI ICGU LAGU MALL
+ OSPR PAWA PEEP PESA PISI PUSA RBNU REDH RUDU 
+RUTU RWBL SAGU SATE SCAU SEPL
+ SESA SOSP POJA RBGU SPSA TRES UCAT ULSB UNBI
+ UNEI UNFR UNPE UNLG UNME UNST
+ BANS WFSP WHIM GLGU GOME GREG MODO WILL WIPH
+ WODU YCNH YRWA UCRT BLKI BCPE
+ BOGU BRNO CANG AWPE
+
+species GWTE
+is linked to 3 from 204 species, named:
+ GRSC UNDU USSB
+
+species HADU
+is linked to 79 from 204 species, named:
+  COLO DOVE GBBG AMGO AMKE AMOY AMRO BBPL BHCO
+ BHGU GRSH ROST BRBO CHSW COME
+ DEJU DUNL EUST GADW GRHE GBHE SBDO GRYE HOME 
+LESA LEYE NOPI ICGU LAGU MALL
+ OSPR PAWA PEEP PESA PISI PUSA RBNU REDH RUDU 
+RUTU RWBL SAGU SATE SCAU SEPL
+ SESA SOSP POJA RBGU SPSA TRES UCAT ULSB UNBI 
+UNEI UNFR UNPE UNLG UNME UNST
+ BANS WFSP WHIM GLGU GOME GREG MODO WILL WIPH 
+WODU YCNH YRWA UCRT BLKI BCPE
+ BOGU BRNO CANG AWPE
+
+species HOME
+is linked to 79 from 204 species, named:
+  COLO DOVE GBBG AMGO AMKE AMOY AMRO BBPL BHCO 
+BHGU GRSH ROST BRBO CHSW COME
+ DEJU DUNL EUST GADW GRHE GBHE SBDO GRYE HADU 
+LESA LEYE NOPI ICGU LAGU MALL
+ OSPR PAWA PEEP PESA PISI PUSA RBNU REDH RUDU 
+RUTU RWBL SAGU SATE SCAU SEPL
+ SESA SOSP POJA RBGU SPSA TRES UCAT ULSB UNBI 
+UNEI UNFR UNPE UNLG UNME UNST
+ BANS WFSP WHIM GLGU GOME GREG MODO WILL WIPH 
+WODU YCNH YRWA UCRT BLKI BCPE
+ BOGU BRNO CANG AWPE
+
+species LBBG
+is linked to 8 from 204 species, named:
+ BARS GRSK SOTE SHOR UNJA TBMU UNGR UNSK
+
+species LESA
+is linked to 73 from 204 species, named:
+  AMGO AMKE AMOY AMRO BBPL BHCO BHGU GRCO BRBO
+ CATE CHSW COME DEJU DUNL EUST
+ GADW GRHE GBHE SBDO GRYE HADU HOME LEYE LIGU 
+NOPI ICGU LTJA MALL OSPR PAWA
+ PEEP PESA PISI PUMA PUSA RBNU REDH RUDU RUTU 
+RWBL SAGU SAND SATE SEPL SESA
+ SOSP SPSA TRES UCAT ULSB UNEI UNFR UNPE BANS 
+UNWA MYWA WFSP WHIM GLGU GOME
+ GREG MODO BRTE WILL WIPH WODU YCNH YRWA UCRT 
+BLTE BRNO CANG AWPE
+
+species LESC
+is linked to 0 from 204 species
+
+species LEYE
+is linked to 79 from 204 species, named:
+  COLO DOVE GBBG AMGO AMKE AMOY AMRO BBPL BHCO
+ BHGU GRSH ROST BRBO CHSW COME
+ DEJU DUNL EUST GADW GRHE GBHE SBDO GRYE HADU 
+HOME LESA NOPI ICGU LAGU MALL
+ OSPR PAWA PEEP PESA PISI PUSA RBNU REDH RUDU 
+RUTU RWBL SAGU SATE SCAU SEPL
+ SESA SOSP POJA RBGU SPSA TRES UCAT ULSB UNBI 
+UNEI UNFR UNPE UNLG UNME UNST
+ BANS WFSP WHIM GLGU GOME GREG MODO WILL WIPH 
+WODU YCNH YRWA UCRT BLKI BCPE
+ BOGU BRNO CANG AWPE
+
+species LIGU
+is linked to 48 from 204 species, named:
+  ABDU BHCO BHGU GRCO CATE COME DEJU DUNL GADW 
+GRHE GBHE LESA HEPE ICGU LTJA
+ MALL OSPR PEEP PUMA PUSA REDH RWBL SAND SEPL
+ SESA SOSP SPSA TRES ULSB UNEI
+ UNPE WTTR BANS UNWA MYWA WFSP WHIM GLGU GOME
+ MODO BRTE WILL WODU YRWA UCRT
+ BLTE CANG AWPE
+
+species LISH
+is linked to 0 from 204 species
+
+species MABO
+is linked to 0 from 204 species
+
+species MAFR
+is linked to 8 from 204 species, named:
+ GRCO CATE DEJU PUMA SAND GLGU BRTE BLTE
+
+species MAWA
+is linked to 0 from 204 species
+
+species NOFL
+is linked to 0 from 204 species
+
+species NOHA
+is linked to 0 from 204 species
+
+species NOPI
+is linked to 79 from 204 species, named:
+  COLO DOVE GBBG AMGO AMKE AMOY AMRO BBPL 
+BHCO BHGU GRSH ROST BRBO CHSW COME
+ DEJU DUNL EUST GADW GRHE GBHE SBDO GRYE 
+HADU HOME LESA LEYE ICGU LAGU MALL
+ OSPR PAWA PEEP PESA PISI PUSA RBNU REDH
+ RUDU RUTU RWBL SAGU SATE SCAU SEPL
+ SESA SOSP POJA RBGU SPSA TRES UCAT ULSB 
+UNBI UNEI UNFR UNPE UNLG UNME UNST
+ BANS WFSP WHIM GLGU GOME GREG MODO WILL 
+WIPH WODU YCNH YRWA UCRT BLKI BCPE
+ BOGU BRNO CANG AWPE
+
+species NOTE
+is linked to 0 from 204 species
+
+species GRSK
+is linked to 10 from 204 species
+  COMU BARS LBBG HOGR SOTE SHOR UNJA SPSK 
+UNGR BRSP
+
+species HEPE
+is linked to 16 from 204 species, named:
+  ABDU GRCO CATE GBHE LIGU LTJA PUMA RNGR 
+SAND TRES SWAL WTTR UNWA MYWA BRTE
+ BLTE
+
+species HOGR
+is linked to 9 from 204 species, named:
+ COMU BARS GRSK SOTE SHOR UNDD SPSK UNGR BCPE
+
+species ICGU
+is linked to 58 from 204 species, named:
+  AMGO AMKE AMOY AMRO BBPL BHCO BHGU BRBO 
+CHSW COME DEJU DUNL EUST GBHE SBDO
+ GRYE HADU HOME LESA LEYE LIGU NOPI MALL 
+OSPR PAWA PEEP PESA PISI RBNU REDH
+ RUDU RUTU RWBL SAGU SATE SEPL SESA SOSP 
+TRES UCAT UNEI UNFR UNPE BANS MYWA
+ WFSP WHIM GLGU GOME GREG MODO WIPH WODU 
+YCNH YRWA BRNO CANG AWPE
+
+species LAGU
+is linked to 64 from 204 species, named:
+  BLSC COLO DCCO DOVE GBBG LTDU NOGA AMGO 
+AMKE AMOY AMRO BBPL BHCO BHGU GRSH
+ RNPH UNCO BRBO CHSW DUNL EUST FOTE SBDO 
+GRYE HADU HOME LEYE NOPI MALL PAWA
+ PEEP PESA PISI RBNU REDH RUDU RUTU SAGU 
+SATE SOSP SOSH UCAT UNBI UNDD UNEI
+ UNFR UNLT UNPE UNLG BANS WHIM GREG MODO 
+UNSP WIPH WODU YCNH YRWA BRSP BCPE
+ BRNO CANG COGO DASC
+
+species LESP
+is linked to 10 from 204 species
+  NOFU REPH MASH RBME RBGU UBBG UNLA BLKI
+ BOGU COTE
+
+species LETE
+is linked to 10 from 204 species
+  COMU BARS ARTE UNCO SHOR UNDD SPSK UNGR
+ BLGU PAJA
+
+species LTJA
+is linked to 23 from 204 species, named:
+  ABDU GRCO CATE COME DEJU GBHE LESA LIGU 
+HEPE OSPR PUMA RNGR SAND SESA TRES
+ WTTR UNWA MYWA WFSP GLGU GOME BRTE BLTE
+
+species MALL
+is linked to 80 from 204 species
+  COLO DOVE GBBG AMGO AMKE AMOY AMRO BBPL
+ BHCO BHGU ROST BRBO CHSW COME DEJU
+ DUNL EUST GADW GRHE GBHE SBDO GRYE HADU
+ HOME LESA LEYE LIGU NOPI ICGU LAGU
+ OSPR PAWA PEEP PESA PISI PUSA RBNU REDH
+ RUDU RUTU RWBL SAGU SATE SCAU SEPL
+ SESA SOSP POJA RBGU SPSA TRES UCAT ULSB
+ UNBI UNEI UNFR UNPE UNLG UNME UNST
+ BANS MYWA WFSP WHIM GLGU GOME GREG MODO
+ WILL WIPH WODU YCNH YRWA UCRT BLKI
+ BCPE BOGU BRNO CANG AWPE
+
+species MASH
+is linked to 16 from 204 species, named:
+  REPH ROST LESP SCAU POJA RBME UBBG UNLA
+ UNME UNSG UNST AUSH ATPU BRPE BCPE
+ DASC
+
+species NOWA
+is linked to 0 from 204 species
+
+species OSPR
+is linked to 73 from 204 species, named:
+  AMGO AMKE AMOY AMRO BBPL BHCO BHGU GRCO
+ BRBO CATE CHSW COME DEJU DUNL EUST
+ GADW GRHE GBHE SBDO GRYE HADU HOME LESA
+ LEYE LIGU NOPI ICGU LTJA MALL PAWA
+ PEEP PESA PISI PUMA PUSA RBNU REDH RUDU
+ RUTU RWBL SAGU SAND SATE SEPL SESA
+ SOSP SPSA TRES UCAT ULSB UNEI UNFR UNPE
+ BANS UNWA MYWA WFSP WHIM GLGU GOME
+ GREG MODO BRTE WILL WIPH WODU YCNH YRWA
+ UCRT BLTE BRNO CANG AWPE
+
+species PAWA
+is linked to 79 from 204 species, named:
+  COLO DOVE GBBG AMGO AMKE AMOY AMRO BBPL
+ BHCO BHGU GRSH ROST BRBO CHSW COME
+ DEJU DUNL EUST GADW GRHE GBHE SBDO GRYE 
+HADU HOME LESA LEYE NOPI ICGU LAGU
+ MALL OSPR PEEP PESA PISI PUSA RBNU REDH 
+RUDU RUTU RWBL SAGU SATE SCAU SEPL
+ SESA SOSP POJA RBGU SPSA TRES UCAT ULSB
+ UNBI UNEI UNFR UNPE UNLG UNME UNST
+ BANS WFSP WHIM GLGU GOME GREG MODO WILL
+ WIPH WODU YCNH YRWA UCRT BLKI BCPE
+ BOGU BRNO CANG AWPE
+
+species PEEP
+is linked to 69 from 204 species, named:
+  COLO GBBG AMGO AMKE AMOY AMRO BBPL BHCO 
+BHGU ROST BRBO CHSW COME DEJU DUNL
+ EUST GBHE SBDO GRYE HADU HOME LESA LEYE 
+LIGU NOPI ICGU LAGU MALL OSPR PAWA
+ PESA PISI RBNU REDH RUDU RUTU RWBL SAGU 
+SATE SCAU SEPL SESA SOSP POJA RBGU
+ TRES UCAT UNBI UNEI UNFR UNPE UNME BANS 
+MYWA WFSP WHIM GLGU GOME GREG MODO
+ WIPH WODU YCNH YRWA BLKI BOGU BRNO CANG 
+AWPE
+
+species PEFA
+is linked to 0 from 204 species
+
+species PESA
+is linked to 79 from 204 species, named:
+  COLO DOVE GBBG AMGO AMKE AMOY AMRO BBPL 
+BHCO BHGU GRSH ROST BRBO CHSW COME
+ DEJU DUNL EUST GADW GRHE GBHE SBDO GRYE 
+HADU HOME LESA LEYE NOPI ICGU LAGU
+ MALL OSPR PAWA PEEP PISI PUSA RBNU REDH 
+RUDU RUTU RWBL SAGU SATE SCAU SEPL
+ SESA SOSP POJA RBGU SPSA TRES UCAT ULSB 
+UNBI UNEI UNFR UNPE UNLG UNME UNST
+ BANS WFSP WHIM GLGU GOME GREG MODO WILL
+ WIPH WODU YCNH YRWA UCRT BLKI BCPE
+ BOGU BRNO CANG AWPE
+
+species PISI
+is linked to 79 from 204 species, named:
+  COLO DOVE GBBG AMGO AMKE AMOY AMRO BBPL
+ BHCO BHGU GRSH ROST BRBO CHSW COME
+ DEJU DUNL EUST GADW GRHE GBHE SBDO GRYE 
+HADU HOME LESA LEYE NOPI ICGU LAGU
+ MALL OSPR PAWA PEEP PESA PUSA RBNU REDH 
+RUDU RUTU RWBL SAGU SATE SCAU SEPL
+ SESA SOSP POJA RBGU SPSA TRES UCAT ULSB 
+UNBI UNEI UNFR UNPE UNLG UNME UNST
+ BANS WFSP WHIM GLGU GOME GREG MODO WILL 
+WIPH WODU YCNH YRWA UCRT BLKI BCPE
+ BOGU BRNO CANG AWPE
+
+species PUMA
+is linked to 22 from 204 species, named:
+  ABDU GRCO CATE COME DEJU GBHE LESA LIGU 
+MAFR HEPE LTJA OSPR RNGR SAND TRES
+ WTTR UNWA MYWA WFSP GLGU BRTE BLTE
+
+species PUSA
+is linked to 59 from 204 species, named:
+  AMKE AMRO BBPL BHCO BHGU BRBO CHSW COME 
+DEJU DUNL EUST GADW GRHE GBHE SBDO
+ GRYE HADU HOME LESA LEYE LIGU NOPI MALL
+ OSPR PAWA PESA PISI RBNU REDH RUDU
+ RUTU RWBL SAGU SATE SEPL SESA SOSP SPSA 
+TRES ULSB UNEI UNFR UNPE BANS MYWA
+ WFSP WHIM GLGU GOME GREG MODO WILL WIPH 
+WODU YCNH YRWA UCRT BRNO AWPE
+
+species RBNU
+is linked to 79 from 204 species, named:
+  COLO DOVE GBBG AMGO AMKE AMOY AMRO BBPL 
+BHCO BHGU GRSH ROST BRBO CHSW COME
+ DEJU DUNL EUST GADW GRHE GBHE SBDO GRYE 
+HADU HOME LESA LEYE NOPI ICGU LAGU
+ MALL OSPR PAWA PEEP PESA PISI PUSA REDH 
+RUDU RUTU RWBL SAGU SATE SCAU SEPL
+ SESA SOSP POJA RBGU SPSA TRES UCAT ULSB 
+UNBI UNEI UNFR UNPE UNLG UNME UNST
+ BANS WFSP WHIM GLGU GOME GREG MODO WILL WIPH 
+WODU YCNH YRWA UCRT BLKI BCPE
+ BOGU BRNO CANG AWPE
+
+species RBTR
+is linked to 0 from 204 species
+
+species RCKI
+is linked to 0 from 204 species
+
+species REDH
+is linked to 78 from 204 species, named:
+  COLO GBBG AMGO AMKE AMOY AMRO BBPL BHCO
+ BHGU ROST BRBO CHSW COME DEJU DUNL
+ EUST GADW GRHE GBHE SBDO GRYE HADU HOME
+ LESA LEYE LIGU NOPI ICGU LAGU MALL
+ OSPR PAWA PEEP PESA PISI PUSA RBNU RUDU 
+RUTU RWBL SAGU SATE SCAU SEPL SESA
+ SOSP POJA RBGU SPSA TRES UCAT ULSB UNBI
+ UNEI UNFR UNPE UNME UNST BANS MYWA
+ WFSP WHIM GLGU GOME GREG MODO WILL WIPH 
+WODU YCNH YRWA UCRT BLKI BCPE BOGU
+ BRNO CANG AWPE
+
+species RNGR
+is linked to 11 from 204 species, named:
+  ABDU GRCO CATE HEPE LTJA PUMA SAND WTTR 
+UNWA BRTE BLTE
+
+species RUDU
+is linked to 79 from 204 species, named:
+  COLO DOVE GBBG AMGO AMKE AMOY AMRO BBPL 
+BHCO BHGU GRSH ROST BRBO CHSW COME
+ DEJU DUNL EUST GADW GRHE GBHE SBDO GRYE 
+HADU HOME LESA LEYE NOPI ICGU LAGU
+ MALL OSPR PAWA PEEP PESA PISI PUSA RBNU
+ REDH RUTU RWBL SAGU SATE SCAU SEPL
+ SESA SOSP POJA RBGU SPSA TRES UCAT ULSB
+ UNBI UNEI UNFR UNPE UNLG UNME UNST
+ BANS WFSP WHIM GLGU GOME GREG MODO WILL 
+WIPH WODU YCNH YRWA UCRT BLKI BCPE
+ BOGU BRNO CANG AWPE
+
+species RUTU
+is linked to 79 from 204 species, named:
+  COLO DOVE GBBG AMGO AMKE AMOY AMRO BBPL 
+BHCO BHGU GRSH ROST BRBO CHSW COME
+ DEJU DUNL EUST GADW GRHE GBHE SBDO GRYE
+ HADU HOME LESA LEYE NOPI ICGU LAGU
+ MALL OSPR PAWA PEEP PESA PISI PUSA RBNU
+ REDH RUDU RWBL SAGU SATE SCAU SEPL
+ SESA SOSP POJA RBGU SPSA TRES UCAT ULSB 
+UNBI UNEI UNFR UNPE UNLG UNME UNST
+ BANS WFSP WHIM GLGU GOME GREG MODO WILL 
+WIPH WODU YCNH YRWA UCRT BLKI BCPE
+ BOGU BRNO CANG AWPE
+
+species RWBL
+is linked to 70 from 204 species
+  AMGO AMKE AMOY AMRO BBPL BHCO BHGU BRBO 
+CHSW COME DEJU DUNL EUST GADW GRHE
+ GBHE SBDO GRYE HADU HOME LESA LEYE LIGU
+ NOPI ICGU MALL OSPR PAWA PEEP PESA
+ PISI PUSA RBNU REDH RUDU RUTU SAGU SATE
+ SCAU SEPL SESA SOSP RBGU SPSA TRES
+ UCAT ULSB UNEI UNFR UNPE UNST BANS MYWA 
+WFSP WHIM GLGU GOME GREG MODO WILL
+ WIPH WODU YCNH YRWA UCRT BLKI BOGU BRNO 
+CANG AWPE
+
+species SAGU
+is linked to 79 from 204 species, named:
+  COLO DOVE GBBG AMGO AMKE AMOY AMRO BBPL 
+BHCO BHGU GRSH ROST BRBO CHSW COME
+ DEJU DUNL EUST GADW GRHE GBHE SBDO GRYE 
+HADU HOME LESA LEYE NOPI ICGU LAGU
+ MALL OSPR PAWA PEEP PESA PISI PUSA RBNU 
+REDH RUDU RUTU RWBL SATE SCAU SEPL
+ SESA SOSP POJA RBGU SPSA TRES UCAT ULSB
+ UNBI UNEI UNFR UNPE UNLG UNME UNST
+ BANS WFSP WHIM GLGU GOME GREG MODO WILL
+ WIPH WODU YCNH YRWA UCRT BLKI BCPE
+ BOGU BRNO CANG AWPE
+
+species SAND
+is linked to 22 from 204 species, named:
+  ABDU GRCO CATE COME DEJU GBHE LESA LIGU 
+MAFR HEPE LTJA OSPR PUMA RNGR TRES
+ WTTR UNWA MYWA WFSP GLGU BRTE BLTE
+
+species SATE
+is linked to 79 from 204 species, named:
+  COLO DOVE GBBG AMGO AMKE AMOY AMRO BBPL 
+BHCO BHGU GRSH ROST BRBO CHSW COME
+ DEJU DUNL EUST GADW GRHE GBHE SBDO GRYE 
+HADU HOME LESA LEYE NOPI ICGU LAGU
+ MALL OSPR PAWA PEEP PESA PISI PUSA RBNU 
+REDH RUDU RUTU RWBL SAGU SCAU SEPL
+ SESA SOSP POJA RBGU SPSA TRES UCAT ULSB 
+UNBI UNEI UNFR UNPE UNLG UNME UNST
+ BANS WFSP WHIM GLGU GOME GREG MODO WILL 
+WIPH WODU YCNH YRWA UCRT BLKI BCPE
+ BOGU BRNO CANG AWPE
+
+species SAVS
+is linked to 0 from 204 species
+
+species SCAU
+is linked to 63 from 204 species, named:
+  AMGO AMKE AMOY AMRO BBPL BHCO BHGU RNPH
+ REPH ROST UNCO BRBO CHSW DUNL EUST
+ FOTE SBDO GRYE HADU HOME LEYE NOPI MALL 
+MASH PAWA PEEP PESA PISI RBNU REDH
+ RUDU RUTU RWBL SAGU SATE SEPL SOSP POJA 
+RBME UBBG UCAT UNDD UNEI UNFR UNPE
+ UNLA UNME UNST BANS WHIM GREG MODO WIPH 
+WODU YCNH YRWA BRSP BCPE BRNO CANG
+ COGO DASC AWPE
+
+species SEPL
+is linked to 70 from 204 species
+  AMGO AMKE AMOY AMRO BBPL BHCO BHGU BRBO
+ CHSW COME DEJU DUNL EUST GADW GRHE
+ GBHE SBDO GRYE HADU HOME LESA LEYE LIGU 
+NOPI ICGU MALL OSPR PAWA PEEP PESA
+ PISI PUSA RBNU REDH RUDU RUTU RWBL SAGU 
+SATE SCAU SESA SOSP RBGU SPSA TRES
+ UCAT ULSB UNEI UNFR UNPE UNST BANS MYWA 
+WFSP WHIM GLGU GOME GREG MODO WILL
+ WIPH WODU YCNH YRWA UCRT BLKI BOGU BRNO 
+CANG AWPE
+
+species SESA
+is linked to 69 from 204 species, named:
+  AMGO AMKE AMOY AMRO BBPL BHCO BHGU BRBO
+ CATE CHSW COME DEJU DUNL EUST GADW
+ GRHE GBHE SBDO GRYE HADU HOME LESA LEYE 
+LIGU NOPI ICGU LTJA MALL OSPR PAWA
+ PEEP PESA PISI PUSA RBNU REDH RUDU RUTU
+ RWBL SAGU SATE SEPL SOSP SPSA TRES
+ UCAT ULSB UNEI UNFR UNPE BANS UNWA MYWA 
+WFSP WHIM GLGU GOME GREG MODO WILL
+ WIPH WODU YCNH YRWA UCRT BLTE BRNO CANG AWPE
+
+species SNBU
+is linked to 0 from 204 species
+
+species SNGO
+is linked to 5 from 204 species, named:
+ CEDW GBTE UNEG UNSA UNFI
+
+species SOSP
+is linked to 75 from 204 species, named:
+  GBBG AMGO AMKE AMOY AMRO BBPL BHCO BHGU
+ BRBO CHSW COME DEJU DUNL EUST GADW
+ GRHE GBHE SBDO GRYE HADU HOME LESA LEYE 
+LIGU NOPI ICGU LAGU MALL OSPR PAWA
+ PEEP PESA PISI PUSA RBNU REDH RUDU RUTU 
+RWBL SAGU SATE SCAU SEPL SESA POJA
+ RBGU SPSA TRES UCAT ULSB UNBI UNEI UNFR 
+UNPE UNME UNST BANS MYWA WFSP WHIM
+ GLGU GOME GREG MODO WILL WIPH WODU YCNH 
+YRWA UCRT BLKI BOGU BRNO CANG AWPE
+
+species POJA
+is linked to 64 from 204 species, named:
+  DOVE AMGO AMKE AMOY AMRO BBPL BHCO BHGU RNPH 
+REPH ROST BRBO CHSW DUNL EUST
+ FOTE SBDO GRYE HADU HOME LEYE NOPI MALL MASH 
+PAWA PEEP PESA PISI RBNU REDH
+ RUDU RUTU SAGU SATE SCAU SOSP RBME RBGU UBBG 
+UCAT UNBI UNEI UNFR UNPE UNLA
+ UNLG UNME UNST BANS WHIM GREG MODO UNSP WIPH 
+WODU YCNH YRWA BRSP BLKI BCPE
+ BOGU BRNO COGO DASC
+
+species RBME
+is linked to 15 from 204 species, named:
+  REPH ROST LESP MASH SCAU POJA UBBG UNLA UNME
+ UNSG UNST AUSH ATPU BRPE BCPE
+
+species RBGU
+is linked to 63 from 204 species, named:
+  DOVE AMGO AMKE AMOY AMRO BBPL BHCO BHGU RNPH 
+ROST BRBO CHSW DUNL EUST FOTE
+ SBDO GRYE HADU HOME LEYE NOPI LESP MALL PAWA
+ PEEP PESA PISI RBNU REDH RUDU
+ RUTU RWBL SAGU SATE SEPL SOSP POJA UCAT UNBI
+ UNEI UNFR UNPE UNLG UNME UNST
+ BANS WHIM GREG MODO UNSP WIPH WODU YCNH YRWA
+ BRSP BLKI BCPE BOGU BRNO CANG
+ COGO DASC AWPE
+
+species ROYT
+is linked to 6 from 204 species, named:
+ UNAL UNSG ATPU BRPE UNPH UNSH
+
+species SOSH
+is linked to 22 from 204 species, named:
+  BLSC COLO DCCO DOVE GBBG LTDU NOGA GRSH RAZO
+ RNPH UNCO FOTE LAGU UNBI UNDD
+ UNLT UNLG UNSP BRSP BCPE COGO DASC
+
+species SOTE
+is linked to 9 from 204 species, named:
+ COMU BARS LBBG GRSK HOGR SHOR SPSK UNGR DASC
+
+species SHOR
+is linked to 11 from 204 species, named:
+  BARS ARTE LBBG GRSK HOGR LETE SOTE UNJA TBMU 
+UNGR UNSK
+
+species SPSA
+is linked to 59 from 204 species, named:
+  AMKE AMRO BBPL BHCO BHGU BRBO CHSW COME DEJU
+ DUNL EUST GADW GRHE GBHE SBDO
+ GRYE HADU HOME LESA LEYE LIGU NOPI MALL OSPR 
+PAWA PESA PISI PUSA RBNU REDH
+ RUDU RUTU RWBL SAGU SATE SEPL SESA SOSP TRES 
+ULSB UNEI UNFR UNPE BANS MYWA
+ WFSP WHIM GLGU GOME GREG MODO WILL WIPH WODU 
+YCNH YRWA UCRT BRNO AWPE
+
+species TRES
+is linked to 76 from 204 species, named:
+  ABDU AMGO AMKE AMOY AMRO BBPL BHCO BHGU GRCO
+ BRBO CATE CHSW COME DEJU DUNL
+ EUST GADW GRHE GBHE SBDO GRYE HADU HOME LESA 
+LEYE LIGU NOPI HEPE ICGU LTJA
+ MALL OSPR PAWA PEEP PESA PISI PUMA PUSA RBNU 
+REDH RUDU RUTU RWBL SAGU SAND
+ SATE SEPL SESA SOSP SPSA UCAT ULSB UNEI UNFR 
+UNPE WTTR BANS UNWA MYWA WFSP
+ WHIM GLGU GOME GREG MODO BRTE WILL WIPH WODU 
+YCNH YRWA UCRT BLTE BRNO CANG
+ AWPE
+
+species UBBG
+is linked to 15 from 204 species, named:
+  REPH ROST LESP MASH SCAU POJA RBME UNLA UNME 
+UNSG UNST AUSH ATPU BRPE BCPE
+
+species UCAT
+is linked to 72 from 204 species, named:
+  COLO DOVE GBBG AMGO AMKE AMOY AMRO BBPL BHCO
+ BHGU GRSH ROST BRBO CHSW COME
+ DEJU DUNL EUST GBHE SBDO GRYE HADU HOME LESA 
+LEYE NOPI ICGU LAGU MALL OSPR
+ PAWA PEEP PESA PISI RBNU REDH RUDU RUTU RWBL 
+SAGU SATE SCAU SEPL SESA SOSP
+ POJA RBGU TRES UNBI UNEI UNFR UNPE UNLG UNME 
+UNST BANS WFSP WHIM GLGU GOME
+ GREG MODO WIPH WODU YCNH YRWA BLKI BCPE BOGU 
+BRNO CANG AWPE
+
+species ULSB
+is linked to 59 from 204 species, named:
+  AMKE AMRO BBPL BHCO BHGU BRBO CHSW COME DEJU
+ DUNL EUST GADW GRHE GBHE SBDO
+ GRYE HADU HOME LESA LEYE LIGU NOPI MALL OSPR 
+PAWA PESA PISI PUSA RBNU REDH
+ RUDU RUTU RWBL SAGU SATE SEPL SESA SOSP SPSA 
+TRES UNEI UNFR UNPE BANS MYWA
+ WFSP WHIM GLGU GOME GREG MODO WILL WIPH WODU 
+YCNH YRWA UCRT BRNO AWPE
+
+species UNBI
+is linked to 65 from 204 species, named:
+  BLSC COLO DOVE GBBG LTDU AMGO AMKE AMOY AMRO
+ BBPL BHCO BHGU GRSH RNPH ROST
+ BRBO CHSW DUNL EUST FOTE SBDO GRYE HADU HOME 
+LEYE NOPI LAGU MALL PAWA PEEP
+ PESA PISI RBNU REDH RUDU RUTU SAGU SATE SOSP 
+POJA RBGU SOSH UCAT UNEI UNFR
+ UNLT UNPE UNLG UNME BANS WHIM GREG MODO UNSP 
+WIPH WODU YCNH YRWA BRSP BLKI
+ BCPE BOGU BRNO COGO DASC
+
+species UNDD
+is linked to 21 from 204 species, named:
+  COLO COMU GBBG LTDU NOGA ARTE GRSH RNPH UNCO
+ HOGR LAGU LETE SCAU SOSH UNLT
+ SPSK UNSP BLGU PAJA BRSP COGO
+
+species UNEG
+is linked to 5 from 204 species, named:
+ CEDW GBTE SNGO UNSA UNFI
+
+species UNEI
+is linked to 75 from 204 species, named:
+  GBBG AMGO AMKE AMOY AMRO BBPL BHCO BHGU BRBO
+ CHSW COME DEJU DUNL EUST GADW
+ GRHE GBHE SBDO GRYE HADU HOME LESA LEYE LIGU 
+NOPI ICGU LAGU MALL OSPR PAWA
+ PEEP PESA PISI PUSA RBNU REDH RUDU RUTU RWBL
+ SAGU SATE SCAU SEPL SESA SOSP
+ POJA RBGU SPSA TRES UCAT ULSB UNBI UNFR UNPE
+ UNME UNST BANS MYWA WFSP WHIM
+ GLGU GOME GREG MODO WILL WIPH WODU YCNH YRWA
+ UCRT BLKI BOGU BRNO CANG AWPE
+
+species UNFR
+is linked to 79 from 204 species, named:
+  COLO DOVE GBBG AMGO AMKE AMOY AMRO BBPL BHCO
+ BHGU GRSH ROST BRBO CHSW COME
+ DEJU DUNL EUST GADW GRHE GBHE SBDO GRYE HADU 
+HOME LESA LEYE NOPI ICGU LAGU
+ MALL OSPR PAWA PEEP PESA PISI PUSA RBNU REDH 
+RUDU RUTU RWBL SAGU SATE SCAU
+ SEPL SESA SOSP POJA RBGU SPSA TRES UCAT ULSB 
+UNBI UNEI UNPE UNLG UNME UNST
+ BANS WFSP WHIM GLGU GOME GREG MODO WILL WIPH 
+WODU YCNH YRWA UCRT BLKI BCPE
+ BOGU BRNO CANG AWPE
+
+species UNGO
+is linked to 3 from 204 species, named:
+ TBMU UNMU UNSK
+
+species UNLT
+is linked to 21 from 204 species, named:
+  BLSC COLO DCCO DOVE GBBG LTDU NOGA GRSH RAZO
+ RNPH UNCO FOTE LAGU SOSH UNBI
+ UNDD UNLG UNSP BRSP COGO DASC
+
+species UNPA
+is linked to 1/204 vertex, named:
+ BLGU
+
+species UNPT
+is linked to 0 from 204 species
+
+species UNJA
+is linked to 7 from 204 species, named:
+ BARS LBBG GRSK SHOR TBMU UNGR UNSK
+
+species UNPE
+is linked to 79 from 204 species, named:
+  COLO GBBG AMGO AMKE AMOY AMRO BBPL BHCO BHGU
+ ROST BRBO CHSW COME DEJU DUNL
+ EUST GADW GRHE GBHE SBDO GRYE HADU HOME LESA 
+LEYE LIGU NOPI ICGU LAGU MALL
+ OSPR PAWA PEEP PESA PISI PUSA RBNU REDH RUDU 
+RUTU RWBL SAGU SATE SCAU SEPL
+ SESA SOSP POJA RBGU SPSA TRES UCAT ULSB UNBI 
+UNEI UNFR UNLG UNME UNST BANS
+ MYWA WFSP WHIM GLGU GOME GREG MODO WILL WIPH 
+WODU YCNH YRWA UCRT BLKI BCPE
+ BOGU BRNO CANG AWPE
+
+species SPAR
+is linked to 0 from 204 species
+
+species SWAL
+is linked to 1/204 vertex, named:
+ HEPE
+
+species SPSK
+is linked to 12 from 204 species, named:
+  BLSC COMU LTDU ARTE UNCO GRSK HOGR LETE SOTE
+ UNDD BLGU PAJA
+
+species TBMU
+is linked to 8 from 204 species, named:
+ BARS LBBG SHOR UNGO UNJA UNGR UNMU UNSK
+
+species UNAL
+is linked to 4 from 204 species, named:
+ ROYT BUFF UNPH UNSH
+
+species UNDU
+is linked to 3 from 204 species, named:
+ GRSC GWTE USSB
+
+species UNGR
+is linked to 12 from 204 species, named:
+  COMU BARS ARTE LBBG GRSK HOGR LETE SOTE SHOR
+ UNJA TBMU UNSK
+
+species UNGU
+is linked to 3 from 204 species, named:
+ UNSC UNLO COEI
+
+species UNLA
+is linked to 15 from 204 species, named:
+  REPH ROST LESP MASH SCAU POJA RBME UBBG UNME
+ UNSG UNST AUSH ATPU BRPE BCPE
+
+species UNLG
+is linked to 58 from 204 species, named:
+  BLSC COLO DCCO DOVE GBBG LTDU AMGO AMKE AMOY
+ AMRO BBPL BHCO GRSH RNPH ROST
+ BRBO CHSW EUST FOTE SBDO GRYE HADU HOME LEYE 
+NOPI LAGU MALL PAWA PESA PISI
+ RBNU RUDU RUTU SAGU SATE POJA RBGU SOSH UCAT 
+UNBI UNFR UNLT UNPE UNME BANS
+ WHIM GREG UNSP WIPH WODU YCNH BRSP BLKI BCPE 
+BOGU BRNO COGO DASC
+
+species UNLO
+is linked to 3 from 204 species, named:
+ UNSC UNGU COEI
+
+species UNME
+is linked to 63 from 204 species, named:
+  AMGO AMKE AMOY AMRO BBPL BHCO BHGU RNPH REPH
+ ROST BRBO CHSW DUNL EUST FOTE
+ SBDO GRYE HADU HOME LEYE NOPI MALL MASH PAWA 
+PEEP PESA PISI RBNU REDH RUDU
+ RUTU SAGU SATE SCAU SOSP POJA RBME RBGU UBBG 
+UCAT UNBI UNEI UNFR UNPE UNLA
+ UNLG UNST BANS WHIM GREG MODO UNSP WIPH WODU 
+YCNH YRWA BRSP BLKI BCPE BOGU
+ BRNO COGO DASC
+
+species UNMU
+is linked to 3 from 204 species, named:
+ UNGO TBMU UNSK
+
+species UNSA
+is linked to 5 from 204 species, named:
+ CEDW GBTE SNGO UNEG UNFI
+
+species UNSG
+is linked to 12 from 204 species, named:
+  REPH MASH RBME ROYT UBBG UNLA UNST AUSH 
+ATPU BRPE UNPH UNSH
+
+species UNST
+is linked to 66 from 204 species, named:
+  AMGO AMKE AMOY AMRO BBPL BHCO BHGU RNPH 
+REPH ROST BRBO CHSW DUNL EUST FOTE
+ SBDO GRYE HADU HOME LEYE NOPI MALL MASH 
+PAWA PESA PISI RBNU REDH RUDU RUTU
+ RWBL SAGU SATE SCAU SEPL SOSP POJA RBME 
+RBGU UBBG UCAT UNEI UNFR UNPE UNLA
+ UNME UNSG BANS WHIM GREG MODO WIPH WODU 
+YCNH YRWA AUSH BRPE BRSP BLKI BCPE
+ BOGU BRNO CANG COGO DASC AWPE
+
+species UNTB
+is linked to 0 from 204 species
+
+species WTTR
+is linked to 14 from 204 species, named:
+  ABDU GRCO CATE LIGU HEPE LTJA PUMA RNGR 
+SAND TRES UNWA MYWA BRTE BLTE
+
+species WWSC
+is linked to 6 from 204 species, named:
+ COSH RAZO RTLO UNTE COTE WISP
+
+species BANS
+is linked to 80 from 204 species
+  COLO DOVE GBBG AMGO AMKE AMOY AMRO BBPL
+ BHCO BHGU ROST BRBO CHSW COME DEJU
+ DUNL EUST GADW GRHE GBHE SBDO GRYE HADU 
+HOME LESA LEYE LIGU NOPI ICGU LAGU
+ MALL OSPR PAWA PEEP PESA PISI PUSA RBNU 
+REDH RUDU RUTU RWBL SAGU SATE SCAU
+ SEPL SESA SOSP POJA RBGU SPSA TRES UCAT 
+ULSB UNBI UNEI UNFR UNPE UNLG UNME
+ UNST MYWA WFSP WHIM GLGU GOME GREG MODO 
+WILL WIPH WODU YCNH YRWA UCRT BLKI
+ BCPE BOGU BRNO CANG AWPE
+
+species UNWA
+is linked to 23 from 204 species, named:
+  ABDU GRCO CATE COME DEJU GBHE LESA LIGU
+ HEPE LTJA OSPR PUMA RNGR SAND SESA
+ TRES WTTR MYWA WFSP GLGU GOME BRTE BLTE
+
+species USAN
+is linked to 0 from 204 species
+
+species USSB
+is linked to 3 from 204 species, named:
+ GRSC GWTE UNDU
+
+species MYWA
+is linked to 48 from 204 species, named:
+  ABDU BHCO BHGU GRCO CATE COME DEJU DUNL
+ GADW GRHE GBHE LESA LIGU HEPE ICGU
+ LTJA MALL OSPR PEEP PUMA PUSA REDH RWBL 
+SAND SEPL SESA SOSP SPSA TRES ULSB
+ UNEI UNPE WTTR BANS UNWA WFSP WHIM GLGU 
+GOME MODO BRTE WILL WODU YRWA UCRT
+ BLTE CANG AWPE
+
+species WFSP
+is linked to 72 from 204 species, named:
+  AMGO AMKE AMOY AMRO BBPL BHCO BHGU GRCO
+ BRBO CATE CHSW COME DEJU DUNL EUST
+ GADW GRHE GBHE SBDO GRYE HADU HOME LESA 
+LEYE LIGU NOPI ICGU LTJA MALL OSPR
+ PAWA PEEP PESA PISI PUMA PUSA RBNU REDH 
+RUDU RUTU RWBL SAGU SAND SATE SEPL
+ SESA SOSP SPSA TRES UCAT ULSB UNEI UNFR
+ UNPE BANS UNWA MYWA WHIM GLGU GOME
+ GREG MODO WILL WIPH WODU YCNH YRWA UCRT
+ BLTE BRNO CANG AWPE
+
+species WHIM
+is linked to 80 from 204 species
+  COLO DOVE GBBG AMGO AMKE AMOY AMRO BBPL
+ BHCO BHGU ROST BRBO CHSW COME DEJU
+ DUNL EUST GADW GRHE GBHE SBDO GRYE HADU 
+HOME LESA LEYE LIGU NOPI ICGU LAGU
+ MALL OSPR PAWA PEEP PESA PISI PUSA RBNU
+ REDH RUDU RUTU RWBL SAGU SATE SCAU
+ SEPL SESA SOSP POJA RBGU SPSA TRES UCAT
+ ULSB UNBI UNEI UNFR UNPE UNLG UNME
+ UNST BANS MYWA WFSP GLGU GOME GREG MODO
+ WILL WIPH WODU YCNH YRWA UCRT BLKI
+ BCPE BOGU BRNO CANG AWPE
+
+species BLPW
+is linked to 0 from 204 species
+
+species BTBW
+is linked to 0 from 204 species
+
+species GLGU
+is linked to 74 from 204 species, named:
+  AMGO AMKE AMOY AMRO BBPL BHCO BHGU GRCO
+ BRBO CATE CHSW COME DEJU DUNL EUST
+ GADW GRHE GBHE SBDO GRYE HADU HOME LESA
+ LEYE LIGU MAFR NOPI ICGU LTJA MALL
+ OSPR PAWA PEEP PESA PISI PUMA PUSA RBNU
+ REDH RUDU RUTU RWBL SAGU SAND SATE
+ SEPL SESA SOSP SPSA TRES UCAT ULSB UNEI
+ UNFR UNPE BANS UNWA MYWA WFSP WHIM
+ GOME GREG MODO BRTE WILL WIPH WODU YCNH
+ YRWA UCRT BLTE BRNO CANG AWPE
+
+species GOME
+is linked to 69 from 204 species, named:
+  AMGO AMKE AMOY AMRO BBPL BHCO BHGU BRBO
+ CATE CHSW COME DEJU DUNL EUST GADW
+ GRHE GBHE SBDO GRYE HADU HOME LESA LEYE
+ LIGU NOPI ICGU LTJA MALL OSPR PAWA
+ PEEP PESA PISI PUSA RBNU REDH RUDU RUTU
+ RWBL SAGU SATE SEPL SESA SOSP SPSA
+ TRES UCAT ULSB UNEI UNFR UNPE BANS UNWA
+ MYWA WFSP WHIM GLGU GREG MODO WILL
+ WIPH WODU YCNH YRWA UCRT BLTE BRNO CANG AWPE
+
+species GREG
+is linked to 79 from 204 species, named:
+  COLO DOVE GBBG AMGO AMKE AMOY AMRO BBPL
+ BHCO BHGU GRSH ROST BRBO CHSW COME
+ DEJU DUNL EUST GADW GRHE GBHE SBDO GRYE
+ HADU HOME LESA LEYE NOPI ICGU LAGU
+ MALL OSPR PAWA PEEP PESA PISI PUSA RBNU
+ REDH RUDU RUTU RWBL SAGU SATE SCAU
+ SEPL SESA SOSP POJA RBGU SPSA TRES UCAT
+ ULSB UNBI UNEI UNFR UNPE UNLG UNME
+ UNST BANS WFSP WHIM GLGU GOME MODO WILL
+ WIPH WODU YCNH YRWA UCRT BLKI BCPE
+ BOGU BRNO CANG AWPE
+
+species MERL
+is linked to 0 from 204 species
+
+species MODO
+is linked to 78 from 204 species, named:
+  COLO GBBG AMGO AMKE AMOY AMRO BBPL BHCO
+ BHGU ROST BRBO CHSW COME DEJU DUNL
+ EUST GADW GRHE GBHE SBDO GRYE HADU HOME
+ LESA LEYE LIGU NOPI ICGU LAGU MALL
+ OSPR PAWA PEEP PESA PISI PUSA RBNU REDH
+ RUDU RUTU RWBL SAGU SATE SCAU SEPL
+ SESA SOSP POJA RBGU SPSA TRES UCAT ULSB
+ UNBI UNEI UNFR UNPE UNME UNST BANS
+ MYWA WFSP WHIM GLGU GOME GREG WILL WIPH
+ WODU YCNH YRWA UCRT BLKI BCPE BOGU
+ BRNO CANG AWPE
+
+species RUBL
+is linked to 0 from 204 species
+
+species BRTE
+is linked to 20 from 204 species
+  ABDU GRCO CATE DEJU GBHE LESA LIGU MAFR
+ HEPE LTJA OSPR PUMA RNGR SAND TRES
+ WTTR UNWA MYWA GLGU BLTE
+
+species UNSK
+is linked to 8 from 204 species, named:
+ BARS LBBG SHOR UNGO UNJA TBMU UNGR UNMU
+
+species UNSP
+is linked to 27 from 204 species, named:
+  BLSC COLO DCCO DOVE GBBG LTDU NOGA GRSH
+ RNPH ROST UNCO FOTE LAGU POJA RBGU
+ SOSH UNBI UNDD UNLT UNLG UNME BRSP BLKI
+ BCPE BOGU COGO DASC
+
+species UNTE
+is linked to 7 from 204 species, named:
+ BLSC COSH RAZO RTLO WWSC COTE WISP
+
+species WILL
+is linked to 59 from 204 species, named:
+  AMKE AMRO BBPL BHCO BHGU BRBO CHSW COME
+ DEJU DUNL EUST GADW GRHE GBHE SBDO
+ GRYE HADU HOME LESA LEYE LIGU NOPI MALL
+ OSPR PAWA PESA PISI PUSA RBNU REDH
+ RUDU RUTU RWBL SAGU SATE SEPL SESA SOSP
+ SPSA TRES ULSB UNEI UNFR UNPE BANS
+ MYWA WFSP WHIM GLGU GOME GREG MODO WIPH
+ WODU YCNH YRWA UCRT BRNO AWPE
+
+species WIPH
+is linked to 79 from 204 species, named:
+  COLO DOVE GBBG AMGO AMKE AMOY AMRO BBPL
+ BHCO BHGU GRSH ROST BRBO CHSW COME
+ DEJU DUNL EUST GADW GRHE GBHE SBDO GRYE
+ HADU HOME LESA LEYE NOPI ICGU LAGU
+ MALL OSPR PAWA PEEP PESA PISI PUSA RBNU 
+REDH RUDU RUTU RWBL SAGU SATE SCAU
+ SEPL SESA SOSP POJA RBGU SPSA TRES UCAT
+ ULSB UNBI UNEI UNFR UNPE UNLG UNME
+ UNST BANS WFSP WHIM GLGU GOME GREG MODO
+ WILL WODU YCNH YRWA UCRT BLKI BCPE
+ BOGU BRNO CANG AWPE
+
+species WODU
+is linked to 80 from 204 species
+  COLO DOVE GBBG AMGO AMKE AMOY AMRO BBPL
+ BHCO BHGU ROST BRBO CHSW COME DEJU
+ DUNL EUST GADW GRHE GBHE SBDO GRYE HADU 
+HOME LESA LEYE LIGU NOPI ICGU LAGU
+ MALL OSPR PAWA PEEP PESA PISI PUSA RBNU
+ REDH RUDU RUTU RWBL SAGU SATE SCAU
+ SEPL SESA SOSP POJA RBGU SPSA TRES UCAT
+ ULSB UNBI UNEI UNFR UNPE UNLG UNME
+ UNST BANS MYWA WFSP WHIM GLGU GOME GREG
+ MODO WILL WIPH YCNH YRWA UCRT BLKI
+ BCPE BOGU BRNO CANG AWPE
+
+species WTSP
+is linked to 0 from 204 species
+
+species YBCH
+is linked to 0 from 204 species
+
+species YCNH
+is linked to 79 from 204 species, named:
+  COLO DOVE GBBG AMGO AMKE AMOY AMRO BBPL
+ BHCO BHGU GRSH ROST BRBO CHSW COME
+ DEJU DUNL EUST GADW GRHE GBHE SBDO GRYE
+ HADU HOME LESA LEYE NOPI ICGU LAGU
+ MALL OSPR PAWA PEEP PESA PISI PUSA RBNU
+ REDH RUDU RUTU RWBL SAGU SATE SCAU
+ SEPL SESA SOSP POJA RBGU SPSA TRES UCAT
+ ULSB UNBI UNEI UNFR UNPE UNLG UNME
+ UNST BANS WFSP WHIM GLGU GOME GREG MODO
+ WILL WIPH WODU YRWA UCRT BLKI BCPE
+ BOGU BRNO CANG AWPE
+
+species YRWA
+is linked to 78 from 204 species, named:
+  COLO GBBG AMGO AMKE AMOY AMRO BBPL BHCO BHGU
+ ROST BRBO CHSW COME DEJU DUNL
+ EUST GADW GRHE GBHE SBDO GRYE HADU HOME LESA
+ LEYE LIGU NOPI ICGU LAGU MALL
+ OSPR PAWA PEEP PESA PISI PUSA RBNU REDH RUDU
+ RUTU RWBL SAGU SATE SCAU SEPL
+ SESA SOSP POJA RBGU SPSA TRES UCAT ULSB UNBI
+ UNEI UNFR UNPE UNME UNST BANS
+ MYWA WFSP WHIM GLGU GOME GREG MODO WILL WIPH
+ WODU YCNH UCRT BLKI BCPE BOGU
+ BRNO CANG AWPE
+
+species YWAR
+is linked to 0 from 204 species
+
+species UNFI
+is linked to 5 from 204 species, named:
+ CEDW GBTE SNGO UNEG UNSA
+
+species UCRT
+is linked to 59 from 204 species, named:
+  AMKE AMRO BBPL BHCO BHGU BRBO CHSW COME
+ DEJU DUNL EUST GADW GRHE GBHE SBDO
+ GRYE HADU HOME LESA LEYE LIGU NOPI MALL
+ OSPR PAWA PESA PISI PUSA RBNU REDH
+ RUDU RUTU RWBL SAGU SATE SEPL SESA SOSP
+ SPSA TRES ULSB UNEI UNFR UNPE BANS
+ MYWA WFSP WHIM GLGU GOME GREG MODO WILL
+ WIPH WODU YCNH YRWA BRNO AWPE
+
+species AUSH
+is linked to 9 from 204 species, named:
+ REPH MASH RBME UBBG UNLA UNSG UNST ATPU
+ BRPE
+
+species RTHU
+is linked to 0 from 204 species
+
+species BRAN
+is linked to 0 from 204 species
+
+species UNHU
+is linked to 0 from 204 species
+
+species ATPU
+is linked to 11 from 204 species, named:
+  REPH MASH RBME ROYT UBBG UNLA UNSG AUSH
+ BRPE UNPH UNSH
+
+species BLGU
+is linked to 8 from 204 species, named:
+ COMU ARTE UNCO LETE UNDD UNPA SPSK PAJA
+
+species BRPE
+is linked to 12 from 204 species, named:
+  REPH MASH RBME ROYT UBBG UNLA UNSG UNST
+ AUSH ATPU UNPH UNSH
+
+species HERG
+is linked to 1/204 vertex, named:
+ NOGA
+
+species PAJA
+is linked to 7 from 204 species, named:
+ COMU ARTE UNCO LETE UNDD SPSK BLGU
+
+species BRSP
+is linked to 28 from 204 species, named:
+  COLO DCCO DOVE GBBG NOGA GRSH RNPH ROST
+ UNCO FOTE GRSK LAGU SCAU POJA RBGU
+ SOSH UNBI UNDD UNLT UNLG UNME UNST UNSP
+ BLKI BCPE BOGU COGO DASC
+
+species BLKI
+is linked to 62 from 204 species, named:
+  DOVE AMGO AMKE AMOY AMRO BBPL BHCO BHGU
+ RNPH ROST BRBO CHSW DUNL EUST SBDO
+ GRYE HADU HOME LEYE NOPI LESP MALL PAWA
+ PEEP PESA PISI RBNU REDH RUDU RUTU
+ RWBL SAGU SATE SEPL SOSP POJA RBGU UCAT
+ UNBI UNEI UNFR UNPE UNLG UNME UNST
+ BANS WHIM GREG MODO UNSP WIPH WODU YCNH
+ YRWA BRSP BCPE BOGU BRNO CANG COGO
+ DASC AWPE
+
+species BCPE
+is linked to 64 from 204 species, named:
+  DOVE AMGO AMKE AMOY AMRO BBPL BHCO BHGU
+ RNPH REPH ROST BRBO CHSW DUNL EUST
+ FOTE SBDO GRYE HADU HOME LEYE NOPI HOGR
+ LAGU MALL MASH PAWA PESA PISI RBNU
+ REDH RUDU RUTU SAGU SATE SCAU POJA RBME
+ RBGU SOSH UBBG UCAT UNBI UNFR UNPE
+ UNLA UNLG UNME UNST BANS WHIM GREG MODO
+ UNSP WIPH WODU YCNH YRWA BRSP BLKI
+ BOGU BRNO COGO DASC
+
+species BLTE
+is linked to 24 from 204 species, named:
+  ABDU GRCO CATE COME DEJU GBHE LESA LIGU
+ MAFR HEPE LTJA OSPR PUMA RNGR SAND
+ SESA TRES WTTR UNWA MYWA WFSP GLGU GOME BRTE
+
+species BOGU
+is linked to 63 from 204 species, named:
+  DOVE AMGO AMKE AMOY AMRO BBPL BHCO BHGU
+ RNPH ROST BRBO CHSW DUNL EUST FOTE
+ SBDO GRYE HADU HOME LEYE NOPI LESP MALL
+ PAWA PEEP PESA PISI RBNU REDH RUDU
+ RUTU RWBL SAGU SATE SEPL SOSP POJA RBGU
+ UCAT UNBI UNEI UNFR UNPE UNLG UNME
+ UNST BANS WHIM GREG MODO UNSP WIPH WODU
+ YCNH YRWA BRSP BLKI BCPE BRNO CANG
+ COGO DASC AWPE
+
+species BRNO
+is linked to 79 from 204 species, named:
+  COLO DOVE GBBG AMGO AMKE AMOY AMRO BBPL
+ BHCO BHGU GRSH ROST BRBO CHSW COME
+ DEJU DUNL EUST GADW GRHE GBHE SBDO GRYE
+ HADU HOME LESA LEYE NOPI ICGU LAGU
+ MALL OSPR PAWA PEEP PESA PISI PUSA RBNU
+ REDH RUDU RUTU RWBL SAGU SATE SCAU
+ SEPL SESA SOSP POJA RBGU SPSA TRES UCAT
+ ULSB UNBI UNEI UNFR UNPE UNLG UNME
+ UNST BANS WFSP WHIM GLGU GOME GREG MODO
+ WILL WIPH WODU YCNH YRWA UCRT BLKI
+ BCPE BOGU CANG AWPE
+
+species BUFF
+is linked to 2 from 204 species, named:
+ DCCO UNAL
+
+species CANG
+is linked to 64 from 204 species, named:
+  AMGO AMKE AMOY AMRO BBPL BHCO BHGU BRBO
+ CHSW COME DEJU DUNL EUST GBHE SBDO
+ GRYE HADU HOME LESA LEYE LIGU NOPI ICGU
+ LAGU MALL OSPR PAWA PEEP PESA PISI
+ RBNU REDH RUDU RUTU RWBL SAGU SATE SCAU
+ SEPL SESA SOSP RBGU TRES UCAT UNEI
+ UNFR UNPE UNST BANS MYWA WFSP WHIM GLGU
+ GOME GREG MODO WIPH WODU YCNH YRWA
+ BLKI BOGU BRNO AWPE
+
+species COEI
+is linked to 3 from 204 species, named:
+ UNSC UNGU UNLO
+
+species COGO
+is linked to 26 from 204 species, named:
+  COLO DCCO DOVE GBBG NOGA GRSH RNPH ROST
+ FOTE LAGU SCAU POJA RBGU SOSH UNBI
+ UNDD UNLT UNLG UNME UNST UNSP BRSP BLKI BCPE BOGU DASC
+
+species COTE
+is linked to 5 from 204 species, named:
+ COSH NOFU LESP WWSC UNTE
+
+species WISP
+is linked to 5 from 204 species, named:
+ COSH RAZO RTLO WWSC UNTE
+
+species UNPH
+is linked to 6 from 204 species, named:
+ ROYT UNAL UNSG ATPU BRPE UNSH
+
+species UNSH
+is linked to 6 from 204 species, named:
+ ROYT UNAL UNSG ATPU BRPE UNPH
+
+species DASC
+is linked to 23 from 204 species, named:
+  DOVE GBBG RNPH ROST FOTE LAGU MASH SCAU
+ POJA RBGU SOSH SOTE UNBI UNLT UNLG
+ UNME UNST UNSP BRSP BLKI BCPE BOGU COGO
+
+species AWPE
+is linked to 70 from 204 species
+  AMGO AMKE AMOY AMRO BBPL BHCO BHGU BRBO
+ CHSW COME DEJU DUNL EUST GADW GRHE
+ GBHE SBDO GRYE HADU HOME LESA LEYE LIGU
+ NOPI ICGU MALL OSPR PAWA PEEP PESA
+ PISI PUSA RBNU REDH RUDU RUTU RWBL SAGU
+ SATE SCAU SEPL SESA SOSP RBGU SPSA
+ TRES UCAT ULSB UNEI UNFR UNPE UNST BANS
+ MYWA WFSP WHIM GLGU GOME GREG MODO
+ WILL WIPH WODU YCNH YRWA UCRT BLKI BOGU BRNO CANG
+
+species BUPE
+is linked to 0 from 204 species
+
+\end{lstlisting}
+
+\subsection*{Neighbors for $\alpha=0.6$}
+
+We found the following structure for the threshold $\alpha=.6$
+\begin{lstlisting}
+species BLSC
+is linked to 9 from 204 species, named:
+ COLO DCCO GBBG LTDU NOGA GRSH RAZO 
+    SOSH UNLT
+
+species COLO
+is linked to 9 from 204 species, named:
+ BLSC DOVE GBBG LTDU NOGA GRSH SOSH 
+    UNLT UNSP
+
+species COMU
+is linked to 7 from 204 species, named:
+ ARTE UNCO LETE UNDD SPSK BLGU PAJA
+
+species COSH
+is linked to 2 from 204 species, named:
+ WWSC UNTE
+
+species DCCO
+is linked to 6 from 204 species, named:
+ BLSC LTDU RAZO SOSH UNLT BUFF
+
+species DOVE
+is linked to 13 from 204 species, named:
+ COLO GBBG GRSH RNPH FOTE LAGU 
+ SOSH UNBI UNLT UNLG UNSP BRSP COGO
+
+species GBBG
+is linked to 10 from 204 species, named:
+ BLSC COLO DOVE LTDU GRSH LAGU
+ SOSH UNLT UNLG UNSP
+
+species LTDU
+is linked to 9 from 204 species, named
+ BLSC COLO DCCO GBBG NOGA GRSH 
+ RAZO SOSH UNLT
+
+species NOFU
+is linked to 2 from 204 species, named:
+ LESP COTE
+
+species NOGA
+is linked to 4 from 204 species, named:
+ BLSC COLO LTDU GRSH
+
+species SUSC
+is linked to 0 from 204 species, named:
+
+species ABDU
+is linked to 8 from 204 species, named:
+ GRCO HEPE PUMA RNGR SAND WTTR
+ BRTE BLTE
+
+species AMCO
+is linked to 0 from 204 species, named:
+
+species AMGO
+is linked to 52 from 204 species, named:
+  AMKE AMOY AMRO BBPL BHCO BHGU
+ BRBO CHSW COME DUNL EUST SBDO GRYE
+ HADU HOME
+ LESA LEYE NOPI ICGU MALL OSPR
+ PAWA PEEP PESA PISI RBNU REDH RUDU
+ RUTU RWBL
+ SAGU SATE SEPL SESA SOSP UCAT
+ UNEI UNFR UNPE BANS WFSP WHIM GOME
+ GREG MODO
+ WIPH WODU YCNH YRWA BRNO CANG
+ AWPE
+
+species AMKE
+is linked to 52 from 204 species, named:
+  AMGO AMOY AMRO BBPL BHCO BHGU 
+    BRBO CHSW COME DUNL EUST SBDO 
+GRYE HADU HOME
+ LESA LEYE NOPI ICGU MALL OSPR 
+PAWA PEEP PESA PISI RBNU REDH RUDU RUTU
+ RWBL
+ SAGU SATE SEPL SESA SOSP UCAT
+ UNEI UNFR UNPE BANS WFSP WHIM GOME
+ GREG MODO
+ WIPH WODU YCNH YRWA BRNO CANG AWPE
+
+species AMOY
+is linked to 52 from 204 species, named:
+  AMGO AMKE AMRO BBPL BHCO BHGU 
+BRBO CHSW COME DUNL EUST SBDO GRYE HADU HOME
+ LESA LEYE NOPI ICGU MALL OSPR 
+PAWA PEEP PESA PISI RBNU REDH RUDU RUTU RWBL
+ SAGU SATE SEPL SESA SOSP UCAT 
+UNEI UNFR UNPE BANS WFSP WHIM GOME GREG MODO
+ WIPH WODU YCNH YRWA BRNO CANG AWPE
+
+species AMPI
+is linked to 0 from 204 species, named:
+
+species AMRE
+is linked to 0 from 204 species, named:
+
+species AMRO
+is linked to 52 from 204 species, named:
+  AMGO AMKE AMOY BBPL BHCO BHGU 
+BRBO CHSW COME DUNL EUST SBDO GRYE HADU HOME
+ LESA LEYE NOPI ICGU MALL OSPR 
+PAWA PEEP PESA PISI RBNU REDH RUDU RUTU RWBL
+ SAGU SATE SEPL SESA SOSP UCAT 
+UNEI UNFR UNPE BANS WFSP WHIM GOME GREG MODO
+ WIPH WODU YCNH YRWA BRNO CANG AWPE
+
+species BAOR
+is linked to 0 from 204 species, named:
+
+species BARS
+is linked to 6 from 204 species, named:
+ LBBG GRSK HOGR SOTE SHOR UNGR
+
+species BBPL
+is linked to 52 from 204 species, named:
+  AMGO AMKE AMOY AMRO BHCO BHGU BRBO
+ CHSW COME DUNL EUST SBDO GRYE HADU HOME
+ LESA LEYE NOPI ICGU MALL OSPR PAWA
+ PEEP PESA PISI RBNU REDH RUDU RUTU RWBL
+ SAGU SATE SEPL SESA SOSP UCAT UNEI
+ UNFR UNPE BANS WFSP WHIM GOME GREG MODO
+ WIPH WODU YCNH YRWA BRNO CANG AWPE
+
+species BHCO
+is linked to 55 from 204 species, named:
+  AMGO AMKE AMOY AMRO BBPL BHGU BRBO
+ CHSW COME DEJU DUNL EUST GBHE SBDO GRYE
+ HADU HOME LESA LEYE NOPI ICGU MALL
+ OSPR PAWA PEEP PESA PISI RBNU REDH RUDU
+ RUTU RWBL SAGU SATE SEPL SESA SOSP
+ UCAT UNEI UNFR UNPE BANS WFSP WHIM GLGU
+ GOME GREG MODO WIPH WODU YCNH YRWA
+ BRNO CANG AWPE
+
+species BHGU
+is linked to 55 from 204 species, named:
+  AMGO AMKE AMOY AMRO BBPL BHCO BRBO
+ CHSW COME DEJU DUNL EUST GBHE SBDO GRYE
+ HADU HOME LESA LEYE NOPI ICGU MALL
+ OSPR PAWA PEEP PESA PISI RBNU REDH RUDU
+ RUTU RWBL SAGU SATE SEPL SESA SOSP
+ UCAT UNEI UNFR UNPE BANS WFSP WHIM GLGU
+ GOME GREG MODO WIPH WODU YCNH YRWA
+ BRNO CANG AWPE
+
+species ARTE
+is linked to 7 from 204 species, named:
+ COMU UNCO LETE UNDD SPSK BLGU PAJA
+
+species GRCO
+is linked to 14 from 204 species, named:
+  ABDU CATE GBHE LIGU HEPE LTJA PUMA
+ SAND TRES WTTR UNWA MYWA BRTE BLTE
+
+species GRSH
+is linked to 8 from 204 species, named:
+ BLSC COLO DOVE GBBG LTDU NOGA SOSH UNLT
+
+species RAZO
+is linked to 4 from 204 species, named:
+ BLSC DCCO LTDU UNTE
+
+species RNPH
+is linked to 13 from 204 species, named:
+  DOVE ROST FOTE POJA UNBI UNLG UNME
+ UNST UNSP BRSP BCPE COGO DASC
+
+species RTLO
+is linked to 1 from 204 vertex, named:
+ WISP
+
+species REPH
+is linked to 10 from 204 species, named:
+  MASH RBME UBBG UNLA UNME UNSG UNST
+ AUSH ATPU BRPE
+
+species ROST
+is linked to 13 from 204 species, named:
+  RNPH FOTE SCAU POJA RBGU UNME UNST
+ BRSP BLKI BCPE BOGU COGO DASC
+
+species UNCO
+is linked to 5 from 204 species, named:
+ COMU ARTE LETE UNDD SPSK
+
+species UNSC
+is linked to 3 from 204 species, named:
+ UNGU UNLO COEI
+
+species BRBO
+is linked to 52 from 204 species, named:
+  AMGO AMKE AMOY AMRO BBPL BHCO BHGU
+ CHSW COME DUNL EUST SBDO GRYE HADU HOME
+ LESA LEYE NOPI ICGU MALL OSPR PAWA
+ PEEP PESA PISI RBNU REDH RUDU RUTU RWBL
+ SAGU SATE SEPL SESA SOSP UCAT UNEI
+ UNFR UNPE BANS WFSP WHIM GOME GREG MODO
+ WIPH WODU YCNH YRWA BRNO CANG AWPE
+
+species CATE
+is linked to 15 from 204 species, named:
+  GRCO DEJU GBHE LIGU HEPE LTJA PUMA
+ SAND TRES WTTR UNWA MYWA GLGU BRTE BLTE
+
+species CEDW
+is linked to 5 from 204 species, named:
+ GBTE SNGO UNEG UNSA UNFI
+
+species CHSW
+is linked to 53 from 204 species, named:
+  AMGO AMKE AMOY AMRO BBPL BHCO BHGU
+ BRBO COME DUNL EUST GBHE SBDO GRYE HADU
+ HOME LESA LEYE NOPI ICGU MALL OSPR
+ PAWA PEEP PESA PISI RBNU REDH RUDU RUTU
+ RWBL SAGU SATE SEPL SESA SOSP UCAT
+ UNEI UNFR UNPE BANS WFSP WHIM GOME GREG
+ MODO WIPH WODU YCNH YRWA BRNO CANG
+ AWPE
+
+species COME
+is linked to 58 from 204 species, named:
+  AMGO AMKE AMOY AMRO BBPL BHCO BHGU
+ BRBO CHSW DEJU DUNL EUST GBHE SBDO GRYE
+ HADU HOME LESA LEYE LIGU NOPI ICGU
+ MALL OSPR PAWA PEEP PESA PISI RBNU REDH
+ RUDU RUTU RWBL SAGU SATE SEPL SESA
+ SOSP TRES UCAT UNEI UNFR UNPE BANS MYWA
+ WFSP WHIM GLGU GOME GREG MODO WIPH
+ WODU YCNH YRWA BRNO CANG AWPE
+
+species COYE
+is linked to 0 from 204 species, named:
+
+species DEJU
+is linked to 26 from 204 species, named:
+  BHCO BHGU CATE COME DUNL GBHE LESA
+ LIGU ICGU OSPR REDH RWBL SEPL SESA SOSP
+ TRES UNEI UNPE MYWA WFSP GLGU GOME
+ MODO YRWA CANG AWPE
+
+species DUNL
+is linked to 55 from 204 species, named:
+  AMGO AMKE AMOY AMRO BBPL BHCO BHGU
+ BRBO CHSW COME DEJU EUST GBHE SBDO GRYE
+ HADU HOME LESA LEYE NOPI ICGU MALL
+ OSPR PAWA PEEP PESA PISI RBNU REDH RUDU
+ RUTU RWBL SAGU SATE SEPL SESA SOSP
+ UCAT UNEI UNFR UNPE BANS WFSP WHIM GLGU
+ GOME GREG MODO WIPH WODU YCNH YRWA
+ BRNO CANG AWPE
+
+species EUST
+is linked to 52 from 204 species, named:
+  AMGO AMKE AMOY AMRO BBPL BHCO BHGU
+ BRBO CHSW COME DUNL SBDO GRYE HADU HOME
+ LESA LEYE NOPI ICGU MALL OSPR PAWA
+ PEEP PESA PISI RBNU REDH RUDU RUTU RWBL
+ SAGU SATE SEPL SESA SOSP UCAT UNEI
+ UNFR UNPE BANS WFSP WHIM GOME GREG MODO
+ WIPH WODU YCNH YRWA BRNO CANG AWPE
+
+species FEPE
+is linked to 0 from 204 species, named:
+
+species FOTE
+is linked to 13 from 204 species, named:
+  DOVE RNPH ROST POJA UNBI UNLG UNME
+ UNST UNSP BRSP BCPE COGO DASC
+
+species GADW
+is linked to 6 from 204 species, named:
+ GRHE PUSA SPSA ULSB WILL UCRT
+
+species GBTE
+is linked to 5 from 204 species, named:
+ CEDW SNGO UNEG UNSA UNFI
+
+species GCKI
+is linked to 0 from 204 species, named:
+
+species GRCA
+is linked to 0 from 204 species, named:
+
+species GRHE
+is linked to 6 from 204 species, named:
+ GADW PUSA SPSA ULSB WILL UCRT
+
+species GRSC
+is linked to 2 from 204 species, named:
+ GWTE USSB
+
+species GBHE
+is linked to 41 from 204 species, named:
+  BHCO BHGU GRCO CATE CHSW COME DEJU
+ DUNL LESA LIGU ICGU LTJA MALL OSPR PAWA
+ PEEP PUMA REDH RUTU RWBL SAND SEPL
+ SESA SOSP TRES UNEI UNFR UNPE BANS UNWA
+ MYWA WFSP WHIM GLGU GOME MODO WODU
+ YRWA BLTE CANG AWPE
+
+species SBDO
+is linked to 52 from 204 species, named:
+  AMGO AMKE AMOY AMRO BBPL BHCO BHGU
+ BRBO CHSW COME DUNL EUST GRYE HADU HOME
+ LESA LEYE NOPI ICGU MALL OSPR PAWA
+ PEEP PESA PISI RBNU REDH RUDU RUTU RWBL
+ SAGU SATE SEPL SESA SOSP UCAT UNEI
+ UNFR UNPE BANS WFSP WHIM GOME GREG MODO
+ WIPH WODU YCNH YRWA BRNO CANG AWPE
+
+species GRYE
+is linked to 52 from 204 species, named:
+  AMGO AMKE AMOY AMRO BBPL BHCO BHGU
+ BRBO CHSW COME DUNL EUST SBDO HADU HOME
+ LESA LEYE NOPI ICGU MALL OSPR PAWA
+ PEEP PESA PISI RBNU REDH RUDU RUTU RWBL
+ SAGU SATE SEPL SESA SOSP UCAT UNEI
+ UNFR UNPE BANS WFSP WHIM GOME GREG MODO
+ WIPH WODU YCNH YRWA BRNO CANG AWPE
+
+species GWTE
+is linked to 2 from 204 species, named:
+ GRSC USSB
+
+species HADU
+is linked to 52 from 204 species, named:
+  AMGO AMKE AMOY AMRO BBPL BHCO BHGU
+ BRBO CHSW COME DUNL EUST SBDO GRYE HOME
+ LESA LEYE NOPI ICGU MALL OSPR PAWA
+ PEEP PESA PISI RBNU REDH RUDU RUTU RWBL
+ SAGU SATE SEPL SESA SOSP UCAT UNEI
+ UNFR UNPE BANS WFSP WHIM GOME GREG MODO
+ WIPH WODU YCNH YRWA BRNO CANG AWPE
+
+species HOME
+is linked to 52 from 204 species, named:
+  AMGO AMKE AMOY AMRO BBPL BHCO BHGU
+ BRBO CHSW COME DUNL EUST SBDO GRYE HADU
+ LESA LEYE NOPI ICGU MALL OSPR PAWA
+ PEEP PESA PISI RBNU REDH RUDU RUTU RWBL
+ SAGU SATE SEPL SESA SOSP UCAT UNEI
+ UNFR UNPE BANS WFSP WHIM GOME GREG MODO
+ WIPH WODU YCNH YRWA BRNO CANG AWPE
+
+species LBBG
+is linked to 6 from 204 species, named:
+ BARS SHOR UNJA TBMU UNGR UNSK
+
+species LESA
+is linked to 58 from 204 species, named:
+  AMGO AMKE AMOY AMRO BBPL BHCO BHGU
+ BRBO CHSW COME DEJU DUNL EUST GBHE SBDO
+ GRYE HADU HOME LEYE LIGU NOPI ICGU
+ MALL OSPR PAWA PEEP PESA PISI RBNU REDH
+ RUDU RUTU RWBL SAGU SATE SEPL SESA
+ SOSP TRES UCAT UNEI UNFR UNPE BANS MYWA
+ WFSP WHIM GLGU GOME GREG MODO WIPH
+ WODU YCNH YRWA BRNO CANG AWPE
+
+species LESC
+is linked to 0 from 204 species, named:
+
+species LEYE
+is linked to 52 from 204 species, named:
+  AMGO AMKE AMOY AMRO BBPL BHCO BHGU
+ BRBO CHSW COME DUNL EUST SBDO GRYE HADU
+ HOME LESA NOPI ICGU MALL OSPR PAWA
+ PEEP PESA PISI RBNU REDH RUDU RUTU RWBL
+ SAGU SATE SEPL SESA SOSP UCAT UNEI
+ UNFR UNPE BANS WFSP WHIM GOME GREG MODO
+ WIPH WODU YCNH YRWA BRNO CANG AWPE
+
+species LIGU
+is linked to 20 from 204 species, named:
+  GRCO CATE COME DEJU GBHE LESA HEPE
+ LTJA OSPR PUMA SAND SESA TRES UNWA MYWA
+ WFSP GLGU GOME BRTE BLTE
+
+species LISH
+is linked to 0 from 204 species, named:
+
+species MABO
+is linked to 0 from 204 species, named:
+
+species MAFR
+is linked to 0 from 204 species, named:
+
+species MAWA
+is linked to 0 from 204 species, named:
+
+species NOFL
+is linked to 0 from 204 species, named:
+
+species NOHA
+is linked to 0 from 204 species, named:
+
+species NOPI
+is linked to 52 from 204 species, named:
+  AMGO AMKE AMOY AMRO BBPL BHCO BHGU
+ BRBO CHSW COME DUNL EUST SBDO GRYE HADU
+ HOME LESA LEYE ICGU MALL OSPR PAWA
+ PEEP PESA PISI RBNU REDH RUDU RUTU RWBL
+ SAGU SATE SEPL SESA SOSP UCAT UNEI
+ UNFR UNPE BANS WFSP WHIM GOME GREG MODO
+ WIPH WODU YCNH YRWA BRNO CANG AWPE
+
+species NOTE
+is linked to 0 from 204 species, named:
+
+species GRSK
+is linked to 5 from 204 species, named:
+ BARS HOGR SOTE SHOR UNGR
+
+species HEPE
+is linked to 14 from 204 species, named:
+  ABDU GRCO CATE LIGU LTJA PUMA RNGR
+ SAND TRES WTTR UNWA MYWA BRTE BLTE
+
+species HOGR
+is linked to 4 from 204 species, named:
+ BARS GRSK SOTE UNGR
+
+species ICGU
+is linked to 56 from 204 species, named:
+  AMGO AMKE AMOY AMRO BBPL BHCO BHGU
+ BRBO CHSW COME DEJU DUNL EUST GBHE SBDO
+ GRYE HADU HOME LESA LEYE NOPI MALL
+ OSPR PAWA PEEP PESA PISI RBNU REDH RUDU
+ RUTU RWBL SAGU SATE SEPL SESA SOSP
+ TRES UCAT UNEI UNFR UNPE BANS WFSP WHIM
+ GLGU GOME GREG MODO WIPH WODU YCNH
+ YRWA BRNO CANG AWPE
+
+species LAGU
+is linked to 6 from 204 species, named:
+ DOVE GBBG SOSH UNLT UNLG UNSP
+
+species LESP
+is linked to 1 from 204 vertex, named:
+ NOFU
+
+species LETE
+is linked to 7 from 204 species, named:
+ COMU ARTE UNCO UNDD SPSK BLGU PAJA
+
+species LTJA
+is linked to 12 from 204 species, named:
+  GRCO CATE GBHE LIGU HEPE PUMA SAND
+ TRES UNWA MYWA BRTE BLTE
+
+species MALL
+is linked to 53 from 204 species, named:
+  AMGO AMKE AMOY AMRO BBPL BHCO BHGU
+ BRBO CHSW COME DUNL EUST GBHE SBDO GRYE
+ HADU HOME LESA LEYE NOPI ICGU OSPR
+ PAWA PEEP PESA PISI RBNU REDH RUDU RUTU
+ RWBL SAGU SATE SEPL SESA SOSP UCAT
+ UNEI UNFR UNPE BANS WFSP WHIM GOME GREG
+ MODO WIPH WODU YCNH YRWA BRNO CANG
+ AWPE
+
+species MASH
+is linked to 10 from 204 species, named:
+  REPH RBME UBBG UNLA UNME UNSG UNST
+ AUSH ATPU BRPE
+
+species NOWA
+is linked to 0 from 204 species, named:
+
+species OSPR
+is linked to 58 from 204 species, named:
+  AMGO AMKE AMOY AMRO BBPL BHCO BHGU
+ BRBO CHSW COME DEJU DUNL EUST GBHE SBDO
+ GRYE HADU HOME LESA LEYE LIGU NOPI
+ ICGU MALL PAWA PEEP PESA PISI RBNU REDH
+ RUDU RUTU RWBL SAGU SATE SEPL SESA
+ SOSP TRES UCAT UNEI UNFR UNPE BANS MYWA
+ WFSP WHIM GLGU GOME GREG MODO WIPH
+ WODU YCNH YRWA BRNO CANG AWPE
+
+species PAWA
+is linked to 53 from 204 species, named:
+  AMGO AMKE AMOY AMRO BBPL BHCO BHGU
+ BRBO CHSW COME DUNL EUST GBHE SBDO GRYE
+ HADU HOME LESA LEYE NOPI ICGU MALL
+ OSPR PEEP PESA PISI RBNU REDH RUDU RUTU
+ RWBL SAGU SATE SEPL SESA SOSP UCAT
+ UNEI UNFR UNPE BANS WFSP WHIM GOME GREG
+ MODO WIPH WODU YCNH YRWA BRNO CANG
+ AWPE
+
+species PEEP
+is linked to 53 from 204 species, named:
+  AMGO AMKE AMOY AMRO BBPL BHCO BHGU
+ BRBO CHSW COME DUNL EUST GBHE SBDO GRYE
+ HADU HOME LESA LEYE NOPI ICGU MALL
+ OSPR PAWA PESA PISI RBNU REDH RUDU RUTU
+ RWBL SAGU SATE SEPL SESA SOSP UCAT
+ UNEI UNFR UNPE BANS WFSP WHIM GOME GREG
+ MODO WIPH WODU YCNH YRWA BRNO CANG AWPE
+
+species PEFA
+is linked to 0 from 204 species, named:
+
+species PESA
+is linked to 52 from 204 species, named:
+  AMGO AMKE AMOY AMRO BBPL BHCO BHGU
+ BRBO CHSW COME DUNL EUST SBDO GRYE HADU
+ HOME LESA LEYE NOPI ICGU MALL OSPR
+ PAWA PEEP PISI RBNU REDH RUDU RUTU RWBL
+ SAGU SATE SEPL SESA SOSP UCAT UNEI
+ UNFR UNPE BANS WFSP WHIM GOME GREG MODO
+ WIPH WODU YCNH YRWA BRNO CANG AWPE
+
+species PISI
+is linked to 52 from 204 species, named:
+  AMGO AMKE AMOY AMRO BBPL BHCO BHGU
+ BRBO CHSW COME DUNL EUST SBDO GRYE HADU
+ HOME LESA LEYE NOPI ICGU MALL OSPR
+ PAWA PEEP PESA RBNU REDH RUDU RUTU RWBL
+ SAGU SATE SEPL SESA SOSP UCAT UNEI
+ UNFR UNPE BANS WFSP WHIM GOME GREG MODO
+ WIPH WODU YCNH YRWA BRNO CANG AWPE
+
+species PUMA
+is linked to 14 from 204 species, named:
+  ABDU GRCO CATE GBHE LIGU HEPE LTJA
+ SAND TRES WTTR UNWA MYWA BRTE BLTE
+
+species PUSA
+is linked to 6 from 204 species, named:
+ GADW GRHE SPSA ULSB WILL UCRT
+
+species RBNU
+is linked to 52 from 204 species, named:
+  AMGO AMKE AMOY AMRO BBPL BHCO BHGU
+ BRBO CHSW COME DUNL EUST SBDO GRYE HADU
+ HOME LESA LEYE NOPI ICGU MALL OSPR
+ PAWA PEEP PESA PISI REDH RUDU RUTU RWBL
+ SAGU SATE SEPL SESA SOSP UCAT UNEI
+ UNFR UNPE BANS WFSP WHIM GOME GREG MODO
+ WIPH WODU YCNH YRWA BRNO CANG AWPE
+
+species RBTR
+is linked to 0 from 204 species, named:
+
+species RCKI
+is linked to 0 from 204 species, named:
+
+species REDH
+is linked to 55 from 204 species, named:
+  AMGO AMKE AMOY AMRO BBPL BHCO BHGU
+ BRBO CHSW COME DEJU DUNL EUST GBHE SBDO
+ GRYE HADU HOME LESA LEYE NOPI ICGU
+ MALL OSPR PAWA PEEP PESA PISI RBNU RUDU
+ RUTU RWBL SAGU SATE SEPL SESA SOSP
+ UCAT UNEI UNFR UNPE BANS WFSP WHIM GLGU
+ GOME GREG MODO WIPH WODU YCNH YRWA
+ BRNO CANG AWPE
+
+species RNGR
+is linked to 3 from 204 species, named:
+ ABDU HEPE WTTR
+
+species RUDU
+is linked to 52 from 204 species, named:
+  AMGO AMKE AMOY AMRO BBPL BHCO BHGU
+ BRBO CHSW COME DUNL EUST SBDO GRYE HADU
+ HOME LESA LEYE NOPI ICGU MALL OSPR
+ PAWA PEEP PESA PISI RBNU REDH RUTU RWBL
+ SAGU SATE SEPL SESA SOSP UCAT UNEI
+ UNFR UNPE BANS WFSP WHIM GOME GREG MODO
+ WIPH WODU YCNH YRWA BRNO CANG AWPE
+
+species RUTU
+is linked to 53 from 204 species, named:
+  AMGO AMKE AMOY AMRO BBPL BHCO BHGU
+ BRBO CHSW COME DUNL EUST GBHE SBDO GRYE
+ HADU HOME LESA LEYE NOPI ICGU MALL
+ OSPR PAWA PEEP PESA PISI RBNU REDH RUDU
+ RWBL SAGU SATE SEPL SESA SOSP UCAT
+ UNEI UNFR UNPE BANS WFSP WHIM GOME GREG
+ MODO WIPH WODU YCNH YRWA BRNO CANG AWPE
+
+species RWBL
+is linked to 56 from 204 species, named:
+  AMGO AMKE AMOY AMRO BBPL BHCO BHGU
+ BRBO CHSW COME DEJU DUNL EUST GBHE SBDO
+ GRYE HADU HOME LESA LEYE NOPI ICGU
+ MALL OSPR PAWA PEEP PESA PISI RBNU REDH
+ RUDU RUTU SAGU SATE SEPL SESA SOSP
+ TRES UCAT UNEI UNFR UNPE BANS WFSP WHIM
+ GLGU GOME GREG MODO WIPH WODU YCNH
+ YRWA BRNO CANG AWPE
+
+species SAGU
+is linked to 52 from 204 species, named:
+  AMGO AMKE AMOY AMRO BBPL BHCO BHGU
+ BRBO CHSW COME DUNL EUST SBDO GRYE HADU
+ HOME LESA LEYE NOPI ICGU MALL OSPR
+ PAWA PEEP PESA PISI RBNU REDH RUDU RUTU
+ RWBL SATE SEPL SESA SOSP UCAT UNEI
+ UNFR UNPE BANS WFSP WHIM GOME GREG MODO
+ WIPH WODU YCNH YRWA BRNO CANG AWPE
+
+species SAND
+is linked to 14 from 204 species, named:
+  ABDU GRCO CATE GBHE LIGU HEPE LTJA
+ PUMA TRES WTTR UNWA MYWA BRTE BLTE
+
+species SATE
+is linked to 52 from 204 species, named:
+  AMGO AMKE AMOY AMRO BBPL BHCO BHGU
+ BRBO CHSW COME DUNL EUST SBDO GRYE HADU
+ HOME LESA LEYE NOPI ICGU MALL OSPR
+ PAWA PEEP PESA PISI RBNU REDH RUDU RUTU
+ RWBL SAGU SEPL SESA SOSP UCAT UNEI
+ UNFR UNPE BANS WFSP WHIM GOME GREG MODO
+ WIPH WODU YCNH YRWA BRNO CANG AWPE
+
+species SAVS
+is linked to 0 from 204 species, named:
+
+species SCAU
+is linked to 6 from 204 species, named:
+ ROST POJA UNME UNST BCPE DASC
+
+species SEPL
+is linked to 56 from 204 species, named:
+  AMGO AMKE AMOY AMRO BBPL BHCO BHGU
+ BRBO CHSW COME DEJU DUNL EUST GBHE SBDO
+ GRYE HADU HOME LESA LEYE NOPI ICGU
+ MALL OSPR PAWA PEEP PESA PISI RBNU REDH
+ RUDU RUTU RWBL SAGU SATE SESA SOSP
+ TRES UCAT UNEI UNFR UNPE BANS WFSP WHIM
+ GLGU GOME GREG MODO WIPH WODU YCNH
+ YRWA BRNO CANG AWPE
+
+species SESA
+is linked to 58 from 204 species, named:
+  AMGO AMKE AMOY AMRO BBPL BHCO BHGU
+ BRBO CHSW COME DEJU DUNL EUST GBHE SBDO
+ GRYE HADU HOME LESA LEYE LIGU NOPI
+ ICGU MALL OSPR PAWA PEEP PESA PISI RBNU
+ REDH RUDU RUTU RWBL SAGU SATE SEPL
+ SOSP TRES UCAT UNEI UNFR UNPE BANS MYWA
+ WFSP WHIM GLGU GOME GREG MODO WIPH
+ WODU YCNH YRWA BRNO CANG AWPE
+
+species SNBU
+is linked to 0 from 204 species, named:
+
+species SNGO
+is linked to 5 from 204 species, named:
+ CEDW GBTE UNEG UNSA UNFI
+
+species SOSP
+is linked to 56 from 204 species, named:
+  AMGO AMKE AMOY AMRO BBPL BHCO BHGU
+ BRBO CHSW COME DEJU DUNL EUST GBHE SBDO
+ GRYE HADU HOME LESA LEYE NOPI ICGU
+ MALL OSPR PAWA PEEP PESA PISI RBNU REDH
+ RUDU RUTU RWBL SAGU SATE SEPL SESA
+ TRES UCAT UNEI UNFR UNPE BANS WFSP WHIM
+ GLGU GOME GREG MODO WIPH WODU YCNH
+ YRWA BRNO CANG AWPE
+
+species POJA
+is linked to 11 from 204 species, named:
+  RNPH ROST FOTE SCAU UNME UNST BRSP
+ BLKI BCPE COGO DASC
+
+species RBME
+is linked to 10 from 204 species, named:
+  REPH MASH UBBG UNLA UNME UNSG UNST
+ AUSH ATPU BRPE
+
+species RBGU
+is linked to 6 from 204 species, named:
+ ROST UNBI UNLG BLKI BCPE BOGU
+
+species ROYT
+is linked to 5 from 204 species, named:
+ UNSG ATPU BRPE UNPH UNSH
+
+species SOSH
+is linked to 12 from 204 species, named:
+  BLSC COLO DCCO DOVE GBBG LTDU
+ GRSH
+ LAGU UNBI UNLT UNLG UNSP
+
+species SOTE
+is linked to 5 from 204 species, named:
+ BARS GRSK HOGR SHOR UNGR
+
+species SHOR
+is linked to 8 from 204 species, named:
+ BARS LBBG GRSK SOTE UNJA TBMU 
+UNGR UNSK
+
+species SPSA
+is linked to 6 from 204 species, named:
+ GADW GRHE PUSA ULSB WILL UCRT
+
+species TRES
+is linked to 26 from 204 species, named:
+  GRCO CATE COME DEJU GBHE LESA 
+LIGU HEPE ICGU LTJA OSPR PUMA RWBL SAND SEPL
+ SESA SOSP UNEI UNWA MYWA WFSP
+ GLGU GOME BRTE BLTE AWPE
+
+species UBBG
+is linked to 9 from 204 species, named:
+ REPH MASH RBME UNLA UNSG UNST
+ AUSH ATPU BRPE
+
+species UCAT
+is linked to 52 from 204 species, named:
+  AMGO AMKE AMOY AMRO BBPL BHCO
+ BHGU BRBO CHSW COME DUNL EUST SBDO GRYE HADU
+ HOME LESA LEYE NOPI ICGU MALL
+ OSPR PAWA PEEP PESA PISI RBNU REDH RUDU RUTU
+ RWBL SAGU SATE SEPL SESA SOSP
+ UNEI UNFR UNPE BANS WFSP WHIM GOME GREG MODO
+ WIPH WODU YCNH YRWA BRNO CANG
+ AWPE
+
+species ULSB
+is linked to 6 from 204 species, named:
+ GADW GRHE PUSA SPSA WILL UCRT
+
+species UNBI
+is linked to 13 from 204 species, named:
+  DOVE RNPH FOTE RBGU SOSH UNLT
+ UNLG UNSP BRSP BLKI BOGU COGO DASC
+
+species UNDD
+is linked to 5 from 204 species, named:
+ COMU ARTE UNCO LETE SPSK
+
+species UNEG
+is linked to 5 from 204 species, named:
+ CEDW GBTE SNGO UNSA UNFI
+
+species UNEI
+is linked to 56 from 204 species, named:
+  AMGO AMKE AMOY AMRO BBPL BHCO
+ BHGU BRBO CHSW COME DEJU DUNL EUST GBHE SBDO
+ GRYE HADU HOME LESA LEYE NOPI
+ ICGU MALL OSPR PAWA PEEP PESA PISI RBNU REDH
+ RUDU RUTU RWBL SAGU SATE SEPL
+ SESA SOSP TRES UCAT UNFR UNPE BANS WFSP WHIM
+ GLGU GOME GREG MODO WIPH WODU
+ YCNH YRWA BRNO CANG AWPE
+
+species UNFR
+is linked to 53 from 204 species, named:
+  AMGO AMKE AMOY AMRO BBPL BHCO
+ BHGU BRBO CHSW COME DUNL EUST GBHE SBDO GRYE
+ HADU HOME LESA LEYE NOPI ICGU
+ MALL OSPR PAWA PEEP PESA PISI RBNU REDH RUDU
+ RUTU RWBL SAGU SATE SEPL SESA
+ SOSP UCAT UNEI UNPE BANS WFSP WHIM GOME GREG
+ MODO WIPH WODU YCNH YRWA BRNO CANG AWPE
+
+species UNGO
+is linked to 1 from 204 vertex, named:
+ UNMU
+
+species UNLT
+is linked to 12 from 204 species, named:
+  BLSC COLO DCCO DOVE GBBG LTDU
+ GRSH LAGU SOSH UNBI UNLG UNSP
+
+species UNPA
+is linked to 0 from 204 species, named:
+
+species UNPT
+is linked to 0 from 204 species, named:
+
+species UNJA
+is linked to 4 from 204 species, named:
+ LBBG SHOR TBMU UNSK
+
+species UNPE
+is linked to 55 from 204 species, named:
+  AMGO AMKE AMOY AMRO BBPL BHCO
+ BHGU BRBO CHSW COME DEJU DUNL EUST GBHE SBDO
+ GRYE HADU HOME LESA LEYE NOPI
+ ICGU MALL OSPR PAWA PEEP PESA PISI RBNU REDH
+ RUDU RUTU RWBL SAGU SATE SEPL
+ SESA SOSP UCAT UNEI UNFR BANS WFSP WHIM GLGU
+ GOME GREG MODO WIPH WODU YCNH YRWA BRNO CANG AWPE
+
+species SPAR
+is linked to 0 from 204 species, named:
+
+species SWAL
+is linked to 0 from 204 species, named:
+
+species SPSK
+is linked to 7 from 204 species, named:
+ COMU ARTE UNCO LETE UNDD BLGU PAJA
+
+species TBMU
+is linked to 4 from 204 species, named:
+ LBBG SHOR UNJA UNSK
+
+species UNAL
+is linked to 2 from 204 species, named:
+ BUFF UNPH
+
+species UNDU
+is linked to 0 from 204 species, named:
+
+species UNGR
+is linked to 6 from 204 species, named:
+ BARS LBBG GRSK HOGR SOTE SHOR
+
+species UNGU
+is linked to 3 from 204 species, named:
+ UNSC UNLO COEI
+
+species UNLA
+is linked to 10 from 204 species, named:
+  REPH MASH RBME UBBG UNME UNSG
+ UNST AUSH ATPU BRPE
+
+species UNLG
+is linked to 13 from 204 species, named:
+  DOVE GBBG RNPH FOTE LAGU RBGU
+ SOSH UNBI UNLT UNSP BRSP BOGU COGO
+
+species UNLO
+is linked to 3 from 204 species, named:
+ UNSC UNGU COEI
+
+species UNME
+is linked to 14 from 204 species, named:
+  RNPH REPH ROST FOTE MASH SCAU
+ POJA RBME UNLA UNST BRSP BCPE COGO DASC
+
+species UNMU
+is linked to 1 from 204 vertex, named:
+ UNGO
+
+species UNSA
+is linked to 5 from 204 species, named:
+ CEDW GBTE SNGO UNEG UNFI
+
+species UNSG
+is linked to 10 from 204 species, named:
+  REPH MASH RBME ROYT UBBG UNLA
+ AUSH ATPU BRPE UNSH
+
+species UNST
+is linked to 15 from 204 species, named:
+  RNPH REPH ROST FOTE MASH SCAU
+ POJA RBME UBBG UNLA UNME BRSP BCPE COGO DASC
+
+species UNTB
+is linked to 0 from 204 species, named:
+
+species WTTR
+is linked to 10 from 204 species, named:
+  ABDU GRCO CATE HEPE PUMA RNGR 
+SAND UNWA BRTE BLTE
+
+species WWSC
+is linked to 3 from 204 species, named:
+ COSH UNTE COTE
+
+species BANS
+is linked to 53 from 204 species, named:
+  AMGO AMKE AMOY AMRO BBPL BHCO
+ BHGU BRBO CHSW COME DUNL EUST GBHE SBDO GRYE
+ HADU HOME LESA LEYE NOPI ICGU
+ MALL OSPR PAWA PEEP PESA PISI RBNU REDH RUDU
+ RUTU RWBL SAGU SATE SEPL SESA
+ SOSP UCAT UNEI UNFR UNPE WFSP WHIM GOME GREG
+ MODO WIPH WODU YCNH YRWA BRNO
+ CANG AWPE
+
+species UNWA
+is linked to 13 from 204 species, named:
+  GRCO CATE GBHE LIGU HEPE LTJA
+ PUMA SAND TRES WTTR MYWA BRTE BLTE
+
+species USAN
+is linked to 0 from 204 species, named:
+
+species USSB
+is linked to 2 from 204 species, named:
+ GRSC GWTE
+
+species MYWA
+is linked to 20 from 204 species, named:
+  GRCO CATE COME DEJU GBHE LESA
+ LIGU HEPE LTJA OSPR PUMA SAND SESA TRES UNWA
+ WFSP GLGU GOME BRTE BLTE
+
+species WFSP
+is linked to 58 from 204 species, named:
+  AMGO AMKE AMOY AMRO BBPL BHCO
+ BHGU BRBO CHSW COME DEJU DUNL EUST GBHE SBDO
+ GRYE HADU HOME LESA LEYE LIGU
+ NOPI ICGU MALL OSPR PAWA PEEP PESA PISI RBNU
+ REDH RUDU RUTU RWBL SAGU SATE
+ SEPL SESA SOSP TRES UCAT UNEI UNFR UNPE BANS
+ MYWA WHIM GLGU GOME GREG MODO
+ WIPH WODU YCNH YRWA BRNO CANG AWPE
+
+species WHIM
+is linked to 53 from 204 species, named:
+  AMGO AMKE AMOY AMRO BBPL BHCO
+ BHGU BRBO CHSW COME DUNL EUST GBHE SBDO GRYE
+ HADU HOME LESA LEYE NOPI ICGU
+ MALL OSPR PAWA PEEP PESA PISI RBNU REDH RUDU
+ RUTU RWBL SAGU SATE SEPL SESA
+ SOSP UCAT UNEI UNFR UNPE BANS WFSP GOME GREG
+ MODO WIPH WODU YCNH YRWA BRNO
+ CANG AWPE
+
+species BLPW
+is linked to 0 from 204 species, named:
+
+species BTBW
+is linked to 0 from 204 species, named:
+
+species GLGU
+is linked to 26 from 204 species, named:
+  BHCO BHGU CATE COME DEJU DUNL
+ GBHE LESA LIGU ICGU OSPR REDH RWBL SEPL SESA
+ SOSP TRES UNEI UNPE MYWA WFSP
+ GOME MODO YRWA CANG AWPE
+
+species GOME
+is linked to 58 from 204 species, named:
+  AMGO AMKE AMOY AMRO BBPL BHCO
+ BHGU BRBO CHSW COME DEJU DUNL EUST GBHE SBDO
+ GRYE HADU HOME LESA LEYE LIGU
+ NOPI ICGU MALL OSPR PAWA PEEP PESA PISI RBNU
+ REDH RUDU RUTU RWBL SAGU SATE
+ SEPL SESA SOSP TRES UCAT UNEI UNFR UNPE BANS
+ MYWA WFSP WHIM GLGU GREG MODO
+ WIPH WODU YCNH YRWA BRNO CANG AWPE
+
+species GREG
+is linked to 52 from 204 species, named:
+  AMGO AMKE AMOY AMRO BBPL BHCO
+ BHGU BRBO CHSW COME DUNL EUST SBDO GRYE HADU
+ HOME LESA LEYE NOPI ICGU MALL
+ OSPR PAWA PEEP PESA PISI RBNU REDH RUDU RUTU
+ RWBL SAGU SATE SEPL SESA SOSP
+ UCAT UNEI UNFR UNPE BANS WFSP WHIM GOME MODO
+ WIPH WODU YCNH YRWA BRNO CANG AWPE
+
+species MERL
+is linked to 0 from 204 species, named:
+
+species MODO
+is linked to 55 from 204 species, named:
+  AMGO AMKE AMOY AMRO BBPL BHCO
+ BHGU BRBO CHSW COME DEJU DUNL EUST GBHE SBDO
+ GRYE HADU HOME LESA LEYE NOPI
+ ICGU MALL OSPR PAWA PEEP PESA PISI RBNU REDH
+ RUDU RUTU RWBL SAGU SATE SEPL
+ SESA SOSP UCAT UNEI UNFR UNPE BANS WFSP WHIM
+ GLGU GOME GREG WIPH WODU YCNH
+ YRWA BRNO CANG AWPE
+
+species RUBL
+is linked to 0 from 204 species, named:
+
+species BRTE
+is linked to 13 from 204 species, named:
+  ABDU GRCO CATE LIGU HEPE LTJA
+ PUMA SAND TRES WTTR UNWA MYWA BLTE
+
+species UNSK
+is linked to 4 from 204 species, named:
+ LBBG SHOR UNJA TBMU
+
+species UNSP
+is linked to 13 from 204 species, named:
+  COLO DOVE GBBG RNPH FOTE LAGU
+ SOSH UNBI UNLT UNLG BRSP COGO DASC
+
+species UNTE
+is linked to 3 from 204 species, named:
+ COSH RAZO WWSC
+
+species WILL
+is linked to 6 from 204 species, named:
+ GADW GRHE PUSA SPSA ULSB UCRT
+
+species WIPH
+is linked to 52 from 204 species, named:
+  AMGO AMKE AMOY AMRO BBPL BHCO
+ BHGU BRBO CHSW COME DUNL EUST SBDO GRYE HADU
+ HOME LESA LEYE NOPI ICGU MALL
+ OSPR PAWA PEEP PESA PISI RBNU REDH RUDU RUTU
+ RWBL SAGU SATE SEPL SESA SOSP
+ UCAT UNEI UNFR UNPE BANS WFSP WHIM GOME GREG
+ MODO WODU YCNH YRWA BRNO CANG AWPE
+
+species WODU
+is linked to 53 from 204 species, named:
+  AMGO AMKE AMOY AMRO BBPL BHCO
+ BHGU BRBO CHSW COME DUNL EUST GBHE SBDO GRYE
+ HADU HOME LESA LEYE NOPI ICGU
+ MALL OSPR PAWA PEEP PESA PISI RBNU REDH RUDU
+ RUTU RWBL SAGU SATE SEPL SESA
+ SOSP UCAT UNEI UNFR UNPE BANS WFSP WHIM GOME
+ GREG MODO WIPH YCNH YRWA BRNO CANG AWPE
+
+species WTSP
+is linked to 0 from 204 species, named:
+
+species YBCH
+is linked to 0 from 204 species, named:
+
+species YCNH
+is linked to 52 from 204 species, named:
+  AMGO AMKE AMOY AMRO BBPL BHCO
+ BHGU BRBO CHSW COME DUNL EUST SBDO GRYE HADU
+ HOME LESA LEYE NOPI ICGU MALL
+ OSPR PAWA PEEP PESA PISI RBNU REDH RUDU RUTU
+ RWBL SAGU SATE SEPL SESA SOSP
+ UCAT UNEI UNFR UNPE BANS WFSP WHIM GOME GREG
+ MODO WIPH WODU YRWA BRNO CANG AWPE
+
+species YRWA
+is linked to 55 from 204 species, named:
+  AMGO AMKE AMOY AMRO BBPL BHCO
+ BHGU BRBO CHSW COME DEJU DUNL EUST GBHE SBDO
+ GRYE HADU HOME LESA LEYE NOPI
+ ICGU MALL OSPR PAWA PEEP PESA PISI RBNU REDH
+ RUDU RUTU RWBL SAGU SATE SEPL
+ SESA SOSP UCAT UNEI UNFR UNPE BANS WFSP WHIM
+ GLGU GOME GREG MODO WIPH WODU 
+YCNH BRNO CANG AWPE
+
+species YWAR
+is linked to 0 from 204 species, named:
+
+species UNFI
+is linked to 5 from 204 species, named:
+ CEDW GBTE SNGO UNEG UNSA
+
+species UCRT
+is linked to 6 from 204 species, named:
+ GADW GRHE PUSA SPSA ULSB WILL
+
+species AUSH
+is linked to 7 from 204 species, named:
+ REPH MASH RBME UBBG UNLA UNSG BRPE
+
+species RTHU
+is linked to 0 from 204 species, named:
+
+species BRAN
+is linked to 0 from 204 species, named:
+
+species UNHU
+is linked to 0 from 204 species, named:
+
+species ATPU
+is linked to 10 from 204 species, named:
+  REPH MASH RBME ROYT UBBG
+ UNLA UNSG BRPE UNPH UNSH
+
+species BLGU
+is linked to 5 from 204 species, named:
+ COMU ARTE LETE SPSK PAJA
+
+species BRPE
+is linked to 11 from 204 species, named:
+  REPH MASH RBME ROYT UBBG
+ UNLA UNSG AUSH ATPU UNPH UNSH
+
+species HERG
+is linked to 0 from 204 species, named:
+
+species PAJA
+is linked to 5 from 204 species, named:
+ COMU ARTE LETE SPSK BLGU
+
+species BRSP
+is linked to 13 from 204 species, named:
+  DOVE RNPH ROST FOTE POJA UNBI
+ UNLG UNME UNST UNSP BCPE COGO DASC
+
+species BLKI
+is linked to 6 from 204 species, named:
+ ROST POJA RBGU UNBI BCPE BOGU
+
+species BCPE
+is linked to 13 from 204 species, named:
+  RNPH ROST FOTE SCAU POJA RBGU
+ UNME UNST BRSP BLKI BOGU COGO DASC
+
+species BLTE
+is linked to 14 from 204 species, named:
+  ABDU GRCO CATE GBHE LIGU HEPE
+ LTJA PUMA SAND TRES WTTR UNWA MYWA BRTE
+
+species BOGU
+is linked to 6 from 204 species, named:
+ ROST RBGU UNBI UNLG BLKI BCPE
+
+species BRNO
+is linked to 52 from 204 species, named:
+  AMGO AMKE AMOY AMRO BBPL BHCO
+ BHGU BRBO CHSW COME DUNL EUST SBDO GRYE HADU
+ HOME LESA LEYE NOPI ICGU MALL
+ OSPR PAWA PEEP PESA PISI RBNU REDH RUDU RUTU
+ RWBL SAGU SATE SEPL SESA SOSP
+ UCAT UNEI UNFR UNPE BANS WFSP WHIM GOME GREG
+ MODO WIPH WODU YCNH YRWA CANG AWPE
+
+species BUFF
+is linked to 2 from 204 species, named:
+ DCCO UNAL
+
+species CANG
+is linked to 55 from 204 species, named:
+  AMGO AMKE AMOY AMRO BBPL BHCO
+ BHGU BRBO CHSW COME DEJU DUNL EUST GBHE SBDO
+ GRYE HADU HOME LESA LEYE NOPI
+ ICGU MALL OSPR PAWA PEEP PESA PISI RBNU REDH
+ RUDU RUTU RWBL SAGU SATE SEPL
+ SESA SOSP UCAT UNEI UNFR UNPE BANS WFSP WHIM
+ GLGU GOME GREG MODO WIPH WODU
+ YCNH YRWA BRNO AWPE
+
+species COEI
+is linked to 3 from 204 species, named:
+ UNSC UNGU UNLO
+
+species COGO
+is linked to 13 from 204 species, named:
+  DOVE RNPH ROST FOTE POJA UNBI
+ UNLG UNME UNST UNSP BRSP BCPE DASC
+
+species COTE
+is linked to 2 from 204 species, named:
+ NOFU WWSC
+
+species WISP
+is linked to 1 from 204 vertex, named:
+ RTLO
+
+species UNPH
+is linked to 5 from 204 species, named:
+ ROYT UNAL ATPU BRPE UNSH
+
+species UNSH
+is linked to 5 from 204 species, named:
+ ROYT UNSG ATPU BRPE UNPH
+
+species DASC
+is linked to 12 from 204 species, named:
+  RNPH ROST FOTE SCAU POJA UNBI
+ UNME UNST UNSP BRSP BCPE COGO
+
+species AWPE
+is linked to 56 from 204 species, named:
+  AMGO AMKE AMOY AMRO BBPL BHCO
+ BHGU BRBO CHSW COME DEJU DUNL EUST GBHE SBDO
+ GRYE HADU HOME LESA LEYE NOPI
+ ICGU MALL OSPR PAWA PEEP PESA PISI RBNU REDH
+ RUDU RUTU RWBL SAGU SATE SEPL
+ SESA SOSP TRES UCAT UNEI UNFR UNPE BANS WFSP
+ WHIM GLGU GOME GREG MODO WIPH
+ WODU YCNH YRWA BRNO CANG
+
+species BUPE
+is linked to 0 from 204 species, named:
+\end{lstlisting}
+
 \bibliographystyle{rss}

### 2017-08-26 paper1_jrss.tex
updates to intro and data sections, table 1, bib file

@@
   Graphical modeling of seabird distributions.
-Simultaneous estimation of conditional spatial interrelation for a subset of $79$ seabird species by means of a spatial dependence graph model (SDGM).
+Simultaneous estimation of conditional spatial interrelation for a subset of $204$ seabird species by means of a spatial dependence graph model (SDGM).
 Linkage to Social network analysis toolbox to detect the most influential species (in term of importance within the estimated SDGM)
@@
 
+Information on the spatial distribution of marine birds is of particular interest to ecologists, environmentalists and policy-makers. 
+%Individual species maps conveying the spatial and temporal distribution over the US Mid- and Northeast-Atlantic ocean regions were created by~\cite{Balderama2016} for several sea bird species.
+
+%Models are usually run on individual species. 
+%There is a danger in this, in that it doesn't take into account the dependence structure between species. 
+There is a danger in this in that it is generally known that species distributions are not independent.
+Maps of the spatial distribution of marine birds undoubtedly have some overlap
+%It creates a false sense that a species distribution is independent
+
+Models are usually run on either individual species or all-species-combined data.
+\cite{Winiarski2014} first categorized species into different taxonomic groups before fitting a separate model to each grouping.
+\cite{Balderama2016} modeled several species individually and created separate distribution maps for each species.
+
+In ecology,
+Quantifying the spatial dependence structure between bird species and environmental covariates is important.
+While studies have related the spatial distribution of one species with that of a prey or predator species or of environmental variables acting as proxies for climate \citep{Goyert2014, Goyert2016}, there has been relatively few studies that investigate and utilize measures of inter-species dependence.
+
+Community models may combine several species, known to have facilitative interactions with each other, into one model \citep{Goyert2016, Sollmann2016}.
+However, these models treat the observed data the same way as if the observations belong to the same species, i.e., come from the same distribution.
+
+Studying the degree of interaction between species may help inform ocean planning and develop effective strategies for ecosystem management.
+Mapping the distribution of rare and endangered avian species is important when planning the placement of offshore wind energy developments.
+Such rare species are obviously difficult to monitor, so finding a more commonly occurring species that is highly dependent with the rare species has ecological importance.
+
+Ecological data usually contains spatial observations from multiple species of interest.
+
 The occurrence of a sea bird species in a particular location is affected (either positively or negatively) by the occurrence of other species in the same location. 
 Thus, external factors that may cause changes to the distribution of a single species will undoubtedly have an effect on the distribution of other species. 
-Determining these associations between different species has been difficult (CITATIONS), especially when trying to associate many species all at once.
-
-Quantifying the spatial dependence structure between bird species and environmental covariates is important.
-While studies have related the spatial distribution of one species with that of a prey or predator species, or of environmental variables acting as proxies for climate \citep{Goyert2014, Goyert2016}, there has been relatively few studies that investigate and utilize measures of inter-species dependence.
-
-Community models may combine several species, known to have facilitative interactions with each other, into one model \citep{Goyert2016, Sollmann2016}.
-However, these models treat the observed data the same way as if the observations are of only one species.
-
-Studying the degree of interaction between species may help inform ocean planning.
-Mapping the distribution of rare and endangered avian species is important when planning the placement of offshore wind farms.
-Such rare species are obviously difficult to monitor, so finding a more commonly occuring species that is highly dependent with the rare species has ecological importance.
-
+Determining these associations between different species has been difficult~\citep{Stachowicz2001}, especially when trying to find the associations between many species all at once.
 Attempts at modeling between-species interactions are often limited to the bivariate case \citep{Andersen1992, Nightingale2015}.
@@
 
-Ecological data usually contains spatial observations from multiple species of interest.
-
-There is a need for fast and practically applicable methods for analysing multivariate point patterns, and is currently a growing but challenging topic for researchers \citep{Moller2016}.
-
-Information on the distribution of sea birds, especially in the form of maps, is of particular interest to ecologists, environmentalists and policy-makers.
-Maps conveying the spatial and temporal distribution over the US Mid- and Northeast-Atlantic ocean regions were created by \cite{Balderama2016} for several individual species of marine birds.
-
-Models are usually run on inidivudal species. 
-%There is a danger in this, in that it doesn't take into account the dependence structure between species. 
-There is a danger in this in that tt is generally known that species distributions are not independent.
-Maps of the spatial distribution of marine birds undoubetedly have some overlap
-
-However, a multivariate analysis of sea bird distribution would be very useful in determining how bird species affect one another's presence.
-
-This will also help us to categorize observations of unidentified or unknown species to those of identified species.
-
-%It creates a false sense that a species distribution is independent
-
-%Models are usually run on either indivudual species or all-species-combined data.
-
-There are several advantages with this approach:
-
-1. These observations are usually removed before analyzing data at the species level.
-
-Here we include these locations of unknown species and from the results may be able to determine what species they are more likely to be from the resulting network map.
+At the same time, there is a need for fast and practically applicable methods for analyzing multivariate point patterns, and this is currently a growing but challenging topic for researchers~\citep{Moller2016}.
+
+In this paper, we explore the dependence structure between multiple sea bird species distributions, using the graphical modelling approach of~\cite{Eckardt2016b}. %%%%%%%%%
+
+%There are several advantages with this approach:
+Using this approach,
+1. A multivariate analysis of sea bird distributions may be useful in determining how one bird species affects the presence of another.
+
+2. This will help us to categorize observations of unidentified or unknown species to those of identified species.
+
+Observations labelled as ``unidentified'' are often removed before analyzing data at the species level.
+Here we include these data and may be able to determine what species they are most likely to be from the resulting network map.
+
+The sea bird data is described, as a multivariate spatially marked point process, in Section~\ref{Data}.
+We apply the graphical model to the sea bird data in Section~\ref{Methods} and illustrate some resulting network maps in Section~\ref{Results}.
+Concluding remarks are given in Section~\ref{Conclusions}.
 
 %============================================
-\section{Data}
+\section{Data}\label{Data}
 %============================================
@@
 Data are point locations of marine bird sightings over the Northeast- and Mid-Atlantic coast regions of the United States, as described in \cite{Balderama2016}.
-The point locations are the longitude and latitude coordinates of the midpoints of line transect segments from boat and aerial surveys between July, 1998 and April, 2014.
-Species are labelled by its common name and a four-letter species code.
-Names that include the word ``unidentified'' accommodate birds identified to a family but not to a species.
-
-Table~\ref{tab:species} shows a summary of the observed data by species code and common name. There are 79 different codes. However, some codes signify an unidentified or partially identified species.
-
-\textit{ For our analysis we considered  on 128812 locations on marine bird sightings related to 306 different marine birds.
+The point locations are the longitude and latitude coordinates of the midpoints of transect segments from boat and aerial strip transect surveys between July, 1998 and April, 2014.
+Out of 90660 total point locations for potential sightings, 53842 have at least one species sighting.
+Because more than one species may be sighted in any one location, the full data contains 128812 total species-location combinations.
+Species are labelled by its common name and a corresponding four-letter species code.
+The full data contains 306 different codes.
+Some codes signify an unidentified or partially identified species.
+For example, the word ``unidentified'' may accommodate birds that have been identified to a family but not to a species.
+In this paper, however, we will use the term ``species'' to refer to different four-letter codes.
+For our analysis we consider only 204 (out of 306) species that have been sighted in at least three locations. By this, our analysis covers 53820 locations and 128674 species-location combinations.
+
+A sighting is a recorded observation at least one individual bird.
+In the context of spatially marked point patterns, each sighting corresponds to one point of a species' point pattern, with the mark of the point being the number of birds observed in that sighting.
+Table~\ref{tab:species} shows the total number of birds observed and the average mark for the twenty most frequently recorded bird species by common name and species code.
+Observed planar point patterns for these twenty most sighted species are shown in Figure~\ref{fig:birds20}.
+
+%\textit{ For our analysis we considered on 128812 locations on marine bird sightings related to 306 different marine birds.
 Form this data, we preselected a sample of 204 species which have have at least been observed at three locations.
 By this, our analysis covered 128674 different locations.}
-
-The observed planar point patterns for the $20$ most frequently recorded bird species is shown in Figure \ref{fig:birds20}.
 
@@
 
-\textbf{Maybe reduce table to most frequent species, eg. top 20 birds}
-
-%\afterpage{
-{\scriptsize
-\begin{longtable}{| l | c | c | c | c | c | c | }
-\caption{Summary of observed data by species code.}
-\label{tab:species}\\
+%\textbf{Maybe reduce table to most frequent species, eg. top 20 birds}
+
+%latex.default(format.df(latdf, cdec = c(0, 0, 0, 0, 2), na.blank = TRUE),     file = "", longtable = TRUE, rowname = NULL, size = "scriptsize",     caption = "Summary of top 20 most frequently sighted species.",     label = "tab:species")%
+\setlongtables{\scriptsize
+\begin{longtable}{llrrr}\caption{Summary of top 20 most frequently sighted species.} \tabularnewline
+\hline\hline
+\multicolumn{1}{c}{Species code}&\multicolumn{1}{c}{Common name}&\multicolumn{1}{c}{total}&\multicolumn{1}{c}{sightings}&\multicolumn{1}{c}{average mark}\tabularnewline
 \hline
-  &   &  &   &   &   &  \\ 
-\textbf{Species code}  & \textbf{Common name}  & \textbf{sightings}  &\textbf{average mark}  &\textbf{}  &\textbf{}  &\textbf{}   \\ 
+\endfirsthead\caption[]{\em (continued)} \tabularnewline
 \hline
-ABDU &  American Black Duck & 47 & 1.25 &  &  &  \\ 
-ARTE &  Arctic Tern & 103 & 0.94 &  &   &  \\ 
-ATPU &  Atlantic Puffin & 403 & 1.17 &   &  &  \\ 
-AUSH &  Audubon's Shearwater & 86 & 1.20 &   &  &  \\ 
-BRSP &  Band-rumped Storm-petrel & 23   & 0.29 &  &  &  \\ 
-BARS &  Barn Swallow & 99 & 0.34 &  &  &    \\ 
-BCPE &  Black-capped Petrel & 3 & 1.56  &    &  &  \\ 
-BLKI &  Black-legged Kittiwake & 971 & 1.45 &  &  &  \\ 
-BLGU &  Black Guillemot & 75 & 0.42  &  &  &  \\ 
-BLSC &  Black Scoter & 669 & 4.31 &  &   &  \\ 
-BOGU &  Bonaparte's Gull & 708 & 0.99 &  &   &  \\ 
-BRPE &  Brown Pelican & 92 & 0.29 &  &  &   \\ 
-BUFF &  Bufflehead & 159 & 1.86 &  &  &  \\ 
-COEI &  Common Eider & 528 & 59.74 &  &    &  \\ 
-COGO &  Common Goldeneye & 82 & 1.25 &    &  &  \\ 
-COLO &  Common Loon & 1900 & 0.51 &   &  &  \\ 
-COMU &  Common Murre & 153 & 0.88  &   &  &  \\ 
-COTE &  Common Tern & 982 & 1.80 &  &   &  \\ 
-COSH &  Cory's Shearwater & 1138 & 2.69 &  &  &  \\ 
-DASC &  Dark Scoter (Black or Surf) & 199 & 2.09 &  &  &   \\ 
-DCCO &  Double-crested Cormorant & 354 & 2.37 &  &  &  \\ 
-DOVE &  Dovekie & 962 & 5.73 &  &  &    \\ 
-FOTE &  Forster's Tern & 119 & 0.52 &  &    &  \\ 
-GBBG &  Great Black-backed Gull & 3319 & 2.46  &  &   &  \\ 
-UBBG &  Great or Lesser Black-backed Gull & 299 & 0.18 &  &   &  \\ 
-GRSH &  Great Shearwater & 3732 & 8.99 &  &  &   \\ 
-GRSK &  Great Skua & 117 & 0.61 &  &  & \\ 
-HERG &  Herring Gull & 3978 & 2.71 &  &  &  \\ 
-HOGR &  Horned Grebe & 65 & 0.07 &  &  &  \\ 
-LAGU &  Laughing Gull & 856  & 0.80 &  &   &  \\ 
-LESP &  Leach's Storm-petrel & 1005 & 3.63 &  &  &  \\ 
-LETE &  Least Tern & 61 & 0.27 &  &  &  \\ 
-LBBG &  Lesser Black-backed Gull & 97 & 0.30 &  &  &  \\ 
-LTDU &  Long-tailed Duck & 851 & 8.64 &  &  &    \\ 
-MASH &  Manx Shearwater & 374 & 0.92 &  &  &    \\ 
-NOFU &  Northern Fulmar & 1688 & 5.25 &  &  &   \\ 
-NOGA &  Northern Gannet & 3451 & 2.51 &  &  &   \\ 
-PAJA &  Parasitic Jaeger & 154 & 0.37 &  &  &   \\ 
-POJA &  Pomarine Jaeger & 287 & 0.70 &  &  &   \\ 
-RAZO &  Razorbill & 908 & 1.26 &  &  &   \\ 
-REPH &  Red Phalarope & 394 & 8.64 &  &  &  \\ 
-RBME &  Red-breasted Merganser & 220 & 0.78 &  &  &  \\ 
-RNGR &  Red-necked Grebe & 49 & 0.11 &  &  &    \\ 
-RNPH &  Red-necked Phalarope & 207 & 7.65 &  &  &    \\ 
-RTLO &  Red-throated Loon & 1400 & 0.59 &  &  &   \\ 
-RBGU &  Ring-billed Gull & 530 & 0.71 &  &  &   \\ 
-ROST &  Roseate Tern & 115 & 0.88 &  &  &    \\ 
-ROYT &  Royal Tern & 207 & 0.22 &  &  &    \\ 
-SOSH &  Sooty Shearwater & 871 & 6.69 &  &  &   \\ 
-SPSK &  South Polar Skua & 169 & 0.74  &  &  &  \\ 
-SUSC &  Surf Scoter & 678 & 4.96 &  &  &   \\ 
-TBMU &  Thick-billed Murre & 83 & 1.33 & &  &  \\ 
-UNAL &  Unidentified Alcid & 555 & 0.71 &  &  &  \\ 
-UNBI &  Unidentified Bird & 543 & 1.06 &  &  &  \\ 
-UNCO &  Unidentified Cormorant & 99 & 0.43  &  &  &  \\ 
-UNDD &  Unidentified Diving/Sea Duck & 121 & 0.80 &  &  &  \\ 
-UNGO &  Unidentified Goldeneye & 34 & 2.29 &  &  &  \\ 
-UNGR &  Unidentified Grebe & 63 & 0.06 &  &  &  \\ 
-UNGU &  Unidentified Gull & 984 & 2.98 &  &  &  \\ 
-UNJA &  Unidentified Jaeger & 78 & 0.46 & &  &  \\ 
-UNLA &  Unidentified Large Alcid (Razorbill or Murre) & 330 & 0.84 &  &  &  \\ 
-UNLG &  Unidentified Large Gull & 553 & 3.51  &  &  &  \\ 
-UNLT &  Unidentified Large Tern & 91 & 0.35 & &  &  \\ 
-UNLO &  Unidentified Loon & 754 & 0.64 &  &  &  \\ 
-UNME &  Unidentified Merganser & 117 & 0.97 &  &  &  \\ 
-UNMU &  Unidentified Murre & 73 & 1.98 & &  &  \\ 
-UNPA &  Unidentified Passerine & 97 & 0.47 &  &  &  \\ 
-UNPH &  Unidentified Phalarope & 292 & 28.47 &  &  &  \\ 
-SCAU &  Unidentified Scaup & 52 & 11.02  & &  &  \\ 
-UNSC &  Unidentified Scoter & 703 & 26.64 &  &  &  \\ 
-UNSH &  Unidentified Shearwater & 364 & 3.80 & &  &  \\ 
-SHOR &  Unidentified Shorebird & 87 & 1.96 &  &  &  \\ 
-UNSK &  Unidentified Skua & 89 & 0.67 &  &  &  \\ 
-UNSG &  Unidentified Small Gull & 313 & 0.38  &  &  &  \\ 
-UNST &  Unidentified Small Tern & 184 & 0.18 &  &  &  \\ 
-UNSP &  Unidentified Storm-petrel & 379 & 40.11 & &  &  \\ 
-UNTE &  Unidentified Tern & 619 & 2.62 &  &  &  \\ 
-WWSC &  White-winged Scoter & 522 & 2.78 &  &  &   \\ 
-WISP &  Wilson's Storm-petrel & 2746 & 6.88 &  &  &  \\ 
+\multicolumn{1}{c}{Species code}&\multicolumn{1}{c}{Common name}&\multicolumn{1}{c}{total}&\multicolumn{1}{c}{sightings}&\multicolumn{1}{c}{average mark}\tabularnewline
+\hline
+\endhead
+\hline
+\endfoot
+\label{tab:species}
+BLSC&Black Scoter&$ 88865$&$ 2444$&$ 36.36$\tabularnewline
+COEI&Common Eider&$958282$&$ 4127$&$232.20$\tabularnewline
+COLO&Common Loon&$ 17456$&$ 6795$&$  2.57$\tabularnewline
+COSH&Cory's Shearwater&$  9434$&$ 2328$&$  4.05$\tabularnewline
+COTE&Common Tern&$ 15054$&$ 2212$&$  6.81$\tabularnewline
+GBBG&Great Black-backed Gull&$ 26882$&$ 7581$&$  3.55$\tabularnewline
+GRSH&Greater Shearwater&$ 64941$&$ 6213$&$ 10.45$\tabularnewline
+HERG&Herring gull&$ 55233$&$10990$&$  5.03$\tabularnewline
+LAGU&Laughing Gull&$ 12535$&$ 2834$&$  4.42$\tabularnewline
+LTDU&Long-tailed Duck&$209151$&$ 5602$&$ 37.34$\tabularnewline
+NOGA&Northern Gannet&$ 81759$&$12831$&$  6.37$\tabularnewline
+RAZO&Razorbill&$ 17306$&$ 2410$&$  7.18$\tabularnewline
+RTLO&Red-throated Loon&$ 16039$&$ 4737$&$  3.39$\tabularnewline
+SUSC&Surf Scoter&$106770$&$ 4059$&$ 26.30$\tabularnewline
+UNGU&Unidentified Gull&$ 39067$&$ 3976$&$  9.83$\tabularnewline
+UNLO&Unidentified Loon&$ 31741$&$ 3962$&$  8.01$\tabularnewline
+UNSC&Unidentified Scoter&$546211$&$ 3950$&$138.28$\tabularnewline
+UNTE&Unidentified Tern&$ 24232$&$ 2331$&$ 10.40$\tabularnewline
+WISP&Wilson's Storm-petrel&$ 40689$&$ 4845$&$  8.40$\tabularnewline
+WWSC&White-winged Scoter&$ 33095$&$ 2310$&$ 14.33$\tabularnewline
 \hline
 \end{longtable}}
-%}
-
-While some marine bird species such as various types of gulls have been sighted at numerous locations, other species occurred only very rarely.
+
+While some marine bird species, such as various types of gulls, have been sighted at numerous locations, other species occurred only very rarely.
 At the same time, as we defined a minimum of at least $50$ marine birds per species as inclusion criteria, this limited number of locations equivalently implies that certain marine bird species appeared in groupings rather than as isolated birds or occurred only in a geographically strictly-limited habitat.
@@
 Discovering the relevant subset of species whose spatial occurrence is linked to the spatial pattern of any endangered species  by means of a SDGM might provide new insights into multivariate interdependencies.
-This new insights might provide important knowledge for the conservation of endangered species and might assist to understand such phenomena from a global perspective on different natural environments.
+These new insights might provide important knowledge for the conservation of endangered species and might assist to understand such phenomena from a global perspective on different natural environments.
 
